\bibbook{H PROS TOUS KORINJIOUS\\\LARGE DEUTERA\r{}}{PROS KORINJIOUS B'}{II Corinthians}{2Co}[PROS KORINJIOUS B']
\vs 2Co 1:1
pa~uloc
\fnt{\src{T}: H PROS TOUS KORINJIOUS DEUTERA, \src{K}: PAULOU TOU APOSTOLOU H PROS TOUS KORINJIOUS EPISTOLH DEUTERA, \src{M|V}: PROS KORINJIOUS B.}
>ap'ostoloc
>ihso~u\r{}
\fn{\src{TMK}: ihsou qristou, \src{V}: qristou ihsou.}
qristo~u
di`a
vjel'hmatoc
vjeo~u
ka`i
tim'ojeoc
<o
>adelf`oc
t~h|
>ekklhs'ia|
to~u
vjeo~u
t~h|
o>'ush|
>en
kor'injw|
s`un
to~ic
<ag'ioic
p~asin
to~ic
o>~usin
>en
<'olh|
t~h|
>aqa"'ia|\bibvsend
\vs 2Co 1:2
q'aric
<um~in
ka`i
e>ir'hnh
>ap`o
vjeo~u
patr`oc
<hm~wn
ka`i
kur'iou
>ihso~u
qristo~u\bibvsend
\vs 2Co 1:3
e>uloght`oc
<o
vje`oc
ka`i
pat`hr
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
<o
pat`hr
t~wn
o>iktirm~wn
ka`i
vje`oc
p'ashc
parakl'hsewc\bibvsend
\vs 2Co 1:4
<o
parakal~wn
<hm~ac
>ep`i
p'ash|
t~h|
vjl'iyei
<hm~wn
e>ic
t`o
d'unasjai
<hm~ac
parakale~in
to`uc
>en
p'ash|
vjl'iyei
di`a
t~hc
parakl'hsewc
<~hc
parakalo'umeja
a>uto`i
<up`o
to~u
vjeo~u\bibvsend
\vs 2Co 1:5
<'oti
kaj`wc
perisse'uei
t`a
paj'hmata
to~u
qristo~u
e>ic
<hm~ac
o<'utwc
di`a\r{}
\fn{\src{T|K}: dia, \src{M|V}: dia tou.}
qristo~u
perisse'uei
ka`i
<h
par'aklhsic
<hm~wn\bibvsend
\vs 2Co 1:6
e>'ite
d`e
vjlib'omeja
<up`er
t~hc
<um~wn
parakl'hsewc
ka`i
swthr'iac
\r{t}~hc
\fn{\src{TMK}: thc, \src{V}: eite parakaloumeja uper thc umwn paraklhsewc thc.}
>energoum'enhc
>en
<upomon~h|
t~wn
a>ut~wn
pajhm'atwn
<~wn
ka`i
<hme~ic
p'asqomen
e>'ite\r{}
\fn{\src{T|K}: eite parakaloumeja uper thc umwn paraklhsewc kai swthriac kai h elpic hmwn vbebaia uper umwn, \src{M}: kai h elpic hmwn vbebaia uper umwn eite parakaloumeja uper thc umwn paraklhsewc kai swthriac, \src{V}: kai h elpic hmwn vbebaia uper umwn.}
parakalo'umeja
<up`er
t~hc
<um~wn
parakl'hsewc
ka`i
swthr'iac
ka`i
<h
>elp`ic
<hm~wn
vbeba'ia
<up`er
<um~wn\bibvsend
\vs 2Co 1:7
e>id'otec
<'oti
<'ws\r{p}er
\fn{\src{TMK}: wsper, \src{V}: wc.}
koinwno'i
>este
t~wn
pajhm'atwn
o<'utwc
ka`i
t~hc
parakl'hsewc\bibvsend
\vs 2Co 1:8
o>u
g`ar
vj'elomen
<um~ac
>agnoe~in
>adelfo`i
<up`er
t~hc
vjl'iyewc
<hm~wn
t~hc
genom'enhc
<h\r{m}~in
\fn{\src{TMK}: hmin, \src{V}: \bibempty.}
>en
t~h|
>as'ia|
<'oti
kaj>
<uperbol`hn
>ebar'hjhmen\r{}
\fn{\src{TMK}: ebarhjhmen uper dunamin, \src{V}: uper dunamin ebarhjhmen.}
<up`er
d'unamin
<'wste
>exaporhj~hnai
<hm~ac
ka`i
to~u
vz~h|n\bibvsend
\vs 2Co 1:9
>all`a
a>uto`i
>en
<eauto~ic
t`o
>ap'okrima
to~u
vjan'atou
>esq'hkamen
<'ina
m`h
pepoij'otec
>~wmen
>ef>
<eauto~ic
>all>
>ep`i
t~w|
vje~w|
t~w|
>ege'ironti
to`uc
nekro'uc\bibvsend
\vs 2Co 1:10
<`oc
>ek
thliko'utou
vjan'atou
>err'usato
<hm~ac
ka`i
<r'u\r{e}tai
\fn{\src{TMK}: vruetai, \src{V}: vrusetai.}
e>ic
<`on
>hlp'ikamen
<'oti
ka`i
>'eti
<r'usetai\bibvsend
\vs 2Co 1:11
sunupourgo'untwn
ka`i
<um~wn
<up`er
<hm~wn
t~h|
de'hsei
<'ina
>ek
poll~wn
pros'wpwn
t`o
e>ic
<hm~ac
q'arisma
di`a
poll~wn
e>uqaristhj~h|
<up`er
<h\r{m}~wn\bibvsend
\fn{\src{T|K|V}: hmwn, \src{M}: umwn.}
\vs 2Co 1:12
<h
g`ar
ka'uqhsic
<hm~wn
a<'uth
>est`in
t`o
mart'urion
t~hc
suneid'hsewc
<hm~wn
<'oti
>en
<apl'othti
ka`i
e>ilikrine'ia|
vj\r{e}o~u
\fn{\src{TMK}: vjeou, \src{V}: tou vjeou [kai].}
o>uk
>en
sof'ia|
sarkik~h|
>all>
>en
q'ariti
vjeo~u
>anestr'afhmen
>en
t~w|
k'osmw|
perissot'erwc
d`e
pr`oc
<um~ac\bibvsend
\vs 2Co 1:13
o>u
g`ar
>'alla
gr'afomen
<um~in
>all>
>`h
<`a
>anagin'wskete
>`h
ka`i
>epigin'wskete
>elp'izw
d`e
<'oti
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
<'ewc
t'elouc
>epign'wsesje\bibvsend
\vs 2Co 1:14
kaj`wc
ka`i
>ep'egnwte
<hm~ac
>ap`o
m'erouc
<'oti
ka'uqhma
<um~wn
>esmen
kaj'aper
ka`i
<ume~ic
<hm~wn
>en
t~h|
<hm'era|
to~u
kur'io\r{u}
\fn{\src{TMK}: kuriou, \src{V}: kuriou [hmwn].}
>ihso~u\bibvsend
\vs 2Co 1:15
ka`i
ta'uth|
t~h|
pepoij'hsei
>eboul'omhn
pr`oc\r{}
\fn{\src{T|K}: proc umac eljein proteron, \src{M}: eljein proc umac to proteron, \src{V}: proteron proc umac eljein.}
<um~ac
>elje~in
pr'oteron
<'ina
deut'eran
q'arin
>'e\r{q}hte\bibvsend
\fn{\src{TMK}: eqhte, \src{V}: sqhte.}
\vs 2Co 1:16
ka`i
di>
<um~wn
dielje~in
e>ic
makedon'ian
ka`i
p'alin
>ap`o
makedon'iac
>elje~in
pr`oc
<um~ac
ka`i
<uf>
<um~wn
propemfj~hnai
e>ic
t`hn
>iouda'ian\bibvsend
\vs 2Co 1:17
to~uto
o>~un
vbouleu'omenoc\r{}
\fn{\src{TMK}: vbouleuomenoc mh ti, \src{V}: vboulomenoc mhti.}
m'h
ti
>'ara
t~h|
>elafr'ia|
>eqrhs'amhn
>`h
<`a
vboule'uomai
kat`a
s'arka
vboule'uomai
<'ina
>~h|
par>
>emo`i
t`o
na`i
na`i
ka`i
t`o
o>`u
o>'u\bibvsend
\vs 2Co 1:18
pist`oc
d`e
<o
vje`oc
<'oti
<o
l'ogoc
<hm~wn
<o
pr`oc
<um~ac
o>uk
>e\r{g}'eneto
\fn{\src{TMK}: egeneto, \src{V}: estin.}
na`i
ka`i
o>'u\bibvsend
\vs 2Co 1:19
<o
g`ar\r{}
\fn{\src{TMK}: gar tou vjeou, \src{V}: tou vjeou gar.}
to~u
vjeo~u
u<i`oc
>ihso~uc
qrist`oc
<o
>en
<um~in
di>
<hm~wn
khruqje`ic
di>
>emo~u
ka`i
silouano~u
ka`i
timoj'eou
o>uk
>eg'eneto
na`i
ka`i
o>`u
>all`a
na`i
>en
a>ut~w|
g'egonen\bibvsend
\vs 2Co 1:20
<'osai
g`ar
>epaggel'iai
vjeo~u
>en
a>ut~w|
t`o
na`i
ka`i\r{}
\fn{\src{TMK}: kai en autw, \src{V}: dio kai di autou.}
>en
a>ut~w|
t`o
>am`hn
t~w|
vje~w|
pr`oc
d'oxan
di>
<hm~wn\bibvsend
\vs 2Co 1:21
<o
d`e
vbebai~wn
<hm~ac
s`un
<um~in
e>ic
qrist`on
ka`i
qr'isac
<hm~ac
vje'oc\bibvsend
\vs 2Co 1:22
<o
ka`i
sfragis'amenoc
<hm~ac
ka`i
do`uc
t`on
>arrab~wna
to~u
pne'umatoc
>en
ta~ic
kard'iaic
<hm~wn\bibvsend
\vs 2Co 1:23
>eg`w
d`e
m'artura
t`on
vje`on
>epikalo~umai
>ep`i
t`hn
>em`hn
yuq`hn
<'oti
vfeid'omenoc
<um~wn
o>uk'eti
>~hljon
e>ic
k'orinjon\bibvsend
\vs 2Co 1:24
o>uq
<'oti
kurie'uomen
<um~wn
t~hc
p'istewc
>all`a
sunergo'i
>esmen
t~hc
qar~ac
<um~wn
t~h|
g`ar
p'istei
<est'hkate\bibvsend
\vs 2Co 2:1
>'ekrina
d`e\r{}
\fn{\src{TMK}: de, \src{V}: gar.}
>emaut~w|
to~uto
t`o
m`h
p'alin
>elje~in\r{}
\fn{\src{T|K}: eljein en luph proc umac, \src{M|V}: en luph proc umac eljein.}
>en
l'uph|
pr`oc
<um~ac\bibvsend
\vs 2Co 2:2
e>i
g`ar
>eg`w
lup~w
<um~ac
ka`i
t'ic
>e\r{s}tin
\fn{\src{TMK}: estin, \src{V}: \bibempty.}
<o
e>ufra'inwn
me
e>i
m`h
<o
lupo'umenoc
>ex
>emo~u\bibvsend
\vs 2Co 2:3
ka`i
>'egraya
<u\r{m}~in
\fn{\src{TMK}: umin, \src{V}: \bibempty.}
to~uto
a>ut`o
<'ina
m`h
>elj`wn
l'uphn
>'e\r{q}w
\fn{\src{TMK}: eqw, \src{V}: sqw.}
>af>
<~wn
>'edei
me
qa'irein
pepoij`wc
>ep`i
p'antac
<um~ac
<'oti
<h
>em`h
qar`a
p'antwn
<um~wn
>estin\bibvsend
\vs 2Co 2:4
>ek
g`ar
poll~hc
vjl'iyewc
ka`i
sunoq~hc
kard'iac
>'egraya
<um~in
di`a
poll~wn
dakr'uwn
o>uq
<'ina
luphj~hte
>all`a
t`hn
>ag'aphn
<'ina
gn~wte
<`hn
>'eqw
perissot'erwc
e>ic
<um~ac\bibvsend
\vs 2Co 2:5
e>i
d'e
tic
lel'uphken
o>uk
>em`e
lel'uphken
>al\r{l}>
\fn{\src{T|K}: all, \src{M|V}: alla.}
>ap`o
m'erouc
<'ina
m`h
>epibar~w
p'antac
<um~ac\bibvsend
\vs 2Co 2:6
<ikan`on
t~w|
toio'utw|
<h
>epitim'ia
a<'uth
<h
<up`o
t~wn
plei'onwn\bibvsend
\vs 2Co 2:7
<'wste
to>unant'ion
m~allon
<um~ac
qar'isasjai
ka`i
parakal'esai
m'h\r{p}wc
\fn{\src{T}: mhpwc, \src{K|M|V}: mh pwc.}
t~h|
perissot'era|
l'uph|
katapoj~h|
<o
toio~utoc\bibvsend
\vs 2Co 2:8
di`o
parakal~w
<um~ac
kur~wsai
e>ic
a>ut`on
>ag'aphn\bibvsend
\vs 2Co 2:9
e>ic
to~uto
g`ar
ka`i
>'egraya
<'ina
gn~w
t`hn
dokim`hn
<um~wn
e>i
e>ic
p'anta
<up'hkoo'i
>este\bibvsend
\vs 2Co 2:10
<~w|
d'e
ti
qar'izesje
ka`i\r{}
\fn{\src{TMK}: kai egw, \src{V}: kagw.}
>eg`w
ka`i
g`ar
>eg`w
e>'i\r{}
\fn{\src{TMK}: ei ti keqarismai w, \src{V}: o keqarismai ei ti.}
ti
keq'arismai
<~w|
keq'arismai
di>
<um~ac
>en
pros'wpw|
qristo~u\bibvsend
\vs 2Co 2:11
<'ina
m`h
pleonekthj~wmen
<up`o
to~u
satan~a
o>u
g`ar
a>uto~u
t`a
no'hmata
>agnoo~umen\bibvsend
\vs 2Co 2:12
>elj`wn
d`e
e>ic
t`hn
trw'ada
e>ic
t`o
e>uagg'elion
to~u
qristo~u
ka`i
vj'urac
moi
>anew|gm'enhc
>en
kur'iw|\bibvsend
\vs 2Co 2:13
o>uk
>'esqhka
>'anesin
t~w|
pne'umat'i
mou
t~w|
m`h
e<ure~in
me
t'iton
t`on
>adelf'on
mou
>all`a
>apotax'amenoc
a>uto~ic
>ex~hljon
e>ic
makedon'ian\bibvsend
\vs 2Co 2:14
t~w|
d`e
vje~w|
q'aric
t~w|
p'antote
vjriambe'uonti
<hm~ac
>en
t~w|
qrist~w|
ka`i
t`hn
>osm`hn
t~hc
gn'wsewc
a>uto~u
vfanero~unti
di>
<hm~wn
>en
pant`i
t'opw|\bibvsend
\vs 2Co 2:15
<'oti
qristo~u
e>uwd'ia
>esm`en
t~w|
vje~w|
>en
to~ic
swzom'enoic
ka`i
>en
to~ic
>apollum'enoic\bibvsend
\vs 2Co 2:16
o<~ic
m`en
>osm`h
vj\r{a}n'atou
\fn{\src{TMK}: vjanatou, \src{V}: ek vjanatou.}
e>ic
vj'anaton
o<~ic
d`e
>osm`h
vz\r{w}~hc
\fn{\src{TMK}: vzwhc, \src{V}: ek vzwhc.}
e>ic
vzw`hn
ka`i
pr`oc
ta~uta
t'ic
<ikan'oc\bibvsend
\vs 2Co 2:17
o>u
g'ar
>esmen
<wc
o<i
\r{p}ollo`i
\fn{\src{T|K|V}: polloi, \src{M}: loipoi.}
kaphle'uontec
t`on
l'ogon
to~u
vjeo~u
>all>
<wc
>ex
e>ilikrine'iac
>all>
<wc
>ek
vjeo~u
katen'wpion\r{}
\fn{\src{TMK}: katenwpion tou, \src{V}: katenanti.}
to~u
vjeo~u
>en
qrist~w|
lalo~umen\bibvsend
\vs 2Co 3:1
>arq'omeja
p'alin
<eauto`uc
sunist'anein
\r{e}>i
\fn{\src{T|M}: ei, \src{K|V}: h.}
m`h
qr'h|zomen
<'wc
tinec
sustatik~wn
>epistol~wn
pr`oc
<um~ac
>`h
>ex
<um~wn
su\-st\r{a}\-ti\-k~wn\bibvsend
\fn{\src{TMK}: sustatikwn, \src{V}: \bibempty.}
\vs 2Co 3:2
<h
>epistol`h
<hm~wn
<ume~ic
>este
>eggegramm'enh
>en
ta~ic
kard'iaic
<hm~wn
ginwskom'enh
ka`i
>anaginwskom'enh
<up`o
p'antwn
>anjr'wpwn\bibvsend
\vs 2Co 3:3
vfanero'umenoi
<'oti
>est`e
>epistol`h
qristo~u
diakonhje~isa
<uf>
<hm~wn
>eggegramm'enh
o>u
m'elani
>all`a
pne'umati
vjeo~u
vz~wntoc
o>uk
>en
plax`in
lij'inaic
>all>
>en
plax`in
kard'i\r{a}c
\fn{\src{T|K}: kardiac, \src{M|V}: kardiaic.}
sark'inaic\bibvsend
\vs 2Co 3:4
pepo'ijhsin
d`e
toia'uthn
>'eqomen
di`a
to~u
qristo~u
pr`oc
t`on
vje'on\bibvsend
\vs 2Co 3:5
o>uq
<'oti
<ikano'i\r{}
\fn{\src{TMK}: ikanoi esmen af eautwn, \src{V}: af eautwn ikanoi esmen.}
>esmen
>af>
<eaut~wn
log'isasja'i
ti
<wc
>ex
<eaut~wn
>all>
<h
<ikan'othc
<hm~wn
>ek
to~u
vjeo~u\bibvsend
\vs 2Co 3:6
<`oc
ka`i
<ik'anwsen
<hm~ac
diak'onouc
kain~hc
diaj'hkhc
o>u
gr'ammatoc
>all`a
pne'umatoc
t`o
g`ar
gr'amma
>apokt\r{e}'inei
\fn{\src{T|K}: apokteinei, \src{M}: apoktenei, \src{V}: apoktennei.}
t`o
d`e
pne~uma
vzwopoie~i\bibvsend
\vs 2Co 3:7
e>i
d`e
<h
diakon'ia
to~u
vjan'atou
>en
gr'ammasin
>entetupwm'enh
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
l'ijoic
>egen'hjh
>en
d'oxh|
<'wste
m`h
d'unasjai
>aten'isai
to`uc
u<io`uc
>isra`hl
e>ic
t`o
pr'oswpon
mw\r{s}'ewc
\fn{\src{T|K}: mwsewc, \src{M|V}: mwusewc.}
di`a
t`hn
d'oxan
to~u
pros'wpou
a>uto~u
t`hn
katargoum'enhn\bibvsend
\vs 2Co 3:8
p~wc
o>uq`i
m~allon
<h
diakon'ia
to~u
pne'umatoc
>'estai
>en
d'oxh|\bibvsend
\vs 2Co 3:9
e>i
g`ar
<h\r{}
\fn{\src{TMK}: h, \src{V}: th.}
diakon'ia|
t~hc
katakr'isewc
d'oxa
poll~w|
m~allon
perisse'uei
<h
diakon'ia
t~hc
dikaios'unhc
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
d'oxh|\bibvsend
\vs 2Co 3:10
ka`i
g`ar
\r{o}>ud`e
\fn{\src{T|K}: oude, \src{M|V}: ou.}
ded'oxastai
t`o
dedoxasm'enon
>en
to'utw|
t~w|
m'erei
<'e\r{n}eken
\fn{\src{TMK}: eneken, \src{V}: eineken.}
t~hc
<uperballo'ushc
d'oxhc\bibvsend
\vs 2Co 3:11
e>i
g`ar
t`o
katargo'umenon
di`a
d'oxhc
poll~w|
m~allon
t`o
m'enon
>en
d'oxh|\bibvsend
\vs 2Co 3:12
>'eqontec
o>~un
toia'uthn
>elp'ida
poll~h|
parrhs'ia|
qr'wmeja\bibvsend
\vs 2Co 3:13
ka`i
o>u
kaj'aper
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
>et'ijei
k'alumma
>ep`i
t`o
pr'oswpon
<e\r{a}uto~u
\fn{\src{TMK}: eautou, \src{V}: autou.}
pr`oc
t`o
m`h
>aten'isai
to`uc
u<io`uc
>isra`hl
e>ic
t`o
t'eloc
to~u
katargoum'enou\bibvsend
\vs 2Co 3:14
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
>epwr'wjh
t`a
no'hmata
a>ut~wn
>'aqri
g`ar
t~hc
s'hmero\r{n}
\fn{\src{TMK}: shmeron, \src{V}: shmeron hmerac.}
t`o
a>ut`o
k'alumma
>ep`i
t~h|
>anagn'wsei
t~hc
palai~ac
diaj'hkhc
m'enei
m`h
>anakalupt'omenon
<'o\r{}
\fn{\src{T|K}: o ti, \src{M|V}: oti.}
ti
>en
qrist~w|
katarge~itai\bibvsend
\vs 2Co 3:15
>all>
<'ewc
s'hmeron
<hn'ika
>anagin'wsk\r{e}tai
\fn{\src{TMK}: anaginwsketai, \src{V}: an anaginwskhtai.}
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
k'alumma
>ep`i
t`hn
kard'ian
a>ut~wn
ke~itai\bibvsend
\vs 2Co 3:16
<hn'ika
d>\r{}
\fn{\src{TMK}: d an, \src{V}: de ean.}
>`an
>epistr'eyh|
pr`oc
k'urion
periaire~itai
t`o
k'alumma\bibvsend
\vs 2Co 3:17
<o
d`e
k'urioc
t`o
pne~um'a
>estin
o<~u
d`e
t`o
pne~uma
kur'iou
>e\r{k}e~i
\fn{\src{TMK}: ekei, \src{V}: \bibempty.}
>eleujer'ia\bibvsend
\vs 2Co 3:18
<hme~ic
d`e
p'antec
>anakekalumm'enw|
pros'wpw|
t`hn
d'oxan
kur'iou
katoptriz'omenoi
t`hn
a>ut`hn
e>ik'ona
metamorfo'umeja
>ap`o
d'oxhc
e>ic
d'oxan
kaj'aper
>ap`o
kur'iou
pne'umatoc\bibvsend
\vs 2Co 4:1
di`a
to~uto
>'eqontec
t`hn
diakon'ian
ta'uthn
kaj`wc
>hle'hjhmen
o>uk
>e\r{k}\-ka\-ko~u\-men\bibvsend
\fn{\src{TMK}: >ekkako~umen, \src{V}: egkakoumen.}
\vs 2Co 4:2
>al\r{l}>
\fn{\src{T|K}: >all>, \src{M|V}: alla.}
>apeip'ameja
t`a
krupt`a
t~hc
a>isq'unhc
m`h
peripato~untec
>en
panourg'ia|
mhd`e
dolo~untec
t`on
l'ogon
to~u
vjeo~u
>all`a
t~h|
vfaner'wsei
t~hc
>alhje'iac
sunist~wn\r{t}ec
\fn{\src{TMK}: sunistwntec, \src{V}: sunistanontec.}
<eauto`uc
pr`oc
p~asan
sune'idhsin
>anjr'wpwn
>en'wpion
to~u
vjeo~u\bibvsend
\vs 2Co 4:3
e>i
d`e
ka`i
>'estin
kekalumm'enon
t`o
e>uagg'elion
<hm~wn
>en
to~ic
>apollum'enoic
>est`in
kekalumm'enon\bibvsend
\vs 2Co 4:4
>en
o<~ic
<o
vje`oc
to~u
a>i~wnoc
to'utou
>et'uflwsen
t`a
no'hmata
t~wn
>ap'istwn
e>ic
t`o
m`h
a>ug'asai
a>u\r{t}o~ic
\fn{\src{TMK}: autoic, \src{V}: \bibempty.}
t`on
vfwtism`on
to~u
e>uaggel'iou
t~hc
d'oxhc
to~u
qristo~u
<'oc
>estin
e>ik`wn
to~u
vjeo~u\bibvsend
\vs 2Co 4:5
o>u
g`ar
<eauto`uc
khr'ussomen
>all`a
qrist`on\r{}
\fn{\src{TMK}: qriston ihsoun, \src{V}: ihsoun qriston.}
>ihso~un
k'urion
<eauto`uc
d`e
do'ulouc
<um~wn
di`a
>ihso~un\bibvsend
\vs 2Co 4:6
<'oti
<o
vje`oc
<o
e>ip`wn
>ek
sk'otouc
vf~wc
l'amy\r{a}i
\fn{\src{TMK}: lamyai, \src{V}: lamyei.}
<`oc
>'elamyen
>en
ta~ic
kard'iaic
<hm~wn
pr`oc
vfwtism`on
t~hc
gn'wsewc
t~hc
d'oxhc
to~u
vjeo~u
>en
pros'wpw|
>ihso~u
qristo~u\bibvsend
\vs 2Co 4:7
>'eqomen
d`e
t`on
vjhsaur`on
to~uton
>en
>ostrak'inoic
ske'uesin
<'ina
<h
<uperbol`h
t~hc
dun'amewc
>~h|
to~u
vjeo~u
ka`i
m`h
>ex
<hm~wn\bibvsend
\vs 2Co 4:8
>en
pant`i
vjlib'omenoi
>all>
o>u
stenoqwro'umenoi
>aporo'umenoi
>all>
o>uk
>exaporo'umenoi\bibvsend
\vs 2Co 4:9
diwk'omenoi
>all>
o>uk
>egkataleip'omenoi
kataball'omenoi
>all>
o>uk
>apoll'umenoi\bibvsend
\vs 2Co 4:10
p'antote
t`hn
n'ekrwsin
to~u
ku\r{r}'iou
\fn{\src{TMK}: kuriou, \src{V}: \bibempty.}
>ihso~u
>en
t~w|
s'wmati
perif'erontec
<'ina
ka`i
<h
vzw`h
to~u
>ihso~u
>en
t~w|
s'wmati
<hm~wn
vfanerwj~h|\bibvsend
\vs 2Co 4:11
>ae`i
g`ar
<hme~ic
o<i
vz~wntec
e>ic
vj'anaton
paradid'omeja
di`a
>ihso~un
<'ina
ka`i
<h
vzw`h
to~u
>ihso~u
vfanerwj~h|
>en
t~h|
vjnht~h|
sark`i
<hm~wn\bibvsend
\vs 2Co 4:12
<'wste
<o
\r{m}`en
\fn{\src{TMK}: men, \src{V}: \bibempty.}
vj'anatoc
>en
<hm~in
>energe~itai
<h
d`e
vzw`h
>en
<um~in\bibvsend
\vs 2Co 4:13
>'eqontec
d`e
t`o
a>ut`o
pne~uma
t~hc
p'istewc
kat`a
t`o
gegramm'enon
>ep'isteusa
di`o
>el'alhsa
ka`i
<hme~ic
piste'uomen
di`o
ka`i
lalo~umen\bibvsend
\vs 2Co 4:14
e>id'otec
<'oti
<o
>ege'irac
t`on
k'urion
>ihso~un
ka`i
<hm~ac
di`a\r{}
\fn{\src{TMK}: dia, \src{V}: sun.}
>ihso~u
>egere~i
ka`i
parast'hsei
s`un
<um~in\bibvsend
\vs 2Co 4:15
t`a
g`ar
p'anta
di>
<um~ac
<'ina
<h
q'aric
pleon'asasa
di`a
t~wn
plei'onwn
t`hn
e>uqarist'ian
perisse'ush|
e>ic
t`hn
d'oxan
to~u
vjeo~u\bibvsend
\vs 2Co 4:16
di`o
o>uk
>e\r{k}kako~umen
\fn{\src{TMK}: ekkakoumen, \src{V}: egkakoumen.}
>all>
e>i
ka`i
<o
>'exw
<hm~wn
>'anjrwpoc
diafje'iretai
>all>
<o
>'e\r{s}wjen
\fn{\src{TMK}: eswjen, \src{V}: esw hmwn.}
>anakaino~utai
<hm'era|
ka`i
<hm'era|\bibvsend
\vs 2Co 4:17
t`o
g`ar
paraut'ika
>elafr`on
t~hc
vjl'iyewc
<hm~wn
kaj>
<uperbol`hn
e>ic
<uperbol`hn
a>i'wnion
vb'aroc
d'oxhc
katerg'azetai
<hm~in\bibvsend
\vs 2Co 4:18
m`h
skopo'untwn
<hm~wn
t`a
vblep'omena
>all`a
t`a
m`h
vblep'omena
t`a
g`ar
vblep'omena
pr'oskaira
t`a
d`e
m`h
vblep'omena
a>i'wnia\bibvsend
\vs 2Co 5:1
o>'idamen
g`ar
<'oti
>e`an
<h
>ep'igeioc
<hm~wn
o>ik'ia
to~u
sk'hnouc
kataluj~h|
o>ikodom`hn
>ek
vjeo~u
>'eqomen
o>ik'ian
>aqeiropo'ihton
a>i'wnion
>en
to~ic
o>urano~ic\bibvsend
\vs 2Co 5:2
ka`i
g`ar
>en
to'utw|
sten'azomen
t`o
o>ikht'hrion
<hm~wn
t`o
>ex
o>urano~u
>epend'usasjai
>epipojo~untec\bibvsend
\vs 2Co 5:3
e>'i
ge
ka`i
>e\r{n}dus'amenoi
\fn{\src{TMK}: endusamenoi, \src{V}: ekdusamenoi.}
o>u
gumno`i
e<urejhs'omeja\bibvsend
\vs 2Co 5:4
ka`i
g`ar
o<i
>'ontec
>en
t~w|
sk'hnei
sten'azomen
vbaro'umenoi
>ep\r{e}id`h
\fn{\src{T}: epeidh, \src{K|M|V}: ef w.}
o>u
vj'elomen
>ekd'usasjai
>all>
>epend'usasjai
<'ina
katapoj~h|
t`o
vjnht`on
<up`o
t~hc
vzw~hc\bibvsend
\vs 2Co 5:5
<o
d`e
katergas'amenoc
<hm~ac
e>ic
a>ut`o
to~uto
vje`oc
<o
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
do`uc
<hm~in
t`on
>arrab~wna
to~u
pne'umatoc\bibvsend
\vs 2Co 5:6
vjarro~untec
o>~un
p'antote
ka`i
e>id'otec
<'oti
>endhmo~untec
>en
t~w|
s'wmati
>ekdhmo~umen
>ap`o
to~u
kur'iou\bibvsend
\vs 2Co 5:7
di`a
p'istewc
g`ar
peripato~umen
o>u
di`a
e>'idouc\bibvsend
\vs 2Co 5:8
vjarro~umen
d`e
ka`i
e>udoko~umen
m~allon
>ekdhm~hsai
>ek
to~u
s'wmatoc
ka`i
>endhm~hsai
pr`oc
t`on
k'urion\bibvsend
\vs 2Co 5:9
di`o
ka`i
vfilotimo'umeja
e>'ite
>endhmo~untec
e>'ite
>ekdhmo~untec
e>u'arestoi
a>ut~w|
e>~inai\bibvsend
\vs 2Co 5:10
to`uc
g`ar
p'antac
<hm~ac
vfanerwj~hnai
de~i
>'emprosjen
to~u
vb'hmatoc
to~u
qristo~u
<'ina
kom'ishtai
<'ekastoc
t`a
di`a
to~u
s'wmatoc
pr`oc
<`a
>'epraxen
e>'ite
>agaj`on
e>'ite
ka\r{k}'on\bibvsend
\fn{\src{TMK}: kakon, \src{V}: vfaulon.}
\vs 2Co 5:11
e>id'otec
o>~un
t`on
vf'obon
to~u
kur'iou
>anjr'wpouc
pe'ijomen
vje~w|
d`e
pefaner'wmeja
>elp'izw
d`e
ka`i
>en
ta~ic
suneid'hsesin
<um~wn
pefaner~wsjai\bibvsend
\vs 2Co 5:12
o>u
\r{g}`ar
\fn{\src{TMK}: gar, \src{V}: \bibempty.}
p'alin
<eauto`uc
sunist'anomen
<um~in
>all`a
>aform`hn
did'ontec
<um~in
kauq'hmatoc
<up`er
<hm~wn
<'ina
>'eqhte
pr`oc
to`uc
>en
pros'wpw|
kauqwm'enouc
ka`i
\r{o}>u
\fn{\src{TMK}: ou, \src{V}: mh en.}
kard'ia|\bibvsend
\vs 2Co 5:13
e>'ite
g`ar
>ex'esthmen
vje~w|
e>'ite
swfrono~umen
<um~in\bibvsend
\vs 2Co 5:14
<h
g`ar
>ag'aph
to~u
qristo~u
sun'eqei
<hm~ac
kr'inantac
to~uto
<'oti
\r{e}>i
\fn{\src{TMK}: ei, \src{V}: \bibempty.}
e<~ic
<up`er
p'antwn
>ap'ejanen
>'ara
o<i
p'antec
>ap'ejanon\bibvsend
\vs 2Co 5:15
ka`i
<up`er
p'antwn
>ap'ejanen
<'ina
o<i
vz~wntec
mhk'eti
<eauto~ic
vz~wsin
>all`a
t~w|
<up`er
a>ut~wn
>apojan'onti
ka`i
>egerj'enti\bibvsend
\vs 2Co 5:16
<'wste
<hme~ic
>ap`o
to~u
n~un
o>ud'ena
o>'idamen
kat`a
s'arka
e>i
d`e\r{}
\fn{\src{TMK}: de, \src{V}: \bibempty.}
ka`i
>egn'wkamen
kat`a
s'arka
qrist`on
>all`a
n~un
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
gin'wskomen\bibvsend
\vs 2Co 5:17
<'wste
e>'i
tic
>en
qrist~w|
kain`h
kt'isic
t`a
>arqa~ia
par~hljen
>ido`u
g'egonen
kain`a
t`a\r{}
\fn{\src{TMK}: ta panta, \src{V}: \bibempty.}
p'anta\bibvsend
\vs 2Co 5:18
t`a
d`e
p'anta
>ek
to~u
vjeo~u
to~u
katall'axantoc
<hm~ac
<eaut~w|
di`a
>ih\r{s}o~u
\fn{\src{TMK}: ihsou, \src{V}: \bibempty.}
qristo~u
ka`i
d'ontoc
<hm~in
t`hn
diakon'ian
t~hc
katallag~hc\bibvsend
\vs 2Co 5:19
<wc
<'oti
vje`oc
>~hn
>en
qrist~w|
k'osmon
katall'asswn
<eaut~w|
m`h
logiz'omenoc
a>uto~ic
t`a
parapt'wmata
a>ut~wn
ka`i
vj'emenoc
>en
<hm~in
t`on
l'ogon
t~hc
katallag~hc\bibvsend
\vs 2Co 5:20
<up`er
qristo~u
o>~un
presbe'uomen
<wc
to~u
vjeo~u
parakalo~untoc
di>
<hm~wn
de'omeja
<up`er
qristo~u
katall'aghte
t~w|
vje~w|\bibvsend
\vs 2Co 5:21
t`on
\r{g}`ar
\fn{\src{TMK}: gar, \src{V}: \bibempty.}
m`h
gn'onta
<amart'ian
<up`er
<hm~wn
<amart'ian
>epo'ihsen
<'ina
<hme~ic
gi\r{n}'wmeja
\fn{\src{T|K}: ginwmeja, \src{M|V}: genwmeja.}
dikaios'unh
vjeo~u
>en
a>ut~w|\bibvsend
\vs 2Co 6:1
sunergo~untec
d`e
ka`i
parakalo~umen
m`h
e>ic
ken`on
t`hn
q'arin
to~u
vjeo~u
d'exasjai
<um~ac\bibvsend
\vs 2Co 6:2
l'egei
g`ar
kair~w|
dekt~w|
>ep'hkous'a
sou
ka`i
>en
<hm'era|
swthr'iac
>ebo'hjhs'a
soi
>ido`u
n~un
kair`oc
e>upr'osdektoc
>ido`u
n~un
<hm'era
swthr'iac\bibvsend
\vs 2Co 6:3
mhdem'ian
>en
mhden`i
did'ontec
proskop`hn
<'ina
m`h
mwmhj~h|
<h
diakon'ia\bibvsend
\vs 2Co 6:4
>all>
>en
pant`i
suni\r{s}t~wntec
\fn{\src{TMK}: sunistwntec, \src{V}: sunistantec.}
<eauto`uc
<wc
vjeo~u
di'akonoi
>en
<upomon~h|
poll~h|
>en
vjl'iyesin
>en
>an'agkaic
>en
stenoqwr'iaic\bibvsend
\vs 2Co 6:5
>en
plhga~ic
>en
vfulaka~ic
>en
>akatastas'iaic
>en
k'opoic
>en
>agrupn'iaic
>en
nhste'iaic\bibvsend
\vs 2Co 6:6
>en
<agn'othti
>en
gn'wsei
>en
makrojum'ia|
>en
qrhst'othti
>en
pne'umati
<ag'iw|
>en
>ag'aph|
>anupokr'itw|\bibvsend
\vs 2Co 6:7
>en
l'ogw|
>alhje'iac
>en
dun'amei
vjeo~u
di`a
t~wn
<'oplwn
t~hc
dikaios'unhc
t~wn
dexi~wn
ka`i
>arister~wn\bibvsend
\vs 2Co 6:8
di`a
d'oxhc
ka`i
>atim'iac
di`a
dusfhm'iac
ka`i
e>ufhm'iac
<wc
pl'anoi
ka`i
>alhje~ic\bibvsend
\vs 2Co 6:9
<wc
>agnoo'umenoi
ka`i
>epiginwsk'omenoi
<wc
>apojn'hskontec
ka`i
>ido`u
vz~wmen
<wc
paideu'omenoi
ka`i
m`h
vjanato'umenoi\bibvsend
\vs 2Co 6:10
<wc
lupo'umenoi
>ae`i
d`e
qa'irontec
<wc
ptwqo`i
pollo`uc
d`e
plout'izontec
<wc
mhd`en
>'eqontec
ka`i
p'anta
kat'eqontec\bibvsend
\vs 2Co 6:11
t`o
st'oma
<hm~wn
>an'ew|gen
pr`oc
<um~ac
kor'injioi
<h
kard'ia
<hm~wn
pepl'atuntai\bibvsend
\vs 2Co 6:12
o>u
stenoqwre~isje
>en
<hm~in
stenoqwre~isje
d`e
>en
to~ic
spl'agqnoic
<um~wn\bibvsend
\vs 2Co 6:13
t`hn
d`e
a>ut`hn
>antimisj'ian
<wc
t'eknoic
l'egw
plat'unjhte
ka`i
<ume~ic\bibvsend
\vs 2Co 6:14
m`h
g'inesje
<eterozugo~untec
>ap'istoic
t'ic
g`ar
metoq`h
dikaios'unh|
ka`i
>anom'ia|
t'ic\r{}
\fn{\src{TMK}: tic de, \src{V}: h tic.}
d`e
koinwn'ia
vfwt`i
pr`oc
sk'otoc\bibvsend
\vs 2Co 6:15
t'ic
d`e
sumf'wnhsic
qris\r{t}~w|
\fn{\src{TMK}: qristw, \src{V}: qristou.}
pr`oc
vbel'ia\r{r}
\fn{\src{T|M|V}: vbeliar, \src{K}: vbelial.}
>`h
t'ic
mer`ic
pist~w|
met`a
>ap'istou\bibvsend
\vs 2Co 6:16
t'ic
d`e
sugkat'ajesic
na~w|
vjeo~u
met`a
e>id'wlwn
<u\r{m}e~ic
\fn{\src{TMK}: umeic, \src{V}: hmeic.}
g`ar
na`o\r{c}
\fn{\src{TMKVN}: naoc, \src{F}: naoi.}
vjeo~u
>es\r{t}e
\fn{\src{TMK}: este, \src{V}: esmen.}
vz~wntoc
kaj`wc
e>~ipen
<o
vje`oc
<'oti
>enoik'hsw
>en
a>uto~ic
ka`i
>emperipat'hsw
ka`i
>'esomai
a>ut~wn
vje`oc
ka`i
a>uto`i
>'esonta'i
m\r{o}i
\fn{\src{TMK}: moi, \src{V}: mou.}
la'oc\bibvsend
\vs 2Co 6:17
di`o
>ex'elj\r{e}te
\fn{\src{TMK}: exeljete, \src{V}: exeljate.}
>ek
m'esou
a>ut~wn
ka`i
>afor'isjhte
l'egei
k'urioc
ka`i
>akaj'artou
m`h
<'aptesje
k>ag`w
e>isd'exomai
<um~ac\bibvsend
\vs 2Co 6:18
ka`i
>'esomai
<um~in
e>ic
pat'era
ka`i
<ume~ic
>'esesj'e
moi
e>ic
u<io`uc
ka`i
vjugat'erac
l'egei
k'urioc
pantokr'atwr\bibvsend
\vs 2Co 7:1
ta'utac
o>~un
>'eqontec
t`ac
>epaggel'iac
>agaphto`i
kajar'iswmen
<eauto`uc
>ap`o
pant`oc
molusmo~u
sark`oc
ka`i
pne'umatoc
>epitelo~untec
<agiws'unhn
>en
vf'obw|
vjeo~u\bibvsend
\vs 2Co 7:2
qwr'hsate
<hm~ac
o>ud'ena
>hdik'hsamen
o>ud'ena
>efje'iramen
o>ud'ena
>epleonekt'hsamen\bibvsend
\vs 2Co 7:3
o>u\r{}
\fn{\src{TMK}: ou proc katakrisin, \src{V}: proc katakrisin ou.}
pr`oc
kat'akrisin
l'egw
proe'irhka
g`ar
<'oti
>en
ta~ic
kard'iaic
<hm~wn
>este
e>ic
t`o
sunapojane~in
ka`i
suz~h|n\bibvsend
\vs 2Co 7:4
poll'h
moi
parrhs'ia
pr`oc
<um~ac
poll'h
moi
ka'uqhsic
<up`er
<um~wn
pepl'hrwmai
t~h|
parakl'hsei
<uperperisse'uomai
t~h|
qar~a|
>ep`i
p'ash|
t~h|
vjl'iyei
<hm~wn\bibvsend
\vs 2Co 7:5
ka`i
g`ar
>elj'ontwn
<hm~wn
e>ic
makedon'ian
o>udem'ian
>'esqhken
>'anesin
<h
s`arx
<hm~wn
>all>
>en
pant`i
vjlib'omenoi
>'exwjen
m'aqai
>'eswjen
vf'oboi\bibvsend
\vs 2Co 7:6
>all>
<o
parakal~wn
to`uc
tapeino`uc
parek'alesen
<hm~ac
<o
vje`oc
>en
t~h|
parous'ia|
t'itou\bibvsend
\vs 2Co 7:7
o>u
m'onon
d`e
>en
t~h|
parous'ia|
a>uto~u
>all`a
ka`i
>en
t~h|
parakl'hsei
<~h|
parekl'hjh
>ef>
<um~in
>anagg'ellwn
<hm~in
t`hn
<um~wn
>epip'ojhsin
t`on
<um~wn
>odurm`on
t`on
<um~wn
vz~hlon
<up`er
>emo~u
<'wste
me
m~allon
qar~hnai\bibvsend
\vs 2Co 7:8
<'oti
e>i
ka`i
>el'uphsa
<um~ac
>en
t~h|
>epistol~h|
o>u
metam'elomai
e>i
ka`i
metemel'omhn
vbl'epw
g`ar
<'oti
<h
>epistol`h
>eke'inh
e>i
ka`i
pr`oc
<'wran
>el'uphsen
<um~ac\bibvsend
\vs 2Co 7:9
n~un
qa'irw
o>uq
<'oti
>elup'hjhte
>all>
<'oti
>elup'hjhte
e>ic
met'anoian
>elup'hjhte
g`ar
kat`a
vje`on
<'ina
>en
mhden`i
vzhmiwj~hte
>ex
<hm~wn\bibvsend
\vs 2Co 7:10
<h
g`ar
kat`a
vje`on
l'uph
met'anoian
e>ic
swthr'ian
>ametam'elhton
\r{k}aterg'azetai
\fn{\src{TMK}: katergazetai, \src{V}: ergazetai.}
<h
d`e
to~u
k'osmou
l'uph
vj'anaton
kat>erg'azetai\bibvsend
\vs 2Co 7:11
>ido`u
g`ar
a>ut`o
to~uto
t`o
kat`a
vje`on
luphj~hnai
<u\r{m}~ac
\fn{\src{TMK}: umac, \src{V}: \bibempty.}
p'oshn
kateirg'asato
<um~in
spoud`hn
>all`a
>apolog'ian
>all`a
>agan'akthsin
>all`a
vf'obon
>all`a
>epip'ojhsin
>all`a
vz~hlon
>al\r{l}>
\fn{\src{T|K}: all, \src{M|V}: alla.}
>ekd'ikhsin
>en
pant`i
sunest'hsate
<eauto`uc
<agno`uc
e>~inai
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
t~w|
pr'agmati\bibvsend
\vs 2Co 7:12
>'ara
e>i
ka`i
>'egraya
<um~in
o>uq
e<'i\r{n}eken
\fn{\src{TMK}: eineken, \src{V}: eneken.}
to~u
>adik'hsantoc
o>ud`e
e<'i\r{n}eken
to~u
>adikhj'entoc
>all>
e<'i\r{n}eken
to~u
vfanerwj~hnai
t`hn
spoud`hn
<um~wn\r{}
\fn{\src{T|M|V}: umwn thn uper hmwn, \src{K}: hmwn thn uper umwn.}
t`hn
<up`er
<hm~wn
pr`oc
<um~ac
>en'wpion
to~u
vjeo~u\bibvsend
\vs 2Co 7:13
di`a
to~uto
parakekl'hmeja
>e\r{p}`i
\fn{\src{T|K}: epi, \src{M|V}: epi de.}
t~h|
parakl'hsei
<um~wn\r{}
\fn{\src{T|K}: umwn perissoterwc de, \src{M}: umwn perissoterwc, \src{V}: hmwn perissoterwc.}
perissot'erwc
d`e
m~allon
>eq'arhmen
>ep`i
t~h|
qar~a|
t'itou
<'oti
>anap'epautai
t`o
pne~uma
a>uto~u
>ap`o
p'antwn
<um~wn\bibvsend
\vs 2Co 7:14
<'oti
e>'i
ti
a>ut~w|
<up`er
<um~wn
keka'uqhmai
o>u
kath|sq'unjhn
>all>
<wc
p'anta
>en
>alhje'ia|
>elal'hsamen
<um~in
o<'utwc
ka`i
<h
ka'uqhsic
<hm~wn
<h
>ep`i
t'itou
>al'hjeia
>egen'hjh\bibvsend
\vs 2Co 7:15
ka`i
t`a
spl'agqna
a>uto~u
perissot'erwc
e>ic
<um~ac
>estin
>anamimnhskom'enou
t`hn
p'antwn
<um~wn
<upako`hn
<wc
met`a
vf'obou
ka`i
tr'omou
>ed'exasje
a>ut'on\bibvsend
\vs 2Co 7:16
qa'ir\r{w}
\fn{\src{T|M|V}: qairw, \src{K}: qairw oun.}
<'oti
>en
pant`i
vjarr~w
>en
<um~in\bibvsend
\vs 2Co 8:1
gnwr'izomen
d`e
<um~in
>adelfo`i
t`hn
q'arin
to~u
vjeo~u
t`hn
dedom'enhn
>en
ta~ic
>ekklhs'iaic
t~hc
makedon'iac\bibvsend
\vs 2Co 8:2
<'oti
>en
poll~h|
dokim~h|
vjl'iyewc
<h
perisse'ia
t~hc
qar~ac
a>ut~wn
ka`i
<h
kat`a
vb'ajouc
ptwqe'ia
a>ut~wn
>eper'isseusen
e>ic
t`on\r{}
\fn{\src{TMK}: ton plouton, \src{V}: to ploutoc.}
plo~uton
t~hc
<apl'othtoc
a>ut~wn\bibvsend
\vs 2Co 8:3
<'oti
kat`a
d'unamin
martur~w
ka`i
<u\r{p}`er
\fn{\src{TMK}: uper, \src{V}: para.}
d'unamin
a>uja'iretoi\bibvsend
\vs 2Co 8:4
met`a
poll~hc
parakl'hsewc
de'omenoi
<hm~wn
t`hn
q'arin
ka`i
t`hn
koinwn'ian
t~hc
diakon'iac
t~hc
e>ic
to`uc
<ag'iouc
d'exasjai\r{}
\fn{\src{T|K}: dexasjai hmac, \src{M|V}: \bibempty.}
<hm~ac\bibvsend
\vs 2Co 8:5
ka`i
o>u
kaj`wc
>hlp'isamen
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<eauto`uc
>'edwkan
pr~wton
t~w|
kur'iw|
ka`i
<hm~in
di`a
vjel'hmatoc
vjeo~u\bibvsend
\vs 2Co 8:6
e>ic
t`o
parakal'esai
<hm~ac
t'iton
<'ina
kaj`wc
proen'hrxato
o<'utwc
ka`i
>epitel'esh|
e>ic
<um~ac
ka`i
t`hn
q'arin
ta'uthn\bibvsend
\vs 2Co 8:7
>all>
<'wsper
>en
pant`i
perisse'uete
p'istei
ka`i
l'ogw|
ka`i
gn'wsei
ka`i
p'ash|
spoud~h|
ka`i
t~h|
>ex
<um~wn\r{}
\fn{\src{TMK}: umwn en hmin, \src{V}: hmwn en umin.}
>en
<hm~in
>ag'aph|
<'ina
ka`i
>en
ta'uth|
t~h|
q'ariti
perisse'uhte\bibvsend
\vs 2Co 8:8
o>u
kat>
>epitag`hn
l'egw
>all`a
di`a
t~hc
<et'erwn
spoud~hc
ka`i
t`o
t~hc
<umet'erac
>ag'aphc
gn'hsion
dokim'azwn\bibvsend
\vs 2Co 8:9
gin'wskete
g`ar
t`hn
q'arin
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
<'oti
di>
<um~ac
>ept'wqeusen
plo'usioc
>`wn
<'ina
<ume~ic
t~h|
>eke'inou
ptwqe'ia|
plout'hshte\bibvsend
\vs 2Co 8:10
ka`i
gn'wmhn
>en
to'utw|
d'idwmi
to~uto
g`ar
<um~in
sumf'erei
o<'itinec
o>u
m'onon
t`o
poi~hsai
>all`a
ka`i
t`o
vj'elein
proen'hrxasje
>ap`o
p'erusi\bibvsend
\vs 2Co 8:11
nun`i
d`e
ka`i
t`o
poi~hsai
>epitel'esate
<'opwc
kaj'aper
<h
projum'ia
to~u
vj'elein
o<'utwc
ka`i
t`o
>epitel'esai
>ek
to~u
>'eqein\bibvsend
\vs 2Co 8:12
e>i
g`ar
<h
projum'ia
pr'okeitai
kaj`o
>e`an
>'eqh|
\r{t}ic
\fn{\src{TMK}: tic, \src{V}: \bibempty.}
e>upr'osdektoc
o>u
kaj`o
o>uk
>'eqei\bibvsend
\vs 2Co 8:13
o>u
g`ar
<'ina
>'alloic
>'anesic
<um~in
d`e\r{}
\fn{\src{TMK}: de, \src{V}: \bibempty.}
vjl'iyic
>all>
>ex
>is'othtoc
>en
t~w|
n~un
kair~w|
t`o
<um~wn
per'isseuma
e>ic
t`o
>eke'inwn
<ust'erhma\bibvsend
\vs 2Co 8:14
<'ina
ka`i
t`o
>eke'inwn
per'isseuma
g'enhtai
e>ic
t`o
<um~wn
<ust'erhma
<'opwc
g'enhtai
>is'othc\bibvsend
\vs 2Co 8:15
kaj`wc
g'egraptai
<o
t`o
pol`u
o>uk
>eple'onasen
ka`i
<o
t`o
>ol'igon
o>uk
>hlatt'onhsen\bibvsend
\vs 2Co 8:16
q'aric
d`e
t~w|
vje~w|
t~w|
did'o\r{n}ti
\fn{\src{TMK}: didonti, \src{V}: donti.}
t`hn
a>ut`hn
spoud`hn
<up`er
<um~wn
>en
t~h|
kard'ia|
t'itou\bibvsend
\vs 2Co 8:17
<'oti
t`hn
m`en
par'aklhsin
>ed'exato
spoudai'oteroc
d`e
<up'arqwn
a>uja'iretoc
>ex~hljen
pr`oc
<um~ac\bibvsend
\vs 2Co 8:18
sunep'emyamen
d`e
met>
a>uto~u
t`on
>adelf`on
o<~u
<o
>'epainoc
>en
t~w|
e>uaggel'iw|
di`a
pas~wn
t~wn
>ekklhsi~wn\bibvsend
\vs 2Co 8:19
o>u
m'onon
d`e
>all`a
ka`i
qeirotonhje`ic
<up`o
t~wn
>ekklhsi~wn
sun'ekdhmoc
<hm~wn
s`un
t~h|
q'ariti
ta'uth|
t~h|
diakonoum'enh|
<uf>
<hm~wn
pr`oc
t`hn
a>uto~u
to~u
kur'iou
d'oxan
ka`i
projum'ian
<u\r{m}~wn\bibvsend
\fn{\src{T|K}: umwn, \src{M|V}: hmwn.}
\vs 2Co 8:20
stell'omenoi
to~uto
m'h
tic
<hm~ac
mwm'hshtai
>en
t~h|
<adr'othti
ta'uth|
t~h|
diakonoum'enh|
<uf>
<hm~wn\bibvsend
\vs 2Co 8:21
pronoo'umenoi\r{}
\fn{\src{TMK}: pronooumenoi, \src{V}: pronooumen gar.}
kal`a
o>u
m'onon
>en'wpion
kur'iou
>all`a
ka`i
>en'wpion
>anjr'wpwn\bibvsend
\vs 2Co 8:22
sunep'emyamen
d`e
a>uto~ic
t`on
>adelf`on
<hm~wn
<`on
>edokim'asamen
>en
pollo~ic
poll'akic
spouda~ion
>'onta
nun`i
d`e
pol`u
spoudai'oteron
pepoij'hsei
poll~h|
t~h|
e>ic
<um~ac\bibvsend
\vs 2Co 8:23
e>'ite
<up`er
t'itou
koinwn`oc
>em`oc
ka`i
e>ic
<um~ac
sunerg`oc
e>'ite
>adelfo`i
<hm~wn
>ap'ostoloi
>ekklhsi~wn
d'oxa
qristo~u\bibvsend
\vs 2Co 8:24
t`hn
o>~un
>'endeixin
t~hc
>ag'aphc
<um~wn
ka`i
<hm~wn
kauq'hsewc
<up`er
<um~wn
e>ic
a>uto`uc
>ende'ixasje\r{}
\fn{\src{T|K}: endeixasje kai, \src{M}: endeixasje, \src{V}: endeiknumenoi.}
ka`i
e>ic
pr'oswpon
t~wn
>ekklhsi~wn\bibvsend
\vs 2Co 9:1
per`i
m`en
g`ar
t~hc
diakon'iac
t~hc
e>ic
to`uc
<ag'iouc
periss'on
mo'i
>estin
t`o
gr'afein
<um~in\bibvsend
\vs 2Co 9:2
o>~ida
g`ar
t`hn
projum'ian
<um~wn
<`hn
<up`er
<um~wn
kauq~wmai
maked'osin
<'oti
>aqa"'ia
pareske'uastai
>ap`o
p'erusi
ka`i
<o\r{}
\fn{\src{TMK}: o ex, \src{V}: to.}
>ex
<um~wn
vz~hloc
>hr'ejisen
to`uc
ple'ionac\bibvsend
\vs 2Co 9:3
>'epemya
d`e
to`uc
>adelfo`uc
<'ina
m`h
t`o
ka'uqhma
<hm~wn
t`o
<up`er
<um~wn
kenwj~h|
>en
t~w|
m'erei
to'utw|
<'ina
kaj`wc
>'elegon
pareskeuasm'enoi
>~hte\bibvsend
\vs 2Co 9:4
m'h
pwc
>e`an
>'eljwsin
s`un
>emo`i
maked'onec
ka`i
e<'urwsin
<um~ac
>aparaskeu'astouc
kataisqunj~wmen
<hme~ic
<'ina
m`h
l'egw\r{m}en
\fn{\src{TMK}: legwmen, \src{V}: legw.}
<ume~ic
>en
t~h|
<upost'asei
ta'uth|
t~hc\r{}
\fn{\src{TMK}: thc kauqhsewc, \src{V}: \bibempty.}
kauq'hsewc\bibvsend
\vs 2Co 9:5
>anagka~ion
o>~un
<hghs'amhn
parakal'esai
to`uc
>adelfo`uc
<'ina
pro'eljwsin
e>ic
<um~ac
ka`i
prokatart'iswsin
t`hn
pro\r{k}athggelm'enhn
\fn{\src{TMK}: prokathggelmenhn, \src{V}: proephggelmenhn.}
e>ulog'ian
<um~wn
ta'uthn
<eto'imhn
e>~inai
o<'utwc
<wc
e>ulog'ian
ka`i
m`h
<'ws\r{p}er
\fn{\src{T|K}: wsper, \src{M|V}: wc.}
pleonex'ian\bibvsend
\vs 2Co 9:6
to~uto
d`e
<o
spe'irwn
vfeidom'enwc
vfeidom'enwc
ka`i
vjer'isei
ka`i
<o
spe'irwn
>ep>
e>ulog'iaic
>ep>
e>ulog'iaic
ka`i
vjer'isei\bibvsend
\vs 2Co 9:7
<'ekastoc
kaj`wc
pro\r{a}ire~itai
\fn{\src{TMK}: proaireitai, \src{V}: prohrhtai.}
t~h|
kard'ia|
m`h
>ek
l'uphc
>`h
>ex
>an'agkhc
<ilar`on
g`ar
d'othn
>agap~a|
<o
vje'oc\bibvsend
\vs 2Co 9:8
dunat`o\r{c}
\fn{\src{TMK}: dunatoc, \src{V}: dunatei.}
d`e
<o
vje`oc
p~asan
q'arin
perisse~usai
e>ic
<um~ac
<'ina
>en
pant`i
p'antote
p~asan
a>ut'arkeian
>'eqontec
perisse'uhte
e>ic
p~an
>'ergon
>agaj'on\bibvsend
\vs 2Co 9:9
kaj`wc
g'egraptai
>esk'orpisen
>'edwken
to~ic
p'enhsin
<h
dikaios'unh
a>uto~u
m'enei
e>ic
t`on
a>i~wna\bibvsend
\vs 2Co 9:10
<o
d`e
>epiqorhg~wn
sp'er\r{m}a
\fn{\src{TMK}: sperma, \src{V}: sporon.}
t~w|
spe'ironti
ka`i
>'arton
e>ic
vbr~wsin
qorhg'hsai\r{}
\fn{\src{TMK}: qorhghsai kai plhjunai, \src{V}: qorhghsei kai plhjunei.}
ka`i
plhj'unai
t`on
sp'oron
<um~wn
ka`i
a>ux'hs\r{a}i
\fn{\src{TMK}: auxhsai, \src{V}: auxhsei.}
t`a
ge\r{n}n'hmata
\fn{\src{T|K}: gennhmata, \src{M|V}: genhmata.}
t~hc
dikaios'unhc
<um~wn\bibvsend
\vs 2Co 9:11
>en
pant`i
ploutiz'omenoi
e>ic
p~asan
<apl'othta
<'htic
katerg'azetai
di>
<hm~wn
e>uqarist'ian
t~w|
vje~w|\bibvsend
\vs 2Co 9:12
<'oti
<h
diakon'ia
t~hc
leitourg'iac
ta'uthc
o>u
m'onon
>est`in
prosanaplhro~usa
t`a
<uster'hmata
t~wn
<ag'iwn
>all`a
ka`i
perisse'uousa
di`a
poll~wn
e>uqaristi~wn
t~w|
vje~w|\bibvsend
\vs 2Co 9:13
di`a
t~hc
dokim~hc
t~hc
diakon'iac
ta'uthc
dox'azontec
t`on
vje`on
>ep`i
t~h|
<upotag~h|
t~hc
<omolog'iac
<um~wn
e>ic
t`o
e>uagg'elion
to~u
qristo~u
ka`i
<apl'othti
t~hc
koinwn'iac
e>ic
a>uto`uc
ka`i
e>ic
p'antac\bibvsend
\vs 2Co 9:14
ka`i
a>ut~wn
de'hsei
<up`er
<um~wn
>epipojo'untwn
<um~ac
di`a
t`hn
<uperb'allousan
q'arin
to~u
vjeo~u
>ef>
<um~in\bibvsend
\vs 2Co 9:15
q'aric
d`e\r{}
\fn{\src{TMK}: de, \src{V}: \bibempty.}
t~w|
vje~w|
>ep`i
t~h|
>anekdihg'htw|
a>uto~u
dwre~a|\bibvsend
\vs 2Co 10:1
a>ut`oc
d`e
>eg`w
pa~uloc
parakal~w
<um~ac
di`a
t~hc
p\r{r}a|\-'oth\-toc
\fn{\src{TMK}: praothtoc, \src{V}: prauthtoc.}
ka`i
>epieike'iac
to~u
qristo~u
<`oc
kat`a
pr'oswpon
m`en
tapein`oc
>en
<um~in
>ap`wn
d`e
vjarr~w
e>ic
<um~ac\bibvsend
\vs 2Co 10:2
d'eomai
d`e
t`o
m`h
par`wn
vjarr~hsai
t~h|
pepoij'hsei
<~h|
log'izomai
tolm~hsai
>ep'i
tinac
to`uc
logizom'enouc
<hm~ac
<wc
kat`a
s'arka
peripato~untac\bibvsend
\vs 2Co 10:3
>en
sark`i
g`ar
peripato~untec
o>u
kat`a
s'arka
strateu'omeja\bibvsend
\vs 2Co 10:4
t`a
g`ar
<'opla
t~hc
strate'iac
<hm~wn
o>u
sarkik`a
>all`a
dunat`a
t~w|
vje~w|
pr`oc
kaja'iresin
>oqurwm'atwn\bibvsend
\vs 2Co 10:5
logismo`uc
kajairo~untec
ka`i
p~an
<'uywma
>epair'omenon
kat`a
t~hc
gn'wsewc
to~u
vjeo~u
ka`i
a>iqmalwt'izontec
p~an
n'ohma
e>ic
t`hn
<upako`hn
to~u
qristo~u\bibvsend
\vs 2Co 10:6
ka`i
>en
<eto'imw|
>'eqontec
>ekdik~hsai
p~asan
parako`hn
<'otan
plhrwj~h|
<um~wn
<h
<upako'h\bibvsend
\vs 2Co 10:7
t`a
kat`a
pr'oswpon
vbl'epete
e>'i
tic
p'epoijen
<eaut~w|
qristo~u
e>~inai
to~uto
logiz'esjw
p'alin
>a\r{f}>
\fn{\src{TMK}: af, \src{V}: ef.}
<eauto~u
<'oti
kaj`wc
a>ut`oc
qristo~u
o<'utwc
ka`i
<hme~ic
qri\r{s}to~u\bibvsend
\fn{\src{TMK}: qristou, \src{V}: \bibempty.}
\vs 2Co 10:8
>e'an
te
g`ar
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
periss'oter'on
ti
kauq'hswmai
per`i
t~hc
>exous'iac
<hm~wn
<~hc
>'edwken
<o
k'urioc
<h\r{m}~in
\fn{\src{TMK}: hmin, \src{V}: \bibempty.}
e>ic
o>ikodom`hn
ka`i
o>uk
e>ic
kaja'iresin
<um~wn
o>uk
a>isqunj'hsomai\bibvsend
\vs 2Co 10:9
<'ina
m`h
d'oxw
<wc
>`an
>ekfobe~in
<um~ac
di`a
t~wn
>epistol~wn\bibvsend
\vs 2Co 10:10
<'oti
a<i
m`en\r{}
\fn{\src{TMK}: men epistolai, \src{V}: epistolai men.}
>epistola`i
vfhs`in
vbare~iai
ka`i
>isqura`i
<h
d`e
parous'ia
to~u
s'wmatoc
>asjen`hc
ka`i
<o
l'ogoc
>exoujenhm'enoc\bibvsend
\vs 2Co 10:11
to~uto
logiz'esjw
<o
toio~utoc
<'oti
o<~io'i
>esmen
t~w|
l'ogw|
di>
>epistol~wn
>ap'ontec
toio~utoi
ka`i
par'ontec
t~w|
>'ergw|\bibvsend
\vs 2Co 10:12
o>u
g`ar
tolm~wmen
>egkr~inai
>`h
sugkr~inai
<eauto'uc
tisin
t~wn
<eauto`uc
sunistan'ontwn
>all`a
a>uto`i
>en
<eauto~ic
<eauto`uc
metro~untec
ka`i
sugkr'inontec
<eauto`uc
<eauto~ic
o>u
suni\r{o}~usin\bibvsend
\fn{\src{TMK}: suniousin, \src{V}: suniasin.}
\vs 2Co 10:13
<hme~ic
d`e
o>u\r{q}`i
\fn{\src{TMK}: ouqi, \src{V}: ouk.}
e>ic
t`a
>'ametra
kauqhs'omeja
>all`a
kat`a
t`o
m'etron
to~u
kan'onoc
o<~u
>em'erisen
<hm~in
<o
vje`oc
m'etrou
>efik'esjai
>'aqri
ka`i
<um~wn\bibvsend
\vs 2Co 10:14
o>u
g`ar
<wc
m`h
>efikno'umenoi
e>ic
<um~ac
<uperekte'inomen
<eauto`uc
>'aqri
g`ar
ka`i
<um~wn
>efj'asamen
>en
t~w|
e>uaggel'iw|
to~u
qristo~u\bibvsend
\vs 2Co 10:15
o>uk
e>ic
t`a
>'ametra
kauq'wmenoi
>en
>allotr'ioic
k'opoic
>elp'ida
d`e
>'eqontec
a>uxanom'enhc
t~hc
p'istewc
<um~wn
>en
<um~in
megalunj~hnai
kat`a
t`on
kan'ona
<hm~wn
e>ic
perisse'ian\bibvsend
\vs 2Co 10:16
e>ic
t`a
<uper'ekeina
<um~wn
e>uaggel'isasjai
o>uk
>en
>allotr'iw|
kan'oni
e>ic
t`a
<'etoima
kauq'hsasjai\bibvsend
\vs 2Co 10:17
<o
d`e
kauq'wmenoc
>en
kur'iw|
kauq'asjw\bibvsend
\vs 2Co 10:18
o>u
g`ar
<o
<eaut`on
sunis\r{t}~wn
\fn{\src{TMK}: sunistwn, \src{V}: sunistanwn.}
>eke~in'oc
>estin
d'okimoc
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<`on
<o
k'urioc
sun'isthsin\bibvsend
\vs 2Co 11:1
>'ofelon
>ane'iqesj'e
mou
mikr`on
t~h|\r{}
\fn{\src{TMK}: th afrosunh, \src{V}: ti afrosunhc.}
>afros'unh|
>all`a
ka`i
>an'eqesj'e
mou\bibvsend
\vs 2Co 11:2
vzhl~w
g`ar
<um~ac
vjeo~u
vz'hlw|
<hrmos'amhn
g`ar
<um~ac
<en`i
>andr`i
parj'enon
<agn`hn
parast~hsai
t~w|
qrist~w|\bibvsend
\vs 2Co 11:3
vfobo~umai
d`e
m'h
pwc
<wc
<o
>'ofic
e>'uan\r{}
\fn{\src{TMK}: euan exhpathsen, \src{V}: exhpathsen euan.}
>exhp'athsen
>en
t~h|
panourg'ia|
a>uto~u
o<'u\r{t}wc
\fn{\src{TMK}: outwc, \src{V}: \bibempty.}
vfjar~h|
t`a
no'hmata
<um~wn
>ap`o
t~hc
<apl'othto\r{c}
\fn{\src{TMK}: aplothtoc, \src{V}: aplothtoc [kai thc agnothtoc].}
t~hc
e>ic
t`on
qrist'on\bibvsend
\vs 2Co 11:4
e>i
m`en
g`ar
<o
>erq'omenoc
>'allon
>ihso~un
khr'ussei
<`on
o>uk
>ekhr'uxamen
>`h
pne~uma
<'eteron
lamb'anete
<`o
o>uk
>el'abete
>`h
e>uagg'elion
<'eteron
<`o
o>uk
>ed'exasje
kal~wc
>h\r{n}e'iqesje\bibvsend
\fn{\src{T|K}: hneiqesje, \src{M}: aneiqesje, \src{V}: aneqesje.}
\vs 2Co 11:5
log'izomai
g`ar
mhd`en
<usterhk'enai
t~wn
<up`er\r{}
\fn{\src{TMK}: uper lian, \src{V}: uperlian.}
l'ian
>apost'olwn\bibvsend
\vs 2Co 11:6
e>i
d`e
ka`i
>idi'wthc
t~w|
l'ogw|
>all>
o>u
t~h|
gn'wsei
>all>
>en
pant`i
vfaner\r{w}j'entec
\fn{\src{TMK}: vfanerwjentec, \src{V}: vfanerwsantec.}
>en
p~asin
e>ic
<um~ac\bibvsend
\vs 2Co 11:7
>`h
<amart'ian
>epo'ihsa
>emaut`on
tapein~wn
<'ina
<ume~ic
<uywj~hte
<'oti
dwre`an
t`o
to~u
vjeo~u
e>uagg'elion
e>uhggelis'amhn
<um~in\bibvsend
\vs 2Co 11:8
>'allac
>ekklhs'iac
>es'ulhsa
lab`wn
>oy'wnion
pr`oc
t`hn
<um~wn
diakon'ian\bibvsend
\vs 2Co 11:9
ka`i
par`wn
pr`oc
<um~ac
ka`i
<usterhje`ic
o>u
katen'arkhsa
o>ud\r{e}n`oc
\fn{\src{TMK}: oudenoc, \src{V}: oujenoc.}
t`o
g`ar
<ust'erhm'a
mou
prosanepl'hrwsan
o<i
>adelfo`i
>elj'ontec
>ap`o
makedon'iac
ka`i
>en
pant`i
>abar~h
<um~in\r{}
\fn{\src{TMK}: umin emauton, \src{V}: emauton umin.}
>emaut`on
>et'hrhsa
ka`i
thr'hsw\bibvsend
\vs 2Co 11:10
>'estin
>al'hjeia
qristo~u
>en
>emo`i
<'oti
<h
ka'uqhsic
a<'uth
o>u
\r{s}frag'isetai
\fn{\src{T}: sfragisetai, \src{K|M|V}: vfraghsetai.}
e>ic
>em`e
>en
to~ic
kl'imasin
t~hc
>aqa"'iac\bibvsend
\vs 2Co 11:11
dia\r{t}`i
\fn{\src{T|K}: diati, \src{M|V}: dia ti.}
<'oti
o>uk
>agap~w
<um~ac
<o
vje`oc
o>~iden\bibvsend
\vs 2Co 11:12
<`o
d`e
poi~w
ka`i
poi'hsw
<'ina
>ekk'oyw
t`hn
>aform`hn
t~wn
vjel'ontwn
>aform`hn
<'ina
>en
<~w|
kauq~wntai
e<urej~wsin
kaj`wc
ka`i
<hme~ic\bibvsend
\vs 2Co 11:13
o<i
g`ar
toio~utoi
yeudap'ostoloi
>erg'atai
d'olioi
metasqhmatiz'omenoi
e>ic
>apost'olouc
qristo~u\bibvsend
\vs 2Co 11:14
ka`i
o>u
vjauma\r{s}t`on
\fn{\src{TMK}: vjaumaston, \src{V}: vjauma.}
a>ut`oc
g`ar
<o
satan~ac
metasqhmat'izetai
e>ic
>'aggelon
vfwt'oc\bibvsend
\vs 2Co 11:15
o>u
m'ega
o>~un
e>i
ka`i
o<i
di'akonoi
a>uto~u
metasqhmat'izontai
<wc
di'akonoi
dikaios'unhc
<~wn
t`o
t'eloc
>'estai
kat`a
t`a
>'erga
a>ut~wn\bibvsend
\vs 2Co 11:16
p'alin
l'egw
m'h
t'ic
me
d'oxh|
>'afrona
e>~inai
e>i
d`e
m'h
ge
k>`an
<wc
>'afrona
d'exasj'e
me
<'ina
mikr'on\r{}
\fn{\src{T|K}: mikron ti kagw, \src{M|V}: kagw mikron ti.}
ti
k>ag`w
kauq'hswmai\bibvsend
\vs 2Co 11:17
<`o
lal~w
o>u
lal~w\r{}
\fn{\src{TMK}: lalw kata kurion, \src{V}: kata kurion lalw.}
kat`a
k'urion
>all>
<wc
>en
>afros'unh|
>en
ta'uth|
t~h|
<upost'asei
t~hc
kauq'hsewc\bibvsend
\vs 2Co 11:18
>epe`i
pollo`i
kauq~wntai
kat`a
\r{t}`hn
\fn{\src{TMK}: thn, \src{V}: \bibempty.}
s'arka
k>ag`w
kauq'hsomai\bibvsend
\vs 2Co 11:19
<hd'ewc
g`ar
>an'eqesje
t~wn
>afr'onwn
vfr'onimoi
>'ontec\bibvsend
\vs 2Co 11:20
>an'eqesje
g`ar
e>'i
tic
<um~ac
katadoulo~i
e>'i
tic
katesj'iei
e>'i
tic
lamb'anei
e>'i
tic
>epa'iretai
e>'i
tic
<um~ac\r{}
\fn{\src{TMK}: umac eic proswpon, \src{V}: eic proswpon umac.}
e>ic
pr'oswpon
d'erei\bibvsend
\vs 2Co 11:21
kat`a
>atim'ian
l'egw
<wc
<'oti
<hme~ic
>hsjen'h\r{s}amen
\fn{\src{TMK}: hsjenhsamen, \src{V}: hsjenhkamen.}
>en
<~w|
d>
>'an
tic
tolm~a|
>en
>afros'unh|
l'egw
tolm~w
k>ag'w\bibvsend
\vs 2Co 11:22
<ebra~io'i
e>isin
k>ag`w
>israhl~ita'i
e>isin
k>ag`w
sp'erma
>abra'am
e>isin
k>ag'w\bibvsend
\vs 2Co 11:23
di'akonoi
qristo~u
e>isin
parafron~wn
lal~w
<up`er
>eg`w
>en
k'opoic
perissot'erwc
>en
plhga~ic\r{}
\fn{\src{TMK}: plhgaic uperballontwc en vfulakaic perissoterwc, \src{V}: vfulakaic perissoterwc en plhgaic uperballontwc.}
<uperball'ontwc
>en
vfulaka~ic
perissot'erwc
>en
vjan'atoic
poll'akic\bibvsend
\vs 2Co 11:24
<up`o
>iouda'iwn
pent'akic
tess\r{a}r'akonta
\fn{\src{TMK}: tessarakonta, \src{V}: tesserakonta.}
par`a
m'ian
>'elabon\bibvsend
\vs 2Co 11:25
tr`ic
>er\r{r}abd'isjhn
\fn{\src{T|K|V}: errabdisjhn, \src{M}: erabdisjhn.}
<'apax
>elij'asjhn
tr`ic
>enau'aghsa
nuqj'hmeron
>en
t~w|
vbuj~w|
pepo'ihka\bibvsend
\vs 2Co 11:26
<odoipor'iaic
poll'akic
kind'unoic
potam~wn
kind'unoic
lh|st~wn
kind'unoic
>ek
g'enouc
kind'unoic
>ex
>ejn~wn
kind'unoic
>en
p'olei
kind'unoic
>en
>erhm'ia|
kind'unoic
>en
vjal'assh|
kind'unoic
>en
yeudad'elfoic\bibvsend
\vs 2Co 11:27
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
k'opw|
ka`i
m'oqjw|
>en
>agrupn'iaic
poll'akic
>en
lim~w|
ka`i
d'iyei
>en
nhste'iaic
poll'akic
>en
y'uqei
ka`i
gumn'othti\bibvsend
\vs 2Co 11:28
qwr`ic
t~wn
parekt`oc
<h
>epis'ustas'ic\r{}
\fn{\src{TMK}: episustasic mou, \src{V}: epistasic moi.}
mou
<h
kaj>
<hm'eran
<h
m'erimna
pas~wn
t~wn
>ekklhsi~wn\bibvsend
\vs 2Co 11:29
t'ic
>asjene~i
ka`i
o>uk
>asjen~w
t'ic
skandal'izetai
ka`i
o>uk
>eg`w
puro~umai\bibvsend
\vs 2Co 11:30
e>i
kauq~asjai
de~i
t`a
t~hc
>asjene'iac
mou
kauq'hsomai\bibvsend
\vs 2Co 11:31
<o
vje`oc
ka`i
pat`hr
to~u
kur'iou
<hm~wn\r{}
\fn{\src{T|K}: hmwn ihsou qristou, \src{M}: ihsou qristou, \src{V}: ihsou.}
>ihso~u
qristo~u
o>~iden
<o
>`wn
e>uloght`oc
e>ic
to`uc
a>i~wnac
<'oti
o>u
ye'udomai\bibvsend
\vs 2Co 11:32
>en
damask~w|
<o
>ejn'arqhc
>ar'eta
to~u
vbasil'ewc
>efro'urei
t`hn
damaskhn~wn\r{}
\fn{\src{TMK}: damaskhnwn polin piasai me vjelwn, \src{V}: polin damaskhnwn piasai me.}
p'olin
pi'asai
me
vj'elwn\bibvsend
\vs 2Co 11:33
ka`i
di`a
vjur'idoc
>en
sarg'anh|
>eqal'asjhn
di`a
to~u
te'iqouc
ka`i
>ex'efugon
t`ac
qe~irac
a>uto~u\bibvsend
\vs 2Co 12:1
kauq~asjai
d`h\r{}
\fn{\src{TMK}: dh ou sumferei moi eleusomai gar, \src{V}: dei ou sumferon men eleusomai de.}
o>u
sumf'erei
moi
>ele'usomai
g`ar
e>ic
>optas'iac
ka`i
>apokal'uyeic
kur'iou\bibvsend
\vs 2Co 12:2
o>~ida
>'anjrwpon
>en
qrist~w|
pr`o
>et~wn
dekatess'arwn
e>'ite
>en
s'wmati
o>uk
o>~ida
e>'ite
>ekt`oc
to~u
s'wmatoc
o>uk
o>~ida
<o
vje`oc
o>~iden
<arpag'enta
t`on
toio~uton
<'ewc
tr'itou
o>urano~u\bibvsend
\vs 2Co 12:3
ka`i
o>~ida
t`on
toio~uton
>'anjrwpon
e>'ite
>en
s'wmati
e>'ite
>e\r{k}t`oc
\fn{\src{TMK}: ektoc, \src{V}: qwric.}
to~u
s'wmatoc
o>uk
o>~ida
<o
vje`oc
o>~iden\bibvsend
\vs 2Co 12:4
<'oti
<hrp'agh
e>ic
t`on
par'adeison
ka`i
>'hkousen
>'arrhta
<r'hmata
<`a
o>uk
>ex`on
>anjr'wpw|
lal~hsai\bibvsend
\vs 2Co 12:5
<up`er
to~u
toio'utou
kauq'hsomai
<up`er
d`e
>emauto~u
o>u
kauq'hsomai
e>i
m`h
>en
ta~ic
>asjene'iaic
m\r{o}u\bibvsend
\fn{\src{TMK}: mou, \src{V}: \bibempty.}
\vs 2Co 12:6
>e`an
g`ar
vjel'hsw
kauq'hsasjai
o>uk
>'esomai
>'afrwn
>al'hjeian
g`ar
>er~w
vfe'idomai
d`e
m'h
tic
e>ic
>em`e
log'ishtai
<up`er
<`o
vbl'epei
me
>`h
>ako'uei
ti
>ex
>emo~u\bibvsend
\vs 2Co 12:7
ka`i
t~h|
<uperbol~h|
t~wn
>apokal'uyewn
<'i\r{n}a
\fn{\src{TMK}: ina, \src{V}: dio ina.}
m`h
<upera'irwmai
>ed'ojh
moi
sk'oloy
t~h|
sark`i
>'aggeloc
sat~a\r{n}
\fn{\src{TMK}: satan, \src{V}: satana.}
<'ina
me
kolaf'izh|
<'ina
m`h
<upera'irwmai\bibvsend
\vs 2Co 12:8
<up`er
to'utou
tr`ic
t`on
k'urion
parek'alesa
<'ina
>apost~h|
>ap>
>emo~u\bibvsend
\vs 2Co 12:9
ka`i
e>'irhk'en
moi
>arke~i
soi
<h
q'aric
mou
<h
g`ar
d'unam'ic
m\r{o}u
\fn{\src{TMK}: mou, \src{V}: \bibempty.}
>en
>asjene'ia|
telei\r{o}~utai
\fn{\src{TMK}: teleioutai, \src{V}: teleitai.}
<'hdista
o>~un
m~allon
kauq'hsomai
>en
ta~ic
>asjene'iaic
mou
<'ina
>episkhn'wsh|
>ep>
>em`e
<h
d'unamic
to~u
qristo~u\bibvsend
\vs 2Co 12:10
di`o
e>udok~w
>en
>asjene'iaic
>en
<'ubresin
>en
>an'agkaic
>en
diwgmo~ic
>e\r{n}
\fn{\src{TMK}: en, \src{V}: kai.}
stenoqwr'iaic
<up`er
qristo~u
<'otan
g`ar
>asjen~w
t'ote
dunat'oc
e>imi\bibvsend
\vs 2Co 12:11
g'egona
>'afrwn
kau\r{q}'wmenoc
\fn{\src{TMK}: kauqwmenoc, \src{V}: \bibempty.}
<ume~ic
me
>hnagk'asate
>eg`w
g`ar
>'wfeilon
<uf>
<um~wn
sun'istasjai
o>ud`en
g`ar
<ust'erhsa
t~wn
<up`er\r{}
\fn{\src{T|K}: uper lian, \src{M|V}: uperlian.}
l'ian
>apost'olwn
e>i
ka`i
o>ud'en
e>imi\bibvsend
\vs 2Co 12:12
t`a
m`en
shme~ia
to~u
>apost'olou
kateirg'asjh
>en
<um~in
>en
p'ash|
<upomon~h|
>en\r{}
\fn{\src{TMK}: en shmeioic, \src{V}: shmeioic te.}
shme'ioic
ka`i
t'erasin
ka`i
dun'amesin\bibvsend
\vs 2Co 12:13
t'i
g'ar
>estin
<`o
<h\r{t}t'hjhte
\fn{\src{TMK}: htthjhte, \src{V}: hsswjhte.}
<up`er
t`ac
loip`ac
>ekklhs'iac
e>i
m`h
<'oti
a>ut`oc
>eg`w
o>u
katen'arkhsa
<um~wn
qar'isasj'e
moi
t`hn
>adik'ian
ta'uthn\bibvsend
\vs 2Co 12:14
>ido`u
tr'ito\r{n}
\fn{\src{TMK}: triton, \src{V}: triton touto.}
<eto'imwc
>'eqw
>elje~in
pr`oc
<um~ac
ka`i
o>u
katanark'hsw
<u\r{m}~wn
\fn{\src{TMK}: umwn, \src{V}: \bibempty.}
o>u
g`ar
vzht~w
t`a
<um~wn
>al\r{l}>
\fn{\src{T|K}: all, \src{M|V}: alla.}
<um~ac
o>u
g`ar
>ofe'ilei
t`a
t'ekna
to~ic
gone~usin
vjhsaur'izein
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
o<i
gone~ic
to~ic
t'eknoic\bibvsend
\vs 2Co 12:15
>eg`w
d`e
<'hdista
dapan'hsw
ka`i
>ekdapanhj'hsomai
<up`er
t~wn
yuq~wn
<um~wn
e>i
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
perissot'erwc
<um~ac
>agap~wn\r{}
\fn{\src{TMK}: agapwn htton, \src{V}: agapw[n] hsson.}
<~htton
>agap~wmai\bibvsend
\vs 2Co 12:16
>'estw
d`e
>eg`w
o>u
kateb'arhsa
<um~ac
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<up'arqwn
pano~urgoc
d'olw|
<um~ac
>'elabon\bibvsend
\vs 2Co 12:17
m'h
tina
<~wn
>ap'estalka
pr`oc
<um~ac
di>
a>uto~u
>epleon'ekthsa
<um~ac\bibvsend
\vs 2Co 12:18
parek'alesa
t'iton
ka`i
sunap'esteila
t`on
>adelf`on
m'h\r{}
\fn{\src{TMK}: mh ti, \src{V}: mhti.}
ti
>epleon'ekthsen
<um~ac
t'itoc
o>u
t~w|
a>ut~w|
pne'umati
periepat'hsamen
o>u
to~ic
a>uto~ic
>'iqnesin\bibvsend
\vs 2Co 12:19
p'ali\r{n}
\fn{\src{TMK}: palin, \src{V}: palai.}
doke~ite
<'oti
<um~in
>apologo'umeja
katen'wpion\r{}
\fn{\src{TMK}: katenwpion tou, \src{V}: katenanti.}
to~u
vjeo~u
>en
qrist~w|
lalo~umen
t`a
d`e
p'anta
>agaphto`i
<up`er
t~hc
<um~wn
o>ikodom~hc\bibvsend
\vs 2Co 12:20
vfobo~umai
g`ar
m'h
pwc
>elj`wn
o>uq
o<'iouc
vj'elw
e<'urw
<um~ac
k>ag`w
e<urej~w
<um~in
o<~ion
o>u
vj'elete
m'h
pwc
>'ereic\r{}
\fn{\src{TMK}: ereic vzhloi, \src{V}: eric vzhloc.}
vz~hloi
vjumo`i
>erije~iai
katalalia`i
yijurismo`i
vfusi'wseic
>akatastas'iai\bibvsend
\vs 2Co 12:21
m`h
p'alin
>elj'onta\r{}
\fn{\src{T|K}: eljonta me tapeinwsh, \src{M}: eljonta me tapeinwsei, \src{V}: eljontoc mou tapeinwsh me.}
me
tapein'wsh|
<o
vje'oc
mou
pr`oc
<um~ac
ka`i
penj'hsw
pollo`uc
t~wn
prohmarthk'otwn
ka`i
m`h
metanohs'antwn
>ep`i
t~h|
>akajars'ia|
ka`i
porne'ia|
ka`i
>aselge'ia|
<~h|
>'epraxan\bibvsend
\vs 2Co 13:1
tr'iton
to~uto
>'erqomai
pr`oc
<um~ac
>ep`i
st'omatoc
d'uo
mart'urwn
ka`i
tri~wn
staj'hsetai
p~an
<r~hma\bibvsend
\vs 2Co 13:2
proe'irhka
ka`i
prol'egw
<wc
par`wn
t`o
de'uteron
ka`i
>ap`wn
n~un
g\r{r}'afw
\fn{\src{TMK}: grafw, \src{V}: \bibempty.}
to~ic
prohmarthk'osin
ka`i
to~ic
loipo~ic
p~asin
<'oti
>e`an
>'eljw
e>ic
t`o
p'alin
o>u
vfe'isomai\bibvsend
\vs 2Co 13:3
>epe`i
dokim`hn
vzhte~ite
to~u
>en
>emo`i
lalo~untoc
qristo~u
<`oc
e>ic
<um~ac
o>uk
>asjene~i
>all`a
dunate~i
>en
<um~in\bibvsend
\vs 2Co 13:4
ka`i
g`ar
\r{e}>i
\fn{\src{TMK}: ei, \src{V}: \bibempty.}
>estaur'wjh
>ex
>asjene'iac
>all`a
vz~h|
>ek
dun'amewc
vjeo~u
ka`i
g`a\r{r}
\fn{\src{T|M|V}: gar, \src{K}: gar kai.}
<hme~ic
>asjeno~umen
>en
a>ut~w|
>all`a
vzhs'omej\r{a}
\fn{\src{TMK}: vzhsomeja, \src{V}: vzhsomen.}
s`un
a>ut~w|
>ek
dun'amewc
vjeo~u
e>ic
<um~ac\bibvsend
\vs 2Co 13:5
<eauto`uc
peir'azete
e>i
>est`e
>en
t~h|
p'istei
<eauto`uc
dokim'azete
>`h
o>uk
>epigin'wskete
<eauto`uc
<'oti
>ihso~uc
qrist`oc
>en
<um~in
>es\r{t}in
\fn{\src{TMK}: estin, \src{V}: \bibempty.}
e>i
m'h\r{}
\fn{\src{T|K}: mh ti, \src{M|V}: mhti.}
ti
>ad'okimo'i
>este\bibvsend
\vs 2Co 13:6
>elp'izw
d`e
<'oti
gn'wsesje
<'oti
<hme~ic
o>uk
>esm`en
>ad'okimoi\bibvsend
\vs 2Co 13:7
e>'uqom\r{a}i
\fn{\src{TMK}: euqomai, \src{V}: euqomeja.}
d`e
pr`oc
t`on
vje`on
m`h
poi~hsai
<um~ac
kak`on
mhd`en
o>uq
<'ina
<hme~ic
d'okimoi
vfan~wmen
>all>
<'ina
<ume~ic
t`o
kal`on
poi~hte
<hme~ic
d`e
<wc
>ad'okimoi
>~wmen\bibvsend
\vs 2Co 13:8
o>u
g`ar
dun'amej'a
ti
kat`a
t~hc
>alhje'iac
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<up`er
t~hc
>alhje'iac\bibvsend
\vs 2Co 13:9
qa'iromen
g`ar
<'otan
<hme~ic
>asjen~wmen
<ume~ic
d`e
dunato`i
>~hte
to~uto
d`e\r{}
\fn{\src{TMK}: de, \src{V}: \bibempty.}
ka`i
e>uq'omeja
t`hn
<um~wn
kat'artisin\bibvsend
\vs 2Co 13:10
di`a
to~uto
ta~uta
>ap`wn
gr'afw
<'ina
par`wn
m`h
>apot'omwc
qr'hswmai
kat`a
t`hn
>exous'ian
<`hn
>'edwk'en\r{}
\fn{\src{TMK}: edwken moi o kurioc, \src{V}: o kurioc edwken moi.}
moi
<o
k'urioc
e>ic
o>ikodom`hn
ka`i
o>uk
e>ic
kaja'iresin\bibvsend
\vs 2Co 13:11
loip`on
>adelfo`i
qa'irete
katart'izesje
parakale~isje
t`o
a>ut`o
vfrone~ite
e>irhne'uete
ka`i
<o
vje`oc
t~hc
>ag'aphc
ka`i
e>ir'hnhc
>'estai
mej>
<um~wn\bibvsend
\vs 2Co 13:12
>asp'asasje
>all'hlouc
>en
<ag'iw|
vfil'hmati
>asp'azontai
<um~ac
o<i
<'agioi
p'antec\bibvsend
\vs 2Co 13:13
<h
q'aric
to~u
kur'iou
>ihso~u
qristo~u
ka`i
<h
>ag'aph
to~u
vjeo~u
ka`i
<h
koinwn'ia
to~u
<ag'iou
pne'umatoc
met`a
p'antwn
<um~wn
>a\r{m}'hn\bibvsend
\fn{\src{TMK}: amhn, \src{V}: \bibempty.}
Pr`oc\r{}
\fn{\src{T}: Proc \ldots\ louka, \src{K|M|V}: \bibempty.}
korinj'iouc
deut'era
>egr'afh
>ap`o
vfil'ippwn
t~hc
makedon'iac
di`a
t'itou
ka`i
louk~a\bibvsend
