\bibbook{EPISTOLH IWANNOU\\\LARGE DEUTERA\r{}}{IWANNOU B'}{II John}{2Jo}[IWANNOU B']
\vs 2Jo 1:1
<o
\fnt{\src{T}: EPISTOLH IWANNOU DEUTERA, \src{K}: IWANNOU EPISTOLH DEUTERA, \src{M|V}: IWANNOU B.}
presb'uteroc
>eklekt~h|
kur'ia|
ka`i
to~ic
t'eknoic
a>ut~hc
o<`uc
>eg`w
>agap~w
>en
>alhje'ia|
ka`i
o>uk
>eg`w
m'onoc
>all`a
ka`i
p'antec
o<i
>egnwk'otec
t`hn
>al'hjeian\bibvsend
\vs 2Jo 1:2
di`a\r{}
\fn{\src{TMKVN}: dia thn alhjeian, \src{F}: \bibempty.}
t`hn
>al'hjeian
t`hn
\r{m}'enousan
\fn{\src{TMKVN}: menousan, \src{A}: enoikousan, \src{F}: ousan.}
>en
<h\r{m}~in
\fn{\src{TMKVN}: hmin, \src{F}: umin.}
ka`i
mej>
<h\r{m}~wn
\fn{\src{TMKVN}: hmwn, \src{F}: umwn.}
>'estai
e>ic
t`on
a>i~wna\bibvsend
\vs 2Jo 1:3
>'estai
mej>
<h\r{m}~wn
\fn{\src{T|M|V}: hmwn, \src{K}: umwn.}
q'aric
>'el\r{e}oc
\fn{\src{TMKVN}: eleoc, \src{F}: umin kai.}
e>ir'hnh
par`a
vjeo~u
patr`oc
ka`i
par`a\r{}
\fn{\src{TMK}: para kuriou, \src{V}: para, \src{aleph}: kuriou.}
kur'iou
>ihso~u
qristo~u
to~u
u<io~u
to~u
pa\r{t}r`oc
\fn{\src{TMKVN}: patroc, \src{F}: vjeou.}
>en
>alhje'ia|
ka`i
>ag'aph|\bibvsend
\vs 2Jo 1:4
>eq'arhn
l'ian
<'oti
e<'urhka
>ek
t~wn
t'eknwn
sou
peripato~untac
>en
>alhje'ia|
kaj`wc
>entol`hn
>el'abo\r{m}en
\fn{\src{TMKVN}: elabomen, \src{aleph}: elabon.}
par`a
to~u
patr'oc\bibvsend
\vs 2Jo 1:5
ka`i
n~un
>erwt~w
se
kur'ia
o>uq
<wc
>entol`hn
gr'afw\r{}
\fn{\src{T}: grafw soi kainhn, \src{K|M}: grafwn soi kainhn, \src{V}: kainhn grafwn soi, \src{F}: kainhn grafw soi.}
soi
kain`hn
>all`a
<`hn
e>'iqomen
>ap>
>arq~hc
<'ina
>agap~wmen
>all'hlouc\bibvsend
\vs 2Jo 1:6
ka`i
a<'uth
>est`in
<h
>ag'aph
<'ina
peripat~wmen
kat`a
t`ac
>entol`ac
a>uto~u
a<'uth
>est`in\r{}
\fn{\src{TMK}: estin h entolh, \src{V}: h entolh estin, \src{aleph}: estin h entolh autou.}
<h
>entol`h
\r{k}aj`wc
\fn{\src{TMKVN}: kajwc, \src{aleph|A}: ina kajwc.}
>hko'usate
>ap>
>arq~hc
<'i\r{n}a
\fn{\src{TMKVN}: ina, \src{F}: \bibempty.}
>en
a>ut~h|
peripat~hte\bibvsend
\vs 2Jo 1:7
<'oti
pollo`i
pl'anoi
e>i\r{s}~hljon
\fn{\src{TMK}: eishljon, \src{V}: exhljon.}
e>ic
t`on
k'osmon
o<i
m`h
<omologo~untec
>ihso~un
qrist`on
>erq'omenon
>en
sark`i
o<~ut'oc
>estin
<o
pl'anoc
ka`i
<o\r{}
\fn{\src{TMKVN}: o, \src{aleph}: \bibempty.}
>ant'iqristoc\bibvsend
\vs 2Jo 1:8
vbl'epete
<eauto`uc
<'ina
m`h
>apol'esw\r{m}en
\fn{\src{TMK}: apoleswmen, \src{V}: apoleshte.}
<`a
e>irgas'a\r{m}eja
\fn{\src{TMKVN}: eirgasameja, \src{aleph|A}: eirgasasje.}
>all`a
misj`on
pl'hrh
>apol'ab\r{w}men\bibvsend
\fn{\src{TMK}: apolabwmen, \src{V}: apolabhte.}
\vs 2Jo 1:9
p~ac
<o
pa\r{r}aba'inwn
\fn{\src{TMK}: parabainwn, \src{V}: proagwn.}
ka`i
m`h
m'enwn
>en
t~h|
dida\r{q}~h|
\fn{\src{TMKVN}: didaqh, \src{F}: agaph.}
to~u
qristo~u
vje`on
o>uk
>'eqei
<o
m'enwn
>en
t~h|
didaq~h|
to~u\r{}
\fn{\src{TMK}: tou qristou, \src{V}: \bibempty, \src{F}: autou.}
qristo~u
o<~utoc
ka`i
t`on
pat'era\r{}
\fn{\src{TMKVN}: patera kai ton uion, \src{A}: uion kai ton patera.}
ka`i
t`on
u<i`on
>'eqei\bibvsend
\vs 2Jo 1:10
e>'i
tic
>'erqetai
pr`oc
<um~ac
ka`i
ta'uthn
t`hn
didaq`hn
o>u
vf'erei
m`h
lamb'anete
a>ut`on
e>ic
o>ik'ian
ka`i
qa'irein
a>ut~w|
m`h
l'egete\bibvsend
\vs 2Jo 1:11
<o
g`ar\r{}
\fn{\src{TMK}: gar legwn autw, \src{V}: legwn gar autw, \src{F}: gar legwn.}
l'egwn
a>ut~w|
qa'irein
koinwne~i
to~ic
>'ergoic
a>uto~u
to~ic
ponhro~ic\bibvsend
\vs 2Jo 1:12
poll`a
>'eqw\r{n}
\fn{\src{TMKVN}: eqwn, \src{aleph|A}: eqw.}
<um~in
gr'a\r{f}ein
\fn{\src{TMKVN}: grafein, \src{A}: grayai.}
o>uk
>hb\r{o}ul'hjhn
\fn{\src{T|K}: hboulhjhn, \src{M|V}: eboulhjhn.}
di`a
q'artou
ka`i
m'elanoc
>all`a\r{}
\fn{\src{TMK}: alla elpizw eljein, \src{V}: alla elpizw genesjai, \src{A}: elpizw gar genesjai.}
>elp'izw
>elje~in
pr`oc
<um~ac
ka`i
st'oma
pr`oc
st'oma
lal~hsai
<'ina
<h
qar`a
<hm~wn\r{}
\fn{\src{TMK}: hmwn h peplhrwmenh, \src{V}: hmwn peplhrwmenh h, \src{A}: umwn h peplhrwmenh.}
>~h|
peplhrwm'enh\bibvsend
\vs 2Jo 1:13
>asp'azeta'i
se
t`a
t'ekna
t~hc
>adelf~hc
sou
t~hc
>ekle\r{k}t~hc
\fn{\src{TMKVN}: eklekthc, \src{F}: ekklhsiac.}
>a\r{m}'hn\bibvsend
\fn{\src{TMK}: amhn, \src{V}: \bibempty, \src{F}: h qaric meta sou amhn.}
