\bibbook{EPISTOLH IWANNOU\\\LARGE TRITH\r{}}{IWANNOU G'}{III John}{3Jo}[IWANNOU G']
\vs 3Jo 1:1
<o
\fnt{\src{T}: EPISTOLH IWANNOU TRITH, \src{K}: IWANNOU EPISTOLH TRITH, \src{M|V}: IWANNOU G.}
presb'uteroc
ga"'iw|
t~w|
>agapht~w|
<`on
>eg`w
>agap~w
>en
>alhje'ia|\bibvsend
\vs 3Jo 1:2
>agapht`e
per`i
p'antwn
e>'uqoma'i
se
e>uodo~usjai
ka`i
<ugia'inein
kaj`wc
e>uodo~uta'i
sou
<h
yuq'h\bibvsend
\vs 3Jo 1:3
>eq'arhn
g`ar
l'ian
>erqom'enwn
>adelf~wn
ka`i
marturo'untwn
sou
t~h|
>alhje'ia|
kaj`wc
s`u
>en
>alhje'ia|
peripate~ic\bibvsend
\vs 3Jo 1:4
meizot'eran
to'utwn
o>uk
>'eqw
qar`an
<'ina
>ako'uw
t`a
>em`a
t'ekna
>e\r{n}
\fn{\src{TMK}: en, \src{V}: en th.}
>alhje'ia|
peripato~unta\bibvsend
\vs 3Jo 1:5
>agapht`e
pist`on
poie~ic
<`o
>e`an
>erg'ash|
e>ic
to`uc
>adelfo`uc
ka`i
e>ic\r{}
\fn{\src{TMK}: eic touc, \src{V}: touto.}
to`uc
x'enouc\bibvsend
\vs 3Jo 1:6
o<`i
>emart'urhs'an
sou
t~h|
>ag'aph|
>en'wpion
>ekklhs'iac
o<`uc
kal~wc
poi'hseic
prop'emyac
>ax'iwc
to~u
vjeo~u\bibvsend
\vs 3Jo 1:7
<up`er
g`ar
to~u
>on'omato\r{c}
\fn{\src{T|M|V}: onomatoc, \src{K}: onomatoc autou.}
>ex~hljon
mhd`en
lamb'anontec
>ap`o
t~wn
>ej\r{n}~wn\bibvsend
\fn{\src{TMK}: ejnwn, \src{V}: ejnikwn.}
\vs 3Jo 1:8
<hme~ic
o>~un
>ofe'ilomen
>a\r{p}olamb'anein
\fn{\src{TMK}: apolambanein, \src{V}: upolambanein.}
to`uc
toio'utouc
<'ina
sunergo`i
gin'wmeja
t~h|
>alhje'ia|\bibvsend
\vs 3Jo 1:9
>'egray\r{a}
\fn{\src{TMK}: egraya, \src{V}: egraya ti.}
t~h|
>ekklhs'ia|
>all>
<o
vfiloprwte'uwn
a>ut~wn
diotref`hc
o>uk
>epid'eqetai
<hm~ac\bibvsend
\vs 3Jo 1:10
di`a
to~uto
>e`an
>'eljw
<upomn'hsw
a>uto~u
t`a
>'erga
<`a
poie~i
l'ogoic
ponhro~ic
vfluar~wn
<hm~ac
ka`i
m`h
>arko'umenoc
>ep`i
to'utoic
o>'ute
a>ut`oc
>epid'eqetai
to`uc
>adelfo`uc
ka`i
to`uc
vboulom'enouc
kwl'uei
ka`i
>ek
t~hc
>ekklhs'iac
>ekb'allei\bibvsend
\vs 3Jo 1:11
>agapht`e
m`h
mimo~u
t`o
kak`on
>all`a
t`o
>agaj`on
<o
>agajopoi~wn
>ek
to~u
vjeo~u
>estin
<o
d`e\r{}
\fn{\src{T|K}: de, \src{M|V}: \bibempty.}
kakopoi~wn
o>uq
<e'wraken
t`on
vje'on\bibvsend
\vs 3Jo 1:12
dhmhtr'iw|
memart'urhtai
<up`o
p'antwn
ka`i
<u\r{p}>
\fn{\src{TMK}: up, \src{V}: upo.}
a>ut~hc
t~hc
>alhje'iac
ka`i
<hme~ic
d`e
marturo~umen
ka`i
o>'ida\r{t}e
\fn{\src{TMK}: oidate, \src{V}: oidac.}
<'oti
<h
martur'ia
<hm~wn
>alhj'hc
>estin\bibvsend
\vs 3Jo 1:13
poll`a
e>~iqon
gr'a\r{f}ein
\fn{\src{TMK}: grafein, \src{V}: grayai soi.}
>all>
o>u
vj'elw
di`a
m'elanoc
ka`i
kal'amou
soi
gr'a\r{y}ai\bibvsend
\fn{\src{TMK}: grayai, \src{V}: grafein.}
\vs 3Jo 1:14
>elp'izw
d`e
e>uj'ewc
>ide~in\r{}
\fn{\src{TMK}: idein se, \src{V}: se idein.}
se
ka`i
st'oma
pr`oc
st'oma
lal'hsomen\bibvsend
\vs 3Jo 1:15
e>ir'hnh
soi
>asp'azonta'i
se
o<i
vf'iloi
>asp'azou
to`uc
vf'ilouc
kat>
>'onoma\bibvsend
