\bibbook{PROS EFESIOUS\\\LARGE EPISTOLH PAULOU\r{}}{PROS EFESIOUS}{Ephesians}{Eph}[PROS EFESIOUS]
\vs Eph 1:1
pa~uloc
\fnt{\src{T}: PROS EFESIOUS EPISTOLH PAULOU, \src{K}: PAULOU TOU APOSTOLOU H PROS EFESIOUS EPISTOLH, \src{M|V}: PROS EFESIOUS.}
>ap'ostoloc
>ihso~u\r{}
\fn{\src{TMK}: ihsou qristou, \src{V}: qristou ihsou.}
qristo~u
di`a
vjel'hmatoc
vjeo~u
to~ic
<ag'ioic
to~ic
o>~usin
>en\r{}
\fn{\src{TMK}: en efesw, \src{V}: [en efesw], \src{B[*]|aleph[*]|Pap[46]}: \bibempty.}
>ef'esw|
ka`i
pisto~ic
>en
qrist~w|
>ihso~u\bibvsend
\vs Eph 1:2
q'aric
<um~in
ka`i
e>ir'hnh
>ap`o
vjeo~u
patr`oc
<hm~wn
ka`i
kur'iou
>ihso~u
qristo~u\bibvsend
\vs Eph 1:3
e>uloght`oc
<o
vje`oc
ka`i
pat`hr
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
<o
e>ulog'hsac
<hm~ac
>en
p'ash|
e>ulog'ia|
pneumatik~h|
>en
to~ic
>epouran'ioic
\r{q}rist~w|\bibvsend
\fn{\src{T}: qristw, \src{K|M|V}: en qristw.}
\vs Eph 1:4
kaj`wc
>exel'exato
<hm~ac
>en
a>ut~w|
pr`o
katabol~hc
k'osmou
e>~inai
<hm~ac
<ag'iouc
ka`i
>am'wmouc
katen'wpion
a>uto~u
>en
>ag'aph|\bibvsend
\vs Eph 1:5
proor'isac
<hm~ac
e>ic
u<iojes'ian
di`a
>ihso~u
qristo~u
e>ic
a>ut`on
kat`a
t`hn
e>udok'ian
to~u
vjel'hmatoc
a>uto~u\bibvsend
\vs Eph 1:6
e>ic
>'epainon
d'oxhc
t~hc
q'aritoc
a>uto~u
>en\r{}
\fn{\src{TMK}: en h, \src{V}: hc.}
<~h|
>eqar'itwsen
<hm~ac
>en
t~w|
>hgaphm'enw|\bibvsend
\vs Eph 1:7
>en
<~w|
>'eqomen
t`hn
>apol'utrwsin
di`a
to~u
a<'imatoc
a>uto~u
t`hn
>'afesin
t~wn
paraptwm'atwn
kat`a
t`on\r{}
\fn{\src{TMK}: ton plouton, \src{V}: to ploutoc.}
plo~uton
t~hc
q'aritoc
a>uto~u\bibvsend
\vs Eph 1:8
<~hc
>eper'isseusen
e>ic
<hm~ac
>en
p'ash|
sof'ia|
ka`i
vfron'hsei\bibvsend
\vs Eph 1:9
gnwr'isac
<hm~in
t`o
must'hrion
to~u
vjel'hmatoc
a>uto~u
kat`a
t`hn
e>udok'ian
a>uto~u
<`hn
pro'ejeto
>en
a>ut~w|\bibvsend
\vs Eph 1:10
e>ic
o>ikonom'ian
to~u
plhr'wmatoc
t~wn
kair~wn
>anakefalai'wsasjai
t`a
p'anta
>en
t~w|
qrist~w|
t'a
te\r{}
\fn{\src{T|K}: te en, \src{M|V}: epi.}
>en
to~ic
o>urano~ic
ka`i
t`a
>ep`i
t~hc
g~hc\bibvsend
\vs Eph 1:11
>en
a>ut~w|
>en
<~w|
ka`i
>eklhr'wjhmen
proorisj'entec
kat`a
pr'ojesin
to~u
t`a
p'anta
>energo~untoc
kat`a
t`hn
vboul`hn
to~u
vjel'hmatoc
a>uto~u\bibvsend
\vs Eph 1:12
e>ic
t`o
e>~inai
<hm~ac
e>ic
>'epainon
\r{t}~hc
\fn{\src{T|K}: thc, \src{M|V}: \bibempty.}
d'oxhc
a>uto~u
to`uc
prohlpik'otac
>en
t~w|
qrist~w|\bibvsend
\vs Eph 1:13
>en
<~w|
ka`i
<ume~ic
>ako'usantec
t`on
l'ogon
t~hc
>alhje'iac
t`o
e>uagg'elion
t~hc
swthr'iac
<um~wn
>en
<~w|
ka`i
piste'usantec
>esfrag'isjhte
t~w|
pne'umati
t~hc
>epaggel'iac
t~w|
<ag'iw|\bibvsend
\vs Eph 1:14
<'oc\r{}
\fn{\src{TMK}: oc, \src{V}: o.}
>estin
>arrab`wn
t~hc
klhronom'iac
<hm~wn
e>ic
>apol'utrwsin
t~hc
peripoi'hsewc
e>ic
>'epainon
t~hc
d'oxhc
a>uto~u\bibvsend
\vs Eph 1:15
di`a
to~uto
k>ag`w
>ako'usac
t`hn
kaj>
<um~ac
p'istin
>en
t~w|
kur'iw|
>ihso~u
ka`i
t`hn
>ag'aphn
t`hn
e>ic
p'antac
to`uc
<ag'iouc\bibvsend
\vs Eph 1:16
o>u
pa'uomai
e>uqarist~wn
<up`er
<um~wn
mne'ian
<u\r{m}~wn
\fn{\src{TMK}: umwn, \src{V}: \bibempty.}
poio'umenoc
>ep`i
t~wn
proseuq~wn
mou\bibvsend
\vs Eph 1:17
<'ina
<o
vje`oc
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
<o
pat`hr
t~hc
d'oxhc
d'wh|
<um~in
pne~uma
sof'iac
ka`i
>apokal'uyewc
>en
>epign'wsei
a>uto~u\bibvsend
\vs Eph 1:18
pefwtism'enouc
to`uc
>ofjalmo`uc
t~hc
dia\r{n}o'iac
\fn{\src{T|K}: dianoiac, \src{M|V}: kardiac.}
<um~wn
e>ic
t`o
e>id'enai
<um~ac
t'ic
>estin
<h
>elp`ic
t~hc
kl'hsewc
a>uto~u
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
t'ic
<o
plo~utoc
t~hc
d'oxhc
t~hc
klhronom'iac
a>uto~u
>en
to~ic
<ag'ioic\bibvsend
\vs Eph 1:19
ka`i
t'i
t`o
<uperb'allon
m'egejoc
t~hc
dun'amewc
a>uto~u
e>ic
<hm~ac
to`uc
piste'uontac
kat`a
t`hn
>en'ergeian
to~u
kr'atouc
t~hc
>isq'uoc
a>uto~u\bibvsend
\vs Eph 1:20
<`hn
>en'hrghsen
>en
t~w|
qrist~w|
>ege'irac
a>ut`on
>ek
nekr~wn\r{}
\fn{\src{T|K}: nekrwn kai ekajisen, \src{M}: twn nekrwn kai ekajisen, \src{V}: nekrwn kai kajisac.}
ka`i
>ek'ajisen
>en
dexi~a|
a>uto~u
>en
to~ic
>epouran'ioic\bibvsend
\vs Eph 1:21
<uper'anw
p'ashc
>arq~hc
ka`i
>exous'iac
ka`i
dun'amewc
ka`i
kuri'othtoc
ka`i
pant`oc
>on'omatoc
>onomazom'enou
o>u
m'onon
>en
t~w|
a>i~wni
to'utw|
>all`a
ka`i
>en
t~w|
m'ellonti\bibvsend
\vs Eph 1:22
ka`i
p'anta
<up'etaxen
<up`o
to`uc
p'odac
a>uto~u
ka`i
a>ut`on
>'edwken
kefal`hn
<up`er
p'anta
t~h|
>ekklhs'ia|\bibvsend
\vs Eph 1:23
<'htic
>est`in
t`o
s~wma
a>uto~u
t`o
pl'hrwma
to~u
\r{p}'anta
\fn{\src{T|K}: panta, \src{M|V}: ta panta.}
>en
p~asin
plhroum'enou\bibvsend
\vs Eph 2:1
ka`i
<um~ac
>'ontac
nekro`uc
to~ic
parapt'wmasin
ka`i
ta~ic
<a\-\r{m}ar\-t'i\-aic\bibvsend
\fn{\src{TMK}: amartiaic, \src{V}: amartiaic umwn, \src{B}: epijumiaic.}
\vs Eph 2:2
>en
a<~ic
pote
periepat'hsate
kat`a
t`on
a>i~wna
to~u
k'osmou
to'utou
kat`a
t`on
>'arqonta
t~hc
>exous'iac
to~u
>a'eroc
to~u
pne'umatoc
to~u
n~un
>energo~untoc
>en
to~ic
u<io~ic
t~hc
>apeije'iac\bibvsend
\vs Eph 2:3
>en
o<~ic
ka`i
<hme~ic
p'antec
>anestr'afhm'en
pote
>en
ta~ic
>epijum'iaic
t~hc
sark`oc
<hm~wn
poio~untec
t`a
vjel'hmata
t~hc
sark`oc
ka`i
t~wn
dianoi~wn
ka`i
>~hme\r{n}
\fn{\src{TMK}: hmen, \src{V}: hmeja.}
t'ekna
vf'usei
>org~hc
<wc
ka`i
o<i
loipo'i\bibvsend
\vs Eph 2:4
<o
d`e
vje`oc
plo'usioc
>`wn
>en
>el'eei
di`a
t`hn
poll`hn
>ag'aphn
a>uto~u
<`hn
>hg'aphsen
<hm~ac\bibvsend
\vs Eph 2:5
ka`i
>'ontac
<hm~ac
nekro`uc
to~ic
parapt'wmasin
sunezwopo'ihsen
\r{t}~w|
\fn{\src{TMKVN}: tw, \src{B}: en tw.}
qrist~w|
\r{q}'arit'i
\fn{\src{TMKVN}: qariti, \src{F}: o<~u qariti.}
>este
seswsm'enoi\bibvsend
\vs Eph 2:6
ka`i
sun'hgeiren
ka`i
sunek'ajisen
>en
to~ic
>epouran'ioic
>en
qrist~w|
>ihso~u\bibvsend
\vs Eph 2:7
<'ina
>ende'ixhtai
>en
to~ic
a>i~wsin
to~ic
>eperqom'enoic
t`on\r{}
\fn{\src{TMK}: ton uperballonta plouton, \src{V}: to uperballon ploutoc.}
<uperb'allonta
plo~uton
t~hc
q'aritoc
a>uto~u
>en
qrhst'othti
>ef>
<hm~ac
>en
qrist~w|
>ihso~u\bibvsend
\vs Eph 2:8
t~h|
g`ar
q'arit'i
>este
seswsm'enoi
di`a
\r{t}~hc
\fn{\src{TMK}: thc, \src{V}: \bibempty.}
p'istewc
ka`i
to~uto
o>uk
>ex
<um~wn
vjeo~u
t`o
d~wron\bibvsend
\vs Eph 2:9
o>uk
>ex
>'ergwn
<'ina
m'h
tic
kauq'hshtai\bibvsend
\vs Eph 2:10
a>uto~u
g'ar
>esmen
po'ihma
ktisj'entec
>en
qrist~w|
>ihso~u
>ep`i
>'ergoic
>agajo~ic
o<~ic
prohto'imasen
<o
vje`oc
<'ina
>en
a>uto~ic
peripat'hswmen\bibvsend
\vs Eph 2:11
di`o
mnhmone'uete
<'oti
<ume~ic\r{}
\fn{\src{TMK}: umeic pote, \src{V}: pote umeic.}
pote
t`a
>'ejnh
>en
sark`i
o<i
leg'omenoi
>akrobust'ia
<up`o
t~hc
legom'enhc
peritom~hc
>en
sark`i
qeiropoi'htou\bibvsend
\vs Eph 2:12
<'oti
>~hte
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
t~w|
kair~w|
>eke'inw|
qwr`ic
qristo~u
>aphllotriwm'enoi
t~hc
polite'iac
to~u
>isra`hl
ka`i
x'enoi
t~wn
diajhk~wn
t~hc
>epaggel'iac
>elp'ida
m`h
>'eqontec
ka`i
>'ajeoi
>en
t~w|
k'osmw|\bibvsend
\vs Eph 2:13
nun`i
d`e
>en
qrist~w|
>ihso~u
<ume~ic
o<i
pot`e
>'ontec
makr`an
>egg`uc\r{}
\fn{\src{TMK}: egguc egenhjhte, \src{V}: egenhjhte egguc.}
>egen'hjhte
>en
t~w|
a<'imati
to~u
qristo~u\bibvsend
\vs Eph 2:14
a>ut`oc
g'ar
>estin
<h
e>ir'hnh
<hm~wn
<o
poi'hsac
t`a
>amf'otera
<`en
ka`i
t`o
mes'otoiqon
to~u
vfragmo~u
l'usac\bibvsend
\vs Eph 2:15
t`hn
>'eqjran
>en
t~h|
sark`i
a>uto~u
t`on
n'omon
t~wn
>entol~wn
>en
d'ogmasin
katarg'hsac
<'ina
to`uc
d'uo
kt'ish|
>en
<e\r{a}ut~w|
\fn{\src{TMK}: eautw, \src{V}: autw.}
e>ic
<'ena
kain`on
>'anjrwpon
poi~wn
e>ir'hnhn\bibvsend
\vs Eph 2:16
ka`i
>apokatall'axh|
to`uc
>amfot'erouc
>en
<en`i
s'wmati
t~w|
vje~w|
di`a
to~u
stauro~u
>apokte'inac
t`hn
>'eqjran
>en
a>ut~w|\bibvsend
\vs Eph 2:17
ka`i
>elj`wn
e>uhggel'isato
e>ir'hnhn
<um~in
to~ic
makr`an
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: kai eirhnhn.}
to~ic
>egg'uc\bibvsend
\vs Eph 2:18
<'oti
di>
a>uto~u
>'eqomen
t`hn
prosagwg`hn
o<i
>amf'oteroi
>en
<en`i
pne'umati
pr`oc
t`on
pat'era\bibvsend
\vs Eph 2:19
>'ara
o>~un
o>uk'eti
>est`e
x'enoi
ka`i
p'aroikoi
>all`a\r{}
\fn{\src{TMK}: alla, \src{V}: alla este.}
sumpol~itai
t~wn
<ag'iwn
ka`i
o>ike~ioi
to~u
vjeo~u\bibvsend
\vs Eph 2:20
>epoikodomhj'entec
>ep`i
t~w|
vjemel'iw|
t~wn
>apost'olwn
ka`i
profht~wn
>'ontoc
>akrogwnia'iou
a>uto~u
>ihso~u\r{}
\fn{\src{TMK}: ihsou qristou, \src{V}: qristou ihsou.}
qristo~u\bibvsend
\vs Eph 2:21
>en
<~w|
p~asa
<h\r{}
\fn{\src{T|K}: h, \src{M|V}: \bibempty.}
o>ikodom`h
sunarmologoum'enh
a>'uxei
e>ic
na`on
<'agion
>en
kur'iw|\bibvsend
\vs Eph 2:22
>en
<~w|
ka`i
<ume~ic
sunoikodome~isje
e>ic
katoikht'hrion
to~u
vjeo~u
>en
pne'umati\bibvsend
\vs Eph 3:1
to'utou
q'arin
>eg`w
pa~uloc
<o
d'esmioc
to~u
qristo~u
>ihso~u
<up`er
<um~wn
t~wn
>ejn~wn\bibvsend
\vs Eph 3:2
e>'i\r{g}e
\fn{\src{TMK}: eige, \src{V}: ei ge.}
>hko'usate
t`hn
o>ikonom'ian
t~hc
q'aritoc
to~u
vjeo~u
t~hc
doje'ishc
moi
e>ic
<um~ac\bibvsend
\vs Eph 3:3
<'oti
kat`a
>apok'aluyin
>egn'wris'e\r{n}
\fn{\src{TMK}: egnwrisen, \src{V}: egnwrisjh.}
moi
t`o
must'hrion
kaj`wc
pro'egraya
>en
>ol'igw|\bibvsend
\vs Eph 3:4
pr`oc
<`o
d'unasje
>anagin'wskontec
no~hsai
t`hn
s'unes'in
mou
>en
t~w|
musthr'iw|
to~u
qristo~u\bibvsend
\vs Eph 3:5
<`o
>e\r{n}
\fn{\src{T|K}: en, \src{M|V}: \bibempty.}
<et'eraic
genea~ic
o>uk
>egnwr'isjh
to~ic
u<io~ic
t~wn
>anjr'wpwn
<wc
n~un
>apekal'ufjh
to~ic
<ag'ioic
>apost'oloic
a>uto~u
ka`i
prof'htaic
>en
pne'umati\bibvsend
\vs Eph 3:6
e>~inai
t`a
>'ejnh
sugklhron'oma
ka`i
s'usswma
ka`i
summ'etoqa
t~hc
>epaggel'iac
a>uto~u\r{}
\fn{\src{TMK}: autou en tw qristw, \src{V}: en qristw ihsou.}
>en
t~w|
qrist~w|
di`a
to~u
e>uaggel'iou\bibvsend
\vs Eph 3:7
o<~u
>ege\r{n}'omhn
\fn{\src{TMK}: egenomhn, \src{V}: egenhjhn.}
di'akonoc
kat`a
t`hn
dwre`an
t~hc
q'aritoc
to~u
vjeo~u
t`hn\r{}
\fn{\src{TMK}: thn dojeisan, \src{V}: thc dojeishc.}
doje~is'an
moi
kat`a
t`hn
>en'ergeian
t~hc
dun'amewc
a>uto~u\bibvsend
\vs Eph 3:8
>emo`i
t~w|
>elaqistot'erw|
p'antwn
\r{t}~wn
\fn{\src{T|K}: twn, \src{M|V}: \bibempty.}
<ag'iwn
>ed'ojh
<h
q'aric
a<'uth
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
to~ic
>'ejnesin
e>uaggel'isasjai
t`on\r{}
\fn{\src{TMK}: ton anexiqniaston plouton, \src{V}: to anexiqniaston ploutoc.}
>anexiqn'iaston
plo~uton
to~u
qristo~u\bibvsend
\vs Eph 3:9
ka`i
vfwt'isai
p'antac
t'ic
<h
koi\r{n}wn'ia
\fn{\src{T|K}: koinwnia, \src{M|V}: oikonomia.}
to~u
musthr'iou
to~u
>apokekrumm'enou
>ap`o
t~wn
a>i'wnwn
>en
t~w|
vje~w|
t~w|
t`a
p'anta
kt'isanti
di`a\r{}
\fn{\src{TMK}: dia ihsou qristou, \src{V}: \bibempty.}
>ihso~u
qristo~u\bibvsend
\vs Eph 3:10
<'ina
gnwrisj~h|
n~un
ta~ic
>arqa~ic
ka`i
ta~ic
>exous'iaic
>en
to~ic
>epouran'ioic
di`a
t~hc
>ekklhs'iac
<h
polupo'ikiloc
sof'ia
to~u
vjeo~u\bibvsend
\vs Eph 3:11
kat`a
pr'ojesin
t~wn
a>i'wnwn
<`hn
>epo'ihsen
>e\r{n}
\fn{\src{TMK}: en, \src{V}: en tw.}
qrist~w|
>ihso~u
t~w|
kur'iw|
<hm~wn\bibvsend
\vs Eph 3:12
>en
<~w|
>'eqomen
t`hn
parrhs'ian
ka`i
\r{t}`hn
\fn{\src{TMK}: thn, \src{V}: \bibempty.}
prosagwg`hn
>en
pepoij'hsei
di`a
t~hc
p'istewc
a>uto~u\bibvsend
\vs Eph 3:13
di`o
a>ito~umai
m`h
>e\r{k}kake~in
\fn{\src{TMK}: ekkakein, \src{V}: egkakein.}
>en
ta~ic
vjl'iyes'in
mou
<up`er
<um~wn
<'htic
>est`in
d'oxa
<um~wn\bibvsend
\vs Eph 3:14
to'utou
q'arin
k'amptw
t`a
g'onat'a
mou
pr`oc
t`on
pat'era
\r{t}o~u
\fn{\src{TMK}: tou kuriou hmwn ihsou qristou, \src{V}: \bibempty.}
kur'iou
<hm~wn
>ihso~u
qristo~u\bibvsend
\vs Eph 3:15
>ex
o<~u
p~asa
patri`a
>en
o>urano~ic
ka`i
>ep`i
g~hc
>onom'azetai\bibvsend
\vs Eph 3:16
<'ina
d'w|h\r{}
\fn{\src{TMK}: dwh, \src{V}: dw.}
<um~in
kat`a
t`on\r{}
\fn{\src{TMK}: ton plouton, \src{V}: to ploutoc.}
plo~uton
t~hc
d'oxhc
a>uto~u
dun'amei
krataiwj~hnai
di`a
to~u
pne'umatoc
a>uto~u
e>ic
t`on
>'esw
>'anjrwpon\bibvsend
\vs Eph 3:17
katoik~hsai
t`on
qrist`on
di`a
t~hc
p'istewc
>en
ta~ic
kard'iaic
<um~wn
>en
>ag'aph|
>errizwm'enoi
ka`i
tejemeliwm'enoi\bibvsend
\vs Eph 3:18
<'ina
>exisq'ushte
katalab'esjai
s`un
p~asin
to~ic
<ag'ioic
t'i
t`o
pl'atoc
ka`i
m~hkoc
ka`i
vb'ajoc\r{}
\fn{\src{TMK}: vbajoc kai uyoc, \src{V}: uyoc kai vbajoc.}
ka`i
<'uyoc\bibvsend
\vs Eph 3:19
gn~wna'i
te
t`hn
<uperb'allousan
t~hc
gn'wsewc
>ag'aphn
to~u
qristo~u
<'ina
plhrwj~hte
e>ic
p~an
t`o
pl'hrwma
to~u
vjeo~u\bibvsend
\vs Eph 3:20
t~w|
d`e
dunam'enw|
<up`er
p'anta
poi~hsai
<up`er\r{}
\fn{\src{T|K}: uper ek perissou, \src{M|V}: uperekperissou.}
>ek
perisso~u
<~wn
a>ito'umeja
>`h
noo~umen
kat`a
t`hn
d'unamin
t`hn
>energoum'enhn
>en
<hm~in\bibvsend
\vs Eph 3:21
a>ut~w|
<h
d'oxa
>en
t~h|
>ekklhs'ia|
>e\r{n}
\fn{\src{TMK}: en, \src{V}: kai en.}
qrist~w|
>ihso~u
e>ic
p'asac
t`ac
gene`ac
to~u
a>i~wnoc
t~wn
a>i'wnwn
>am'hn\bibvsend
\vs Eph 4:1
parakal~w
o>~un
<um~ac
>eg`w
<o
d'esmioc
>en
kur'iw|
>ax'iwc
peripat~hsai
t~hc
kl'hsewc
<~hc
>ekl'hjhte\bibvsend
\vs Eph 4:2
met`a
p'ashc
tapeinofros'unhc
ka`i
p\r{r}a|\-'o\-th\-toc
\fn{\src{TMK}: praothtoc, \src{V}: prauthtoc.}
met`a
makrojum'iac
>aneq'omenoi
>all'hlwn
>en
>ag'aph|\bibvsend
\vs Eph 4:3
spoud'azontec
thre~in
t`hn
<en'othta
to~u
pne'umatoc
>en
t~w|
sund'esmw|
t~hc
e>ir'hnhc\bibvsend
\vs Eph 4:4
<`en
s~wma
ka`i
<`en
pne~uma
kaj`wc
ka`i
>ekl'hjhte
>en
mi~a|
>elp'idi
t~hc
kl'hsewc
<um~wn\bibvsend
\vs Eph 4:5
e<~ic
k'urioc
m'ia
p'istic
<`en
vb'aptisma\bibvsend
\vs Eph 4:6
e<~ic
vje`oc
ka`i
pat`hr
p'antwn
<o
>ep`i
p'antwn
ka`i
di`a
p'antwn
ka`i
>en
p~asin
<u\r{m}~in\bibvsend
\fn{\src{T|K}: umin, \src{M}: hmin, \src{V}: \bibempty.}
\vs Eph 4:7
<en`i
d`e
<ek'astw|
<hm~wn
>ed'ojh
<h
q'aric
kat`a
t`o
m'etron
t~hc
dwre~ac
to~u
qristo~u\bibvsend
\vs Eph 4:8
di`o
l'egei
>anab`ac
e>ic
<'uyoc
>h|qmal'wteusen
a>iqmalws'ian
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
>'edwken
d'omata
to~ic
>anjr'wpoic\bibvsend
\vs Eph 4:9
t`o
d`e
>an'ebh
t'i
>estin
e>i
m`h
<'oti
ka`i
kat'ebh
p\r{r}~wton
\fn{\src{TMK}: prwton, \src{V}: \bibempty.}
e>ic
t`a
kat'wtera
m'erh
t~hc
g~hc\bibvsend
\vs Eph 4:10
<o
katab`ac
a>ut'oc
>estin
ka`i
<o
>anab`ac
<uper'anw
p'antwn
t~wn
o>uran~wn
<'ina
plhr'wsh|
t`a
p'anta\bibvsend
\vs Eph 4:11
ka`i
a>ut`oc
>'edwken
to`uc
m`en
>apost'olouc
to`uc
d`e
prof'htac
to`uc
d`e
e>uaggelist`ac
to`uc
d`e
poim'enac
ka`i
didask'alouc\bibvsend
\vs Eph 4:12
pr`oc
t`on
katartism`on
t~wn
<ag'iwn
e>ic
>'ergon
diakon'iac
e>ic
o>ikodom`hn
to~u
s'wmatoc
to~u
qristo~u\bibvsend
\vs Eph 4:13
m'eqri
katant'hswmen
o<i
p'antec
e>ic
t`hn
<en'othta
t~hc
p'istewc
ka`i
t~hc
>epign'wsewc
to~u
u<io~u
to~u
vjeo~u
e>ic
>'andra
t'eleion
e>ic
m'etron
<hlik'iac
to~u
plhr'wmatoc
to~u
qristo~u\bibvsend
\vs Eph 4:14
<'ina
mhk'eti
>~wmen
n'hpioi
kludwniz'omenoi
ka`i
perifer'omenoi
pant`i
>an'emw|
t~hc
didaskal'iac
>en
t~h|
kube'ia|
t~wn
>anjr'wpwn
>en
panourg'ia|
pr`oc
t`hn
mejode'ian
t~hc
pl'anhc\bibvsend
\vs Eph 4:15
>alhje'uontec
d`e
>en
>ag'aph|
a>ux'hswmen
e>ic
a>ut`on
t`a
p'anta
<'oc
>estin
<h
kefal`h
<o\r{}
\fn{\src{TMK}: o, \src{V}: \bibempty.}
qrist'oc\bibvsend
\vs Eph 4:16
>ex
o<~u
p~an
t`o
s~wma
sunarmologo'umenon
ka`i
sumbibaz'omenon
di`a
p'ashc
<af~hc
t~hc
>epiqorhg'iac
kat>
>en'ergeian
>en
m'etrw|
<en`oc
<ek'astou
m'erouc
t`hn
a>'uxhsin
to~u
s'wmatoc
poie~itai
e>ic
o>ikodom`hn
<eauto~u
>en
>ag'aph|\bibvsend
\vs Eph 4:17
to~uto
o>~un
l'egw
ka`i
mart'uromai
>en
kur'iw|
mhk'eti
<um~ac
peripate~in
kaj`wc
ka`i
t`a
l\r{o}ip`a
\fn{\src{TMK}: loipa, \src{V}: \bibempty.}
>'ejnh
peripate~i
>en
matai'othti
to~u
no`oc
a>ut~wn\bibvsend
\vs Eph 4:18
>eskoti\r{s}m'enoi
\fn{\src{TMK}: eskotismenoi, \src{V}: eskotwmenoi.}
t~h|
diano'ia|
>'ontec
>aphllotriwm'enoi
t~hc
vzw~hc
to~u
vjeo~u
di`a
t`hn
>'agnoian
t`hn
o>~usan
>en
a>uto~ic
di`a
t`hn
p'wrwsin
t~hc
kard'iac
a>ut~wn\bibvsend
\vs Eph 4:19
o<'itinec
>aphlghk'otec
<eauto`uc
par'edwkan
t~h|
>aselge'ia|
e>ic
>ergas'ian
>akajars'iac
p'ashc
>en
pleonex'ia|\bibvsend
\vs Eph 4:20
<ume~ic
d`e
o>uq
o<'utwc
>em'ajete
t`on
qrist'on\bibvsend
\vs Eph 4:21
e>'i\r{g}e
\fn{\src{T|K}: eige, \src{M|V}: ei ge.}
a>ut`on
>hko'usate
ka`i
>en
a>ut~w|
>edid'aqjhte
kaj'wc
>estin
>al'hjeia
>en
t~w|
>ihso~u\bibvsend
\vs Eph 4:22
>apoj'esjai
<um~ac
kat`a
t`hn
prot'eran
>anastrof`hn
t`on
palai`on
>'anjrwpon
t`on
vfjeir'omenon
kat`a
t`ac
>epijum'iac
t~hc
>ap'athc\bibvsend
\vs Eph 4:23
>ananeo~usjai
d`e
t~w|
pne'umati
to~u
no`oc
<um~wn\bibvsend
\vs Eph 4:24
ka`i
>end'usasjai
t`on
kain`on
>'anjrwpon
t`on
kat`a
vje`on
ktisj'enta
>en
dikaios'unh|
ka`i
<osi'othti
t~hc
>alhje'iac\bibvsend
\vs Eph 4:25
di`o
>apoj'emenoi
t`o
ye~udoc
lale~ite
>al'hjeian
<'ekastoc
met`a
to~u
plhs'ion
a>uto~u
<'oti
>esm`en
>all'hlwn
m'elh\bibvsend
\vs Eph 4:26
>org'izesje
ka`i
m`h
<amart'anete
<o
<'hlioc
m`h
>epidu'etw
>ep`i
t~w|
parorgism~w|
<um~wn\bibvsend
\vs Eph 4:27
m'h\r{t}e
\fn{\src{T|K}: mhte, \src{M|V}: mhde.}
d'idote
t'opon
t~w|
diab'olw|\bibvsend
\vs Eph 4:28
<o
kl'eptwn
mhk'eti
klept'etw
m~allon
d`e
kopi'atw
>ergaz'omenoc
t`o\r{}
\fn{\src{TMK}: to agajon taic qersin, \src{V}: taic [idiaic] qersin to agajon.}
>agaj`on
ta~ic
qers`in
<'ina
>'eqh|
metadid'onai
t~w|
qre'ian
>'eqonti\bibvsend
\vs Eph 4:29
p~ac
l'ogoc
sapr`oc
>ek
to~u
st'omatoc
<um~wn
m`h
>ekporeu'esjw
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
e>'i
tic
>agaj`oc
pr`oc
o>ikodom`hn
t~hc
qre'iac
<'ina
d~w|
q'arin
to~ic
>ako'uousin\bibvsend
\vs Eph 4:30
ka`i
m`h
lupe~ite
t`o
pne~uma
t`o
<'agion
to~u
vjeo~u
>en
<~w|
>esfrag'isjhte
e>ic
<hm'eran
>apolutr'wsewc\bibvsend
\vs Eph 4:31
p~asa
pikr'ia
ka`i
vjum`oc
ka`i
>org`h
ka`i
kraug`h
ka`i
vblasfhm'ia
>arj'htw
>af>
<um~wn
s`un
p'ash|
kak'ia|\bibvsend
\vs Eph 4:32
g'inesje
d`e
e>ic
>all'hlouc
qrhsto`i
e>'usplagqnoi
qariz'omenoi
<eauto~ic
kaj`wc
ka`i
<o
vje`oc
>en
qrist~w|
>eqar'isato
<u\r{m}~in\bibvsend
\fn{\src{T|K|V}: umin, \src{M}: hmin.}
\vs Eph 5:1
g'inesje
o>~un
mimhta`i
to~u
vjeo~u
<wc
t'ekna
>agapht'a\bibvsend
\vs Eph 5:2
ka`i
peripate~ite
>en
>ag'aph|
kaj`wc
ka`i
<o
qrist`oc
>hg'aphsen
<hm~ac
ka`i
par'edwken
<eaut`on
<up`er
<hm~wn
prosfor`an
ka`i
vjus'ian
t~w|
vje~w|
e>ic
>osm`hn
e>uwd'iac\bibvsend
\vs Eph 5:3
porne'ia
d`e
ka`i
p~asa\r{}
\fn{\src{TMK}: pasa akajarsia, \src{V}: akajarsia pasa.}
>akajars'ia
>`h
pleonex'ia
mhd`e
>onomaz'esjw
>en
<um~in
kaj`wc
pr'epei
<ag'ioic\bibvsend
\vs Eph 5:4
ka`i
a>isqr'othc
ka`i
mwrolog'ia
>`h
e>utrapel'ia
t`a\r{}
\fn{\src{TMK}: ta ouk anhkonta, \src{V}: a ouk anhken.}
o>uk
>an'hkonta
>all`a
m~allon
e>uqarist'ia\bibvsend
\vs Eph 5:5
to~uto
g'ar
>e\r{s}te
\fn{\src{TMK}: este, \src{V}: iste.}
gin'wskontec
<'oti
p~ac
p'ornoc
>`h
>ak'ajartoc
>`h
pleon'ekthc
<'o\r{c}
\fn{\src{TMK}: oc, \src{V}: o.}
>estin
e>idwlol'atrhc
o>uk
>'eqei
klhronom'ian
>en
t~h|
vbasile'ia|
to~u
qristo~u
ka`i
vjeo~u\bibvsend
\vs Eph 5:6
mhde`ic
<um~ac
>apat'atw
keno~ic
l'ogoic
di`a
ta~uta
g`ar
>'erqetai
<h
>org`h
to~u
vjeo~u
>ep`i
to`uc
u<io`uc
t~hc
>apeije'iac\bibvsend
\vs Eph 5:7
m`h
o>~un
g'inesje
summ'etoqoi
a>ut~wn\bibvsend
\vs Eph 5:8
>~hte
g'ar
pote
sk'otoc
n~un
d`e
vf~wc
>en
kur'iw|
<wc
t'ekna
vfwt`oc
peripate~ite\bibvsend
\vs Eph 5:9
<o
g`ar
karp`oc
to~u
pne'u\r{m}atoc
\fn{\src{TMK}: pneumatoc, \src{V}: vfwtoc.}
>en
p'ash|
>agajws'unh|
ka`i
dikaios'unh|
ka`i
>alhje'ia|\bibvsend
\vs Eph 5:10
dokim'azontec
t'i
>estin
e>u'areston
t~w|
kur'iw|\bibvsend
\vs Eph 5:11
ka`i
m`h
sugkoinwne~ite
to~ic
>'ergoic
to~ic
>ak'arpoic
to~u
sk'otouc
m~allon
d`e
ka`i
>el'egqete\bibvsend
\vs Eph 5:12
t`a
g`ar
kruf~h
gin'omena
<up>
a>ut~wn
a>isqr'on
>estin
ka`i
l'egein\bibvsend
\vs Eph 5:13
t`a
d`e
p'anta
>elegq'omena
<up`o
to~u
vfwt`oc
vfanero~utai
p~an
g`ar
t`o
vfanero'umenon
vf~wc
>estin\bibvsend
\vs Eph 5:14
di`o
l'egei
>'egeir\r{a}i
\fn{\src{T|K}: egeirai, \src{M|V}: egeire.}
<o
kaje'udwn
ka`i
>an'asta
>ek
t~wn
nekr~wn
ka`i
>epifa'usei
soi
<o
qrist'oc\bibvsend
\vs Eph 5:15
vbl'epete
o>~un
p~wc\r{}
\fn{\src{TMK}: pwc akribwc, \src{V}: akribwc pwc.}
>akrib~wc
peripate~ite
m`h
<wc
>'asofoi
>all>
<wc
sofo'i\bibvsend
\vs Eph 5:16
>exagoraz'omenoi
t`on
kair`on
<'oti
a<i
<hm'erai
ponhra'i
e>isin\bibvsend
\vs Eph 5:17
di`a
to~uto
m`h
g'inesje
>'afronec
>all`a
suni'e\r{n}tec
\fn{\src{TMK}: sunientec, \src{V}: suniete.}
t'i
t`o
vj'elhma
to~u
kur'iou\bibvsend
\vs Eph 5:18
ka`i
m`h
mej'uskesje
o>'inw|
>en
<~w|
>estin
>aswt'ia
>all`a
plhro~usje
>en
pne'umati\bibvsend
\vs Eph 5:19
lalo~untec
<eauto~ic
\r{y}almo~ic
\fn{\src{TMK}: yalmoic, \src{V}: [en] yalmoic.}
ka`i
<'umnoic
ka`i
>w|da~ic
pneumatika~ic
>'a|dontec
ka`i
y'allontec
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
t~h|
kard'ia|
<um~wn
t~w|
kur'iw|\bibvsend
\vs Eph 5:20
e>uqaristo~untec
p'antote
<up`er
p'antwn
>en
>on'omati
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
t~w|
vje~w|
ka`i
patr'i\bibvsend
\vs Eph 5:21
<upotass'omenoi
>all'hloic
>en
vf'obw|
vje\r{o}~u\bibvsend
\fn{\src{TMK}: vjeou, \src{V}: qristou.}
\vs Eph 5:22
a<i
guna~ikec
to~ic
>id'ioic
>andr'asin
<upot'a\r{s}sesje
\fn{\src{TMK}: upotassesje, \src{V}: \bibempty.}
<wc
t~w|
kur'iw|\bibvsend
\vs Eph 5:23
<'oti
<o\r{}
\fn{\src{T|K}: o, \src{M|V}: \bibempty.}
>an'hr
>estin
kefal`h
t~hc
gunaik`oc
<wc
ka`i
<o
qrist`oc
kefal`h
t~hc
>ekklhs'iac
ka`i\r{}
\fn{\src{TMK}: kai autoc estin, \src{V}: autoc.}
a>ut'oc
>estin
swt`hr
to~u
s'wmatoc\bibvsend
\vs Eph 5:24
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<'ws\r{p}er
\fn{\src{TMK}: wsper, \src{V}: wc.}
<h
>ekklhs'ia
<upot'assetai
t~w|
qrist~w|
o<'utwc
ka`i
a<i
guna~ikec
to~ic
>id'i\r{o}ic
\fn{\src{TMK}: idioic, \src{V}: \bibempty.}
>andr'asin
>en
pant'i\bibvsend
\vs Eph 5:25
o<i
>'andrec
>agap~ate
t`ac
guna~ikac
<ea\r{u}t~wn
\fn{\src{TMK}: eautwn, \src{V}: \bibempty.}
kaj`wc
ka`i
<o
qrist`oc
>hg'aphsen
t`hn
>ekklhs'ian
ka`i
<eaut`on
par'edwken
<up`er
a>ut~hc\bibvsend
\vs Eph 5:26
<'ina
a>ut`hn
<agi'ash|
kajar'isac
t~w|
loutr~w|
to~u
<'udatoc
>en
<r'hmati\bibvsend
\vs Eph 5:27
<'ina
parast'hsh|
a>ut`h\r{n}
\fn{\src{TMK}: authn, \src{V}: autoc.}
<eaut~w|
>'endoxon
t`hn
>ekklhs'ian
m`h
>'eqousan
sp~ilon
>`h
<rut'ida
>'h
ti
t~wn
toio'utwn
>all>
<'ina
>~h|
<ag'ia
ka`i
>'amwmoc\bibvsend
\vs Eph 5:28
o<'utwc
>ofe'ilousin
\r{o}<i
\fn{\src{TMK}: oi, \src{V}: [kai] oi.}
>'andrec
>agap~a|n
t`ac
<eaut~wn
guna~ikac
<wc
t`a
<eaut~wn
s'wmata
<o
>agap~wn
t`hn
<eauto~u
guna~ika
<eaut`on
>agap~a|\bibvsend
\vs Eph 5:29
o>ude`ic
g'ar
pote
t`hn
<eauto~u
s'arka
>em'ishsen
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
>ektr'efei
ka`i
vj'alpei
a>ut`hn
kaj`wc
ka`i
<o
k'u\r{r}ioc
\fn{\src{TMK}: kurioc, \src{V}: qristoc.}
t`hn
>ekklhs'ian\bibvsend
\vs Eph 5:30
<'oti
m'elh
>esm`en
to~u
s'wmatoc
a>uto~u
>ek\r{}
\fn{\src{TMK}: ek thc sarkoc autou kai ek twn ostewn autou, \src{V}: \bibempty.}
t~hc
sark`oc
a>uto~u
ka`i
>ek
t~wn
>ost'ewn
a>uto~u\bibvsend
\vs Eph 5:31
>ant`i
to'utou
katale'iyei
>'anjrwpoc
t`on
pat'era
a>u\r{t}o~u
\fn{\src{TMK}: autou, \src{V}: \bibempty.}
ka`i
t`hn
mht'era
ka`i
proskollhj'hsetai
pr`oc
t`hn
guna~ika
a>uto~u
ka`i
>'esontai
o<i
d'uo
e>ic
s'arka
m'ian\bibvsend
\vs Eph 5:32
t`o
must'hrion
to~uto
m'ega
>est`in
>eg`w
d`e
l'egw
e>ic
qrist`on
ka`i
e>ic
t`hn
>ekklhs'ian\bibvsend
\vs Eph 5:33
pl`hn
ka`i
<ume~ic
o<i
kaj>
<'ena
<'ekastoc
t`hn
<eauto~u
guna~ika
o<'utwc
>agap'atw
<wc
<eaut`on
<h
d`e
gun`h
<'ina
vfob~htai
t`on
>'andra\bibvsend
\vs Eph 6:1
t`a
t'ekna
<upako'uete
to~ic
gone~usin
<um~wn
>en
kur'iw|
to~uto
g'ar
>estin
d'ikaion\bibvsend
\vs Eph 6:2
t'ima
t`on
pat'era
sou
ka`i
t`hn
mht'era
<'htic
>est`in
>entol`h
pr'wth
>en
>epaggel'ia|\bibvsend
\vs Eph 6:3
<'ina
e>~u
soi
g'enhtai
ka`i
>'esh|
makroqr'onioc
>ep`i
t~hc
g~hc\bibvsend
\vs Eph 6:4
ka`i
o<i
pat'erec
m`h
parorg'izete
t`a
t'ekna
<um~wn
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
>ektr'efete
a>ut`a
>en
paide'ia|
ka`i
noujes'ia|
kur'iou\bibvsend
\vs Eph 6:5
o<i
do~uloi
<upako'uete
to~ic
kur'ioic\r{}
\fn{\src{TMK}: kurioic kata sarka, \src{V}: kata sarka kurioic.}
kat`a
s'arka
met`a
vf'obou
ka`i
tr'omou
>en
<apl'othti
t~hc
kard'iac
<um~wn
<wc
t~w|
qrist~w|\bibvsend
\vs Eph 6:6
m`h
kat>
>ofjalmodoul\r{e}'ian
\fn{\src{TMK}: ofjalmodouleian, \src{V}: ofjalmodoulian.}
<wc
>anjrwp'areskoi
>all>
<wc
do~uloi
t\r{o}~u
\fn{\src{TMK}: tou, \src{V}: \bibempty.}
qristo~u
poio~untec
t`o
vj'elhma
to~u
vjeo~u
>ek
yuq~hc\bibvsend
\vs Eph 6:7
met>
e>uno'iac
doule'uontec
\r{t}~w|
\fn{\src{T}: tw, \src{K|M|V}: wc tw.}
kur'iw|
ka`i
o>uk
>anjr'wpoic\bibvsend
\vs Eph 6:8
e>id'otec
<'oti
<`o\r{}
\fn{\src{T|K}: o ean ti ekastoc, \src{M}: ean ti ekastoc, \src{V}: ekastoc ean ti.}
>e'an
ti
<'ekastoc
poi'hsh|
>agaj`on
to~uto
komie~itai\r{}
\fn{\src{TMK}: komieitai para tou, \src{V}: komisetai para.}
par`a
to~u
kur'iou
e>'ite
do~uloc
e>'ite
>ele'ujeroc\bibvsend
\vs Eph 6:9
ka`i
o<i
k'urioi
t`a
a>ut`a
poie~ite
pr`oc
a>uto`uc
>ani'entec
t`hn
>apeil`hn
e>id'otec
<'oti
ka`i\r{}
\fn{\src{TMK}: kai umwn autwn, \src{V}: kai autwn kai umwn.}
<um~wn
a>ut~wn
<o
k'uri'oc
>estin
>en
o>urano~ic
ka`i
proswpolh\r{y}'ia
\fn{\src{TMK}: proswpolhyia, \src{V}: proswpolhmyia.}
o>uk
>'estin
par>
a>ut~w|\bibvsend
\vs Eph 6:10
t`o\r{}
\fn{\src{TMK}: to loipon adelfoi mou, \src{V}: tou loipou.}
loip`on
>adelfo'i
mou
>endunamo~usje
>en
kur'iw|
ka`i
>en
t~w|
kr'atei
t~hc
>isq'uoc
a>uto~u\bibvsend
\vs Eph 6:11
>end'usasje
t`hn
panopl'ian
to~u
vjeo~u
pr`oc
t`o
d'unasjai
<um~ac
st~hnai
pr`oc
t`ac
mejode'iac
to~u
diab'olou\bibvsend
\vs Eph 6:12
<'oti
o>uk
>'estin
<hm~in
<h
p'alh
pr`oc
a<~ima
ka`i
s'arka
>all`a
pr`oc
t`ac
>arq`ac
pr`oc
t`ac
>exous'iac
pr`oc
to`uc
kosmokr'atorac
to~u
sk'otouc
to~u\r{}
\fn{\src{TMK}: tou aiwnoc, \src{V}: \bibempty.}
a>i~wnoc
to'utou
pr`oc
t`a
pneumatik`a
t~hc
ponhr'iac
>en
to~ic
>epouran'ioic\bibvsend
\vs Eph 6:13
di`a
to~uto
>anal'abete
t`hn
panopl'ian
to~u
vjeo~u
<'ina
dunhj~hte
>antist~hnai
>en
t~h|
<hm'era|
t~h|
ponhr~a|
ka`i
<'apanta
katergas'amenoi
st~hnai\bibvsend
\vs Eph 6:14
st~hte
o>~un
perizws'amenoi
t`hn
>osf`un
<um~wn
>en
>alhje'ia|
ka`i
>endus'amenoi
t`on
vj'wraka
t~hc
dikaios'unhc\bibvsend
\vs Eph 6:15
ka`i
<upodhs'amenoi
to`uc
p'odac
>en
<etoimas'ia|
to~u
e>uaggel'iou
t~hc
e>ir'hnhc\bibvsend
\vs Eph 6:16
>e\r{p}`i
\fn{\src{TMK}: epi, \src{V}: en.}
p~asin
>analab'ontec
t`on
vjure`on
t~hc
p'istewc
>en
<~w|
dun'hsesje
p'anta
t`a
vb'elh
to~u
ponhro~u
t`a
pepurwm'ena
sb'esai\bibvsend
\vs Eph 6:17
ka`i
t`hn
perikefala'ian
to~u
swthr'iou
d'exasj\r{e}
\fn{\src{T|K|V}: dexasje, \src{M}: dexasjai.}
ka`i
t`hn
m'aqairan
to~u
pne'umatoc
<'o
>estin
<r~hma
vjeo~u\bibvsend
\vs Eph 6:18
di`a
p'ashc
proseuq~hc
ka`i
de'hsewc
proseuq'omenoi
>en
pant`i
kair~w|
>en
pne'umati
ka`i
e>ic
a>ut`o
t\r{o}~uto
\fn{\src{TMK}: touto, \src{V}: \bibempty.}
>agrupno~untec
>en
p'ash|
proskarter'hsei
ka`i
de'hsei
per`i
p'antwn
t~wn
<ag'iwn\bibvsend
\vs Eph 6:19
ka`i
<up`er
>emo~u
<'ina
moi
doj\r{e}'ih
\fn{\src{T|K}: dojeih, \src{M|V}: dojh.}
l'ogoc
>en
>ano'ixei
to~u
st'omat'oc
mou
>en
parrhs'ia|
gnwr'isai
t`o
must'hrion
to~u
e>uaggel'iou\bibvsend
\vs Eph 6:20
<up`er
o<~u
presbe'uw
>en
<al'usei
<'ina
>en
a>ut~w|
parrhsi'aswmai
<wc
de~i
me
lal~hsai\bibvsend
\vs Eph 6:21
<'ina
d`e
e>id~hte
ka`i
<ume~ic
t`a
kat>
>em`e
t'i
pr'assw
p'anta
<um~in\r{}
\fn{\src{TMK}: umin gnwrisei, \src{V}: gnwrisei umin.}
gnwr'isei
tuqik`oc
<o
>agapht`oc
>adelf`oc
ka`i
pist`oc
di'akonoc
>en
kur'iw|\bibvsend
\vs Eph 6:22
<`on
>'epemya
pr`oc
<um~ac
e>ic
a>ut`o
to~uto
<'ina
gn~wte
t`a
per`i
<hm~wn
ka`i
parakal'esh|
t`ac
kard'iac
<um~wn\bibvsend
\vs Eph 6:23
e>ir'hnh
to~ic
>adelfo~ic
ka`i
>ag'aph
met`a
p'istewc
>ap`o
vjeo~u
patr`oc
ka`i
kur'iou
>ihso~u
qristo~u\bibvsend
\vs Eph 6:24
<h
q'aric
met`a
p'antwn
t~wn
>agap'wntwn
t`on
k'urion
<hm~wn
>ihso~un
qrist`on
>en
>afjars'ia|
>a\r{m}'hn\bibvsend
\fn{\src{T|M}: amhn, \src{K|V}: \bibempty.}
Pr`oc\r{}
\fn{\src{T}: Proc \ldots\ tuqikou, \src{K|M|V}: \bibempty.}
>efes'iouc
>egr'afh
>ap`o
<r'wmhc
di`a
tuqiko~u\bibvsend
