\bibbook{H PROS GALATAS\\\LARGE EPISTOLH PAULOU\r{}}{PROS GALATAS}{Galatians}{Gal}[PROS GALATAS]
\vs Gal 1:1
pa~uloc
\fnt{\src{T}: H PROS GALATAS EPISTOLH PAULOU, \src{K}: PAULOU H PROS GALATAS EPISTOLH, \src{M|V}: PROS GALATAS.}
>ap'ostoloc
o>uk
>ap>
>anjr'wpwn
o>ud`e
di>
>anjr'wpou
>all`a
di`a
>ihso~u
qristo~u
ka`i
vjeo~u
patr`oc
to~u
>ege'irantoc
a>ut`on
>ek
nekr~wn\bibvsend
\vs Gal 1:2
ka`i
o<i
s`un
>emo`i
p'antec
>adelfo`i
ta~ic
>ekklhs'iaic
t~hc
galat'iac\bibvsend
\vs Gal 1:3
q'aric
<um~in
ka`i
e>ir'hnh
>ap`o
vjeo~u
patr`oc
ka`i\r{}
\fn{\src{TMK}: kai kuriou hmwn, \src{V}: hmwn kai kuriou.}
kur'iou
<hm~wn
>ihso~u
qristo~u\bibvsend
\vs Gal 1:4
to~u
d'ontoc
<eaut`on
<u\r{p}`er
\fn{\src{T|K|V}: uper, \src{M}: peri.}
t~wn
<amarti~wn
<hm~wn
<'opwc
>ex'elhtai
<hm~ac
>ek
to~u
>enest~wtoc\r{}
\fn{\src{TMK}: enestwtoc aiwnoc, \src{V}: aiwnoc tou enestwtoc.}
a>i~wnoc
ponhro~u
kat`a
t`o
vj'elhma
to~u
vjeo~u
ka`i
patr`oc
<hm~wn\bibvsend
\vs Gal 1:5
<~w|
<h
d'oxa
e>ic
to`uc
a>i~wnac
t~wn
a>i'wnwn
>am'hn\bibvsend
\vs Gal 1:6
vjaum'azw
<'oti
o<'utwc
taq'ewc
metat'ijesje
>ap`o
to~u
kal'esantoc
<um~ac
>en
q'ariti
qristo~u
e>ic
<'eteron
e>uagg'elion\bibvsend
\vs Gal 1:7
<`o
o>uk
>'estin
>'allo
e>i
m'h
tin'ec
e>isin
o<i
tar'assontec
<um~ac
ka`i
vj'elontec
metastr'eyai
t`o
e>uagg'elion
to~u
qristo~u\bibvsend
\vs Gal 1:8
>all`a
ka`i
>e`an
<hme~ic
>`h
>'aggeloc
>ex
o>urano~u
e>uaggel'iz\r{h}tai
\fn{\src{T|K|V}: euaggelizhtai, \src{M}: euaggelizetai.}
<um~in
par>
<`o
e>uhggelis'ameja
<um~in
>an'ajema
>'estw\bibvsend
\vs Gal 1:9
<wc
proeir'hkamen
ka`i
>'arti
p'alin
l'egw
e>'i
tic
<um~ac
e>uaggel'izetai
par>
<`o
parel'abete
>an'ajema
>'estw\bibvsend
\vs Gal 1:10
>'arti
g`ar
>anjr'wpouc
pe'ijw
>`h
t`on
vje`on
>`h
vzht~w
>anjr'wpoic
>ar'eskein
e>i
\r{g}`ar
\fn{\src{TMK}: gar, \src{V}: \bibempty.}
>'eti
>anjr'wpoic
>'hreskon
qristo~u
do~uloc
o>uk
>`an
>'hmhn\bibvsend
\vs Gal 1:11
gnwr'izw
d`e\r{}
\fn{\src{TMK}: de, \src{V}: gar.}
<um~in
>adelfo`i
t`o
e>uagg'elion
t`o
e>uaggelisj`en
<up>
>emo~u
<'oti
o>uk
>'estin
kat`a
>'anjrwpon\bibvsend
\vs Gal 1:12
o>ud`e
g`ar
>eg`w
par`a
>anjr'wpou
par'elabon
a>ut`o
o>'ute
>edid'aqjhn
>all`a
di>
>apokal'uyewc
>ihso~u
qristo~u\bibvsend
\vs Gal 1:13
>hko'usate
g`ar
t`hn
>em`hn
>anastrof'hn
pote
>en
t~w|
>iouda"ism~w|
<'oti
kaj>
<uperbol`hn
>ed'iwkon
t`hn
>ekklhs'ian
to~u
vjeo~u
ka`i
>ep'orjoun
a>ut'hn\bibvsend
\vs Gal 1:14
ka`i
pro'ekopton
>en
t~w|
>iouda"ism~w|
<up`er
pollo`uc
sunhliki'wtac
>en
t~w|
g'enei
mou
perissot'erwc
vzhlwt`hc
<up'arqwn
t~wn
patrik~wn
mou
parad'osewn\bibvsend
\vs Gal 1:15
<'ote
d`e
e>ud'okhsen
<o
vje`oc
<o
>afor'isac
me
>ek
koil'iac
mhtr'oc
mou
ka`i
kal'esac
di`a
t~hc
q'aritoc
a>uto~u\bibvsend
\vs Gal 1:16
>apokal'uyai
t`on
u<i`on
a>uto~u
>en
>emo`i
<'ina
e>uaggel'izwmai
a>ut`on
>en
to~ic
>'ejnesin
e>uj'ewc
o>u
prosanej'emhn
sark`i
ka`i
a<'imati\bibvsend
\vs Gal 1:17
o>ud`e
>an~hljon
e>ic
<ieros'oluma
pr`oc
to`uc
pr`o
>emo~u
>apost'olouc
>al\r{l}>
\fn{\src{T|K}: all, \src{M|V}: alla.}
>ap~hljon
e>ic
>arab'ian
ka`i
p'alin
<up'estreya
e>ic
damask'on\bibvsend
\vs Gal 1:18
>'epeita
met`a
>'eth
tr'ia
>an~hljon
e>ic
<ieros'oluma
<istor~hsai
p'e\r{t}ron
\fn{\src{TMK}: petron, \src{V}: khfan.}
ka`i
>ep'emeina
pr`oc
a>ut`on
<hm'erac
dekap'ente\bibvsend
\vs Gal 1:19
<'eteron
d`e
t~wn
>apost'olwn
o>uk
e>~idon
e>i
m`h
>i'akwbon
t`on
>adelf`on
to~u
kur'iou\bibvsend
\vs Gal 1:20
<`a
d`e
gr'afw
<um~in
>ido`u
>en'wpion
to~u
vjeo~u
<'oti
o>u
ye'udomai\bibvsend
\vs Gal 1:21
>'epeita
>~hljon
e>ic
t`a
kl'imata
t~hc
sur'iac
ka`i
t~hc
kilik'iac\bibvsend
\vs Gal 1:22
>'hmhn
d`e
>agnoo'umenoc
t~w|
pros'wpw|
ta~ic
>ekklhs'iaic
t~hc
>iouda'iac
ta~ic
>en
qrist~w|\bibvsend
\vs Gal 1:23
m'onon
d`e
>ako'uontec
>~hsan
<'oti
<o
di'wkwn
<hm~ac
pote
n~un
e>uaggel'izetai
t`hn
p'istin
<'hn
pote
>ep'orjei\bibvsend
\vs Gal 1:24
ka`i
>ed'oxazon
>en
>emo`i
t`on
vje'on\bibvsend
\vs Gal 2:1
>'epeita
di`a
dekatess'arwn
>et~wn
p'alin
>an'ebhn
e>ic
<ieros'oluma
met`a
vbarn'aba
sumparalab`wn
ka`i
t'iton\bibvsend
\vs Gal 2:2
>an'ebhn
d`e
kat`a
>apok'aluyin
ka`i
>anej'emhn
a>uto~ic
t`o
e>uagg'elion
<`o
khr'ussw
>en
to~ic
>'ejnesin
kat>
>id'ian
d`e
to~ic
doko~usin
m'h
pwc
e>ic
ken`on
tr'eqw
>`h
>'edramon\bibvsend
\vs Gal 2:3
>all>
o>ud`e
t'itoc
<o
s`un
>emo`i
<'ellhn
>`wn
>hnagk'asjh
peritmhj~hnai\bibvsend
\vs Gal 2:4
di`a
d`e
to`uc
pareis'aktouc
yeudad'elfouc
o<'itinec
pareis~hljon
kataskop~hsai
t`hn
>eleujer'ian
<hm~wn
<`hn
>'eqomen
>en
qrist~w|
>ihso~u
<'ina
<hm~ac
katadoul'ws\r{w}ntai\bibvsend
\fn{\src{TMK}: katadoulwswntai, \src{V}: katadoulwsousin.}
\vs Gal 2:5
o<~ic
o>ud`e
pr`oc
<'wran
e>'ixamen
t~h|
<upotag~h|
<'ina
<h
>al'hjeia
to~u
e>uaggel'iou
diame'inh|
pr`oc
<um~ac\bibvsend
\vs Gal 2:6
>ap`o
d`e
t~wn
doko'untwn
e>~ina'i
ti
<opo~io'i
pote
>~hsan
o>ud'en
moi
diaf'erei
pr'oswpon
vj\r{e}`oc
\fn{\src{TMK}: vjeoc, \src{V}: [o] vjeoc.}
>anjr'wpou
o>u
lamb'anei
>emo`i
g`ar
o<i
doko~untec
o>ud`en
prosan'ejento\bibvsend
\vs Gal 2:7
>all`a
to>unant'ion
>id'ontec
<'oti
pep'isteumai
t`o
e>uagg'elion
t~hc
>akrobust'iac
kaj`wc
p'etroc
t~hc
peritom~hc\bibvsend
\vs Gal 2:8
<o
g`ar
>energ'hsac
p'etrw|
e>ic
>apostol`hn
t~hc
peritom~hc
>en'hrghsen
ka`i
>emo`i
e>ic
t`a
>'ejnh\bibvsend
\vs Gal 2:9
ka`i
gn'ontec
t`hn
q'arin
t`hn
doje~is'an
moi
>i'akwboc
ka`i
khf~ac
ka`i
>iw'annhc
o<i
doko~untec
st'uloi
e>~inai
dexi`ac
>'edwkan
>emo`i
ka`i
vbarn'aba|
koinwn'iac
<'ina
<hme~ic
e>ic
t`a
>'ejnh
a>uto`i
d`e
e>ic
t`hn
peritom'hn\bibvsend
\vs Gal 2:10
m'onon
t~wn
ptwq~wn
<'ina
mnhmone'uwmen
<`o
ka`i
>espo'udasa
a>ut`o
to~uto
poi~hsai\bibvsend
\vs Gal 2:11
<'ote
d`e
>~hljen
p'e\r{t}roc
\fn{\src{TMK}: petroc, \src{V}: khfac.}
e>ic
>anti'oqeian
kat`a
pr'oswpon
a>ut~w|
>ant'esthn
<'oti
kategnwsm'enoc
>~hn\bibvsend
\vs Gal 2:12
pr`o
to~u
g`ar
>elje~in
tinac
>ap`o
>iak'wbou
met`a
t~wn
>ejn~wn
sun'hsjien
<'ote
d`e
>~hljon
<up'estellen
ka`i
>af'wrizen
<eaut`on
vfobo'umenoc
to`uc
>ek
peritom~hc\bibvsend
\vs Gal 2:13
ka`i
sunupekr'ijhsan
a>ut~w|
ka`i
o<i
loipo`i
>iouda~ioi
<'wste
ka`i
vbarn'abac
sunap'hqjh
a>ut~wn
t~h|
<upokr'isei\bibvsend
\vs Gal 2:14
>all>
<'ote
e>~idon
<'oti
o>uk
>orjopodo~usin
pr`oc
t`hn
>al'hjeian
to~u
e>uaggel'iou
e>~ipon
t~w|
p'e\r{t}rw|
\fn{\src{TMK}: petrw, \src{V}: khfa.}
>'emprosjen
p'antwn
e>i
s`u
>iouda~ioc
<up'arqwn
>ejnik~wc
vz~h|c\r{}
\fn{\src{TMK}: vzhc kai ouk ioudaikwc ti, \src{V}: kai ouqi ioudaikwc vzhc pwc.}
ka`i
o>uk
>iouda"ik~wc
t'i
t`a
>'ejnh
>anagk'azeic
>iouda"'izein\bibvsend
\vs Gal 2:15
<hme~ic
vf'usei
>iouda~ioi
ka`i
o>uk
>ex
>ejn~wn
<amartwlo'i\bibvsend
\vs Gal 2:16
e>id'ote\r{c}
\fn{\src{TMK}: eidotec, \src{V}: eidotec [de].}
<'oti
o>u
dikaio~utai
>'anjrwpoc
>ex
>'ergwn
n'omou
>e`an
m`h
di`a
p'istewc
>ihso~u
qristo~u
ka`i
<hme~ic
e>ic
qrist`on
>ihso~un
>episte'usamen
<'ina
dikaiwj~wmen
>ek
p'istewc
qristo~u
ka`i
o>uk
>ex
>'ergwn
n'omou
di'oti\r{}
\fn{\src{TMK}: dioti ou dikaiwjhsetai ex ergwn nomou, \src{V}: oti ex ergwn nomou ou dikaiwjhsetai.}
o>u
dikaiwj'hsetai
>ex
>'ergwn
n'omou
p~asa
s'arx\bibvsend
\vs Gal 2:17
e>i
d`e
vzhto~untec
dikaiwj~hnai
>en
qrist~w|
e<ur'ejhmen
ka`i
a>uto`i
<amartwlo`i
>~ara
qrist`oc
<amart'iac
di'akonoc
m`h
g'enoito\bibvsend
\vs Gal 2:18
e>i
g`ar
<`a
kat'elusa
ta~uta
p'alin
o>ikodom~w
parab'athn
>emaut`on
sun'ist\r{h}mi\bibvsend
\fn{\src{TMK}: sunisthmi, \src{V}: sunistanw.}
\vs Gal 2:19
>eg`w
g`ar
di`a
n'omou
n'omw|
>ap'ejanon
<'ina
vje~w|
vz'hsw\bibvsend
\vs Gal 2:20
qrist~w|
sunesta'urwmai
vz~w
d`e
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
>eg`w
vz~h|
d`e
>en
>emo`i
qrist`oc
<`o
d`e
n~un
vz~w
>en
sark`i
>en
p'istei
vz~w
t~h|
to~u
u<io~u
to~u
vjeo~u
to~u
>agap'hsant'oc
me
ka`i
parad'ontoc
<eaut`on
<up`er
>emo~u\bibvsend
\vs Gal 2:21
o>uk
>ajet~w
t`hn
q'arin
to~u
vjeo~u
e>i
g`ar
di`a
n'omou
dikaios'unh
>'ara
qrist`oc
dwre`an
>ap'ejanen\bibvsend
\vs Gal 3:1
>~w
>an'ohtoi
gal'atai
t'ic
<um~ac
>eb'askanen
t~h|\r{}
\fn{\src{TMK}: th alhjeia mh peijesjai, \src{V}: \bibempty.}
>alhje'ia|
m`h
pe'ijesjai
o<~ic
kat>
>ofjalmo`uc
>ihso~uc
qrist`oc
proegr'afh
>en\r{}
\fn{\src{TMK}: en umin, \src{V}: \bibempty.}
<um~in
>estaurwm'enoc\bibvsend
\vs Gal 3:2
to~uto
m'onon
vj'elw
maje~in
>af>
<um~wn
>ex
>'ergwn
n'omou
t`o
pne~uma
>el'abete
>`h
>ex
>ako~hc
p'istewc\bibvsend
\vs Gal 3:3
o<'utwc
>an'ohto'i
>este
>enarx'amenoi
pne'umati
n~un
sark`i
>epitele~isje\bibvsend
\vs Gal 3:4
tosa~uta
>ep'ajete
e>ik~h
e>'i
ge
ka`i
e>ik~h\bibvsend
\vs Gal 3:5
<o
o>~un
>epiqorhg~wn
<um~in
t`o
pne~uma
ka`i
>energ~wn
dun'ameic
>en
<um~in
>ex
>'ergwn
n'omou
>`h
>ex
>ako~hc
p'istewc\bibvsend
\vs Gal 3:6
kaj`wc
>abra`am
>ep'isteusen
t~w|
vje~w|
ka`i
>elog'isjh
a>ut~w|
e>ic
dikaios'unhn\bibvsend
\vs Gal 3:7
gin'wskete
>'ara
<'oti
o<i
>ek
p'istewc
o<~uto'i
e>isin\r{}
\fn{\src{TMK}: eisin uioi, \src{V}: uioi eisin.}
u<io`i
>abra'am\bibvsend
\vs Gal 3:8
pro"ido~usa
d`e
<h
graf`h
<'oti
>ek
p'istewc
dikaio~i
t`a
>'ejnh
<o
vje`oc
proeuhggel'isato
t~w|
>abra`am
<'oti
>e\r{n}euloghj'hsontai
\fn{\src{T|M|V}: eneuloghjhsontai, \src{K}: euloghjhsontai.}
>en
so`i
p'anta
t`a
>'ejnh\bibvsend
\vs Gal 3:9
<'wste
o<i
>ek
p'istewc
e>ulogo~untai
s`un
t~w|
pist~w|
>abra'am\bibvsend
\vs Gal 3:10
<'osoi
g`ar
>ex
>'ergwn
n'omou
e>is`in
<up`o
kat'aran
e>is`in
g'egraptai
g`a\r{r}
\fn{\src{TMK}: gar, \src{V}: gar oti.}
>epikat'aratoc
p~ac
<`oc
o>uk
>emm'enei
>e\r{n}
\fn{\src{TMK}: en, \src{V}: \bibempty.}
p~asin
to~ic
gegramm'enoic
>en
t~w|
vbibl'iw|
to~u
n'omou
to~u
poi~hsai
a>ut'a\bibvsend
\vs Gal 3:11
<'oti
d`e
>en
n'omw|
o>ude`ic
dikaio~utai
par`a
t~w|
vje~w|
d~hlon
<'oti
<o
d'ikaioc
>ek
p'istewc
vz'hsetai\bibvsend
\vs Gal 3:12
<o
d`e
n'omoc
o>uk
>'estin
>ek
p'istewc
>all>
<o
poi'hsac
a>ut`a
>'a\r{n}jrwpoc
\fn{\src{TMK}: anjrwpoc, \src{V}: \bibempty.}
vz'hsetai
>en
a>uto~ic\bibvsend
\vs Gal 3:13
qrist`oc
<hm~ac
>exhg'orasen
>ek
t~hc
kat'arac
to~u
n'omou
gen'omenoc
<up`er
<hm~wn
kat'ara
g'egraptai\r{}
\fn{\src{TMK}: gegraptai gar, \src{V}: oti gegraptai.}
g`ar
>epikat'aratoc
p~ac
<o
krem'amenoc
>ep`i
x'ulou\bibvsend
\vs Gal 3:14
<'ina
e>ic
t`a
>'ejnh
<h
e>ulog'ia
to~u
>abra`am
g'enhtai
>en
qrist~w|
>ihso~u
<'ina
t`hn
>epaggel'ian
to~u
pne'umatoc
l'abwmen
di`a
t~hc
p'istewc\bibvsend
\vs Gal 3:15
>adelfo`i
kat`a
>'anjrwpon
l'egw
<'omwc
>anjr'wpou
kekurwm'enhn
diaj'hkhn
o>ude`ic
>ajete~i
>`h
>epidiat'assetai\bibvsend
\vs Gal 3:16
t~w|
d`e
>abra`am
>er\r{r}'hjhsan
\fn{\src{TMK}: errhjhsan, \src{V}: errejhsan.}
a<i
>epaggel'iai
ka`i
t~w|
sp'ermati
a>uto~u
o>u
l'egei
ka`i
to~ic
sp'ermasin
<wc
>ep`i
poll~wn
>all>
<wc
>ef>
<en`oc
ka`i
t~w|
sp'ermat'i
sou
<'oc
>estin
qrist'oc\bibvsend
\vs Gal 3:17
to~uto
d`e
l'egw
diaj'hkhn
prokekurwm'enhn
<up`o
to~u
vjeo~u
e>ic\r{}
\fn{\src{TMK}: eic qriston, \src{V}: \bibempty.}
qrist`on
<o
met`a
>'eth\r{}
\fn{\src{TMK}: eth tetrakosia kai triakonta, \src{V}: tetrakosia kai triakonta eth.}
tetrak'osia
ka`i
tri'akonta
gegon`wc
n'omoc
o>uk
>akuro~i
e>ic
t`o
katarg~hsai
t`hn
>epaggel'ian\bibvsend
\vs Gal 3:18
e>i
g`ar
>ek
n'omou
<h
klhronom'ia
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
>ex
>epaggel'iac
t~w|
d`e
>abra`am
di>
>epaggel'iac
keq'aristai
<o
vje'oc\bibvsend
\vs Gal 3:19
t'i
o>~un
<o
n'omoc
t~wn
parab'asewn
q'arin
proset'ejh
>'aqric
o<~u
>'eljh|
t`o
sp'erma
<~w|
>ep'hggeltai
diatage`ic
di>
>agg'elwn
>en
qeir`i
mes'itou\bibvsend
\vs Gal 3:20
<o
d`e
mes'ithc
<en`oc
o>uk
>'estin
<o
d`e
vje`oc
e<~ic
>estin\bibvsend
\vs Gal 3:21
<o
o>~un
n'omoc
kat`a
t~wn
>epaggeli~wn
to~u
vjeo~u
m`h
g'enoito
e>i
g`ar
>ed'ojh
n'omoc
<o
dun'amenoc
vzwopoi~hsai
>'ontwc
>`an\r{}
\fn{\src{TMK}: an ek nomou, \src{V}: ek nomou an.}
>ek
n'omou
>~hn
<h
dikaios'unh\bibvsend
\vs Gal 3:22
>all`a
sun'ekleisen
<h
graf`h
t`a
p'anta
<up`o
<amart'ian
<'ina
<h
>epaggel'ia
>ek
p'istewc
>ihso~u
qristo~u
doj~h|
to~ic
piste'uousin\bibvsend
\vs Gal 3:23
pr`o
to~u
d`e
>elje~in
t`hn
p'istin
<up`o
n'omon
>efrouro'umeja
sug\r{k}ekleism'enoi
\fn{\src{TMK}: sugkekleismenoi, \src{V}: sugkleiomenoi.}
e>ic
t`hn
m'ellousan
p'istin
>apokalufj~hnai\bibvsend
\vs Gal 3:24
<'wste
<o
n'omoc
paidagwg`oc
<hm~wn
g'egonen
e>ic
qrist`on
<'ina
>ek
p'istewc
dikaiwj~wmen\bibvsend
\vs Gal 3:25
>eljo'ushc
d`e
t~hc
p'istewc
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
<up`o
paidagwg'on
>esmen\bibvsend
\vs Gal 3:26
p'antec
g`ar
u<io`i
vjeo~u
>este
di`a
t~hc
p'istewc
>en
qrist~w|
>ihso~u\bibvsend
\vs Gal 3:27
<'osoi
g`ar
e>ic
qrist`on
>ebapt'isjhte
qrist`on
>ened'usasje\bibvsend
\vs Gal 3:28
o>uk
>'eni
>iouda~ioc
o>ud`e
<'ellhn
o>uk
>'eni
do~uloc
o>ud`e
>ele'ujeroc
o>uk
>'eni
>'arsen
ka`i
vj~hlu
p'antec
g`ar
<ume~ic
e<~ic
>este
>en
qrist~w|
>ihso~u\bibvsend
\vs Gal 3:29
e>i
d`e
<ume~ic
qristo~u
>'ara
to~u
>abra`am
sp'erma
>est`e
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
kat>
>epaggel'ian
klhron'omoi\bibvsend
\vs Gal 4:1
l'egw
d`e
>ef>
<'oson
qr'onon
<o
klhron'omoc
n'hpi'oc
>estin
o>ud`en
diaf'erei
do'ulou
k'urioc
p'antwn
>'wn\bibvsend
\vs Gal 4:2
>all`a
<up`o
>epitr'opouc
>est`in
ka`i
o>ikon'omouc
>'aqri
t~hc
projesm'iac
to~u
patr'oc\bibvsend
\vs Gal 4:3
o<'utwc
ka`i
<hme~ic
<'ote
>~hmen
n'hpioi
<up`o
t`a
stoiqe~ia
to~u
k'osmou
>~hme\r{n}
\fn{\src{TMK}: hmen, \src{V}: hmeja.}
dedoulwm'enoi\bibvsend
\vs Gal 4:4
<'ote
d`e
>~hljen
t`o
pl'hrwma
to~u
qr'onou
>exap'esteilen
<o
vje`oc
t`on
u<i`on
a>uto~u
gen'omenon
>ek
gunaik`oc
gen'omenon
<up`o
n'omon\bibvsend
\vs Gal 4:5
<'ina
to`uc
<up`o
n'omon
>exagor'ash|
<'ina
t`hn
u<iojes'ian
>apol'abwmen\bibvsend
\vs Gal 4:6
<'oti
d'e
>este
u<io`i
>exap'esteilen
<o
vje`oc
t`o
pne~uma
to~u
u<io~u
a>uto~u
e>ic
t`ac
kard'iac
<u\r{m}~wn
\fn{\src{TMK}: umwn, \src{V}: hmwn.}
kr'azon
>abb~a
<o
pat'hr\bibvsend
\vs Gal 4:7
<'wste
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
e>~i
do~uloc
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
u<i`oc
e>i
d`e
u<i`oc
ka`i
klhron'omoc
vjeo~u\r{}
\fn{\src{TMK}: vjeou dia qristou, \src{V}: dia vjeou.}
di`a
qristo~u\bibvsend
\vs Gal 4:8
>all`a
t'ote
m`en
o>uk
e>id'otec
vje`on
>edoule'usate
to~ic
m`h\r{}
\fn{\src{TMK}: mh vfusei, \src{V}: vfusei mh.}
vf'usei
o>~usin
vjeo~ic\bibvsend
\vs Gal 4:9
n~un
d`e
gn'ontec
vje`on
m~allon
d`e
gnwsj'entec
<up`o
vjeo~u
p~wc
>epistr'efete
p'alin
>ep`i
t`a
>asjen~h
ka`i
ptwq`a
stoiqe~ia
o<~ic
p'alin
>'anwjen
doule'uein
vj'elete\bibvsend
\vs Gal 4:10
<hm'erac
parathre~isje
ka`i
m~hnac
ka`i
kairo`uc
ka`i
>eniauto'uc\bibvsend
\vs Gal 4:11
vfobo~umai
<um~ac
m'h
pwc
e>ik~h
kekop'iaka
e>ic
<um~ac\bibvsend
\vs Gal 4:12
g'inesje
<wc
>eg`w
<'oti
k>ag`w
<wc
<ume~ic
>adelfo`i
d'eomai
<um~wn
o>ud'en
me
>hdik'hsate\bibvsend
\vs Gal 4:13
o>'idate
d`e
<'oti
di>
>asj'eneian
t~hc
sark`oc
e>uhggelis'amhn
<um~in
t`o
pr'oteron\bibvsend
\vs Gal 4:14
ka`i
t`on
peirasm'on
mou\r{}
\fn{\src{TMK}: mou ton, \src{V}: umwn.}
t`on
>en
t~h|
sark'i
mou
o>uk
>exoujen'hsate
o>ud`e
>exept'usate
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<wc
>'aggelon
vjeo~u
>ed'exasj'e
me
<wc
qrist`on
>ihso~un\bibvsend
\vs Gal 4:15
t'ic\r{}
\fn{\src{TMK}: tic oun hn, \src{V}: pou oun.}
o>~un
>~hn
<o
makarism`oc
<um~wn
martur~w
g`ar
<um~in
<'oti
e>i
dunat`on
to`uc
>ofjalmo`uc
<um~wn
>exor'uxantec
>`a\r{n}
\fn{\src{TMK}: an, \src{V}: \bibempty.}
>ed'wkat'e
moi\bibvsend
\vs Gal 4:16
<'wste
>eqjr`oc
<um~wn
g'egona
>alhje'uwn
<um~in\bibvsend
\vs Gal 4:17
vzhlo~usin
<um~ac
o>u
kal~wc
>all`a
>ekkle~isai
<um~ac
vj'elousin
<'ina
a>uto`uc
vzhlo~ute\bibvsend
\vs Gal 4:18
kal`on
d`e
\r{t}`o
\fn{\src{TMK}: to, \src{V}: \bibempty.}
vzhlo~usjai
>en
kal~w|
p'antote
ka`i
m`h
m'onon
>en
t~w|
pare~ina'i
me
pr`oc
<um~ac\bibvsend
\vs Gal 4:19
tek\r{n}'ia
\fn{\src{TMK}: teknia, \src{V}: tekna.}
mou
o<`uc
p'alin
>wd'inw
>'a\r{q}ric
\fn{\src{TMK}: aqric, \src{V}: meqric.}
o<~u
morfwj~h|
qrist`oc
>en
<um~in\bibvsend
\vs Gal 4:20
>'hjelon
d`e
pare~inai
pr`oc
<um~ac
>'arti
ka`i
>all'axai
t`hn
vfwn'hn
mou
<'oti
>aporo~umai
>en
<um~in\bibvsend
\vs Gal 4:21
l'eget'e
moi
o<i
<up`o
n'omon
vj'elontec
e>~inai
t`on
n'omon
o>uk
>a\r{k}o'uete\bibvsend
\fn{\src{TMKVN}: akouete, \src{F}: anaginwskete.}
\vs Gal 4:22
g'egraptai
g`ar
<'oti
>abra`am
d'uo
u<io`uc
>'esqen
<'ena
>ek
t~hc
paid'iskhc
ka`i
<'ena
>ek
t~hc
>eleuj'erac\bibvsend
\vs Gal 4:23
>all>
<o
m`en
>ek
t~hc
paid'iskhc
kat`a
s'arka
geg'ennhtai
<o
d`e
>ek
t~hc
>eleuj'erac
di`a\r{}
\fn{\src{TMK}: dia thc, \src{V}: di.}
t~hc
>epaggel'iac\bibvsend
\vs Gal 4:24
<'atin'a
>estin
>allhgoro'umena
a<~utai
g'ar
e>isin
\r{a}<i
\fn{\src{T|K}: ai, \src{M|V}: \bibempty.}
d'uo
diaj~hkai
m'ia
m`en
>ap`o
>'orouc
sin~a
e>ic
doule'ian
genn~wsa
<'htic
>est`in
>'agar\bibvsend
\vs Gal 4:25
t`o
\r{g}`ar
\fn{\src{TMK}: gar, \src{V}: de.}
>'agar
sin~a
>'oroc
>est`in
>en
t~h|
>arab'ia|
sustoiqe~i
d`e
t~h|
n~un
<ierousal`hm
doule'uei
d`e\r{}
\fn{\src{TMK}: de, \src{V}: gar.}
met`a
t~wn
t'eknwn
a>ut~hc\bibvsend
\vs Gal 4:26
<h
d`e
>'anw
<ierousal`hm
>eleuj'era
>est`in
<'htic
>est`in
m'hthr
p'a\r{n}twn
\fn{\src{TMK}: pantwn, \src{V}: \bibempty.}
<hm~wn\bibvsend
\vs Gal 4:27
g'egraptai
g`ar
e>ufr'anjhti
ste~ira
<h
o>u
t'iktousa
<r~hxon
ka`i
vb'ohson
<h
o>uk
>wd'inousa
<'oti
poll`a
t`a
t'ekna
t~hc
>er'hmou
m~allon
>`h
t~hc
>eqo'ushc
t`on
>'andra\bibvsend
\vs Gal 4:28
<h\r{m}e~ic
\fn{\src{TMK}: hmeic, \src{V}: umeic.}
d`e
>adelfo`i
kat`a
>isa`ak
>epaggel'iac
t'ekna
>es\r{m}'en\bibvsend
\fn{\src{TMK}: esmen, \src{V}: este.}
\vs Gal 4:29
>all>
<'wsper
t'ote
<o
kat`a
s'arka
gennhje`ic
>ed'iwken
t`on
kat`a
pne~uma
o<'utwc
ka`i
n~un\bibvsend
\vs Gal 4:30
>all`a
t'i
l'egei
<h
graf`h
>'ekbale
t`hn
paid'iskhn
ka`i
t`on
u<i`on
a>ut~hc
o>u
g`ar
m`h
klhronom'h\r{s}h|
\fn{\src{TMK}: klhronomhsh, \src{V}: klhronomhsei.}
<o
u<i`oc
t~hc
paid'iskhc
met`a
to~u
u<io~u
t~hc
>eleuj'erac\bibvsend
\vs Gal 4:31
>'a\r{r}a
\fn{\src{TMK}: ara, \src{V}: dio.}
>adelfo`i
o>uk
>esm`en
paid'iskhc
t'ekna
>all`a
t~hc
>eleuj'erac\bibvsend
\vs Gal 5:1
t~h|
>eleujer'ia|
o>~un\r{}
\fn{\src{TMK}: oun h qristoc hmac, \src{V}: hmac qristoc.}
<~h|
qrist`oc
<hm~ac
>hleuj'erwsen
st'hket\r{e}
\fn{\src{TMK}: sthkete, \src{V}: sthkete oun.}
ka`i
m`h
p'alin
vzug~w|
doule'iac
>en'eqesje\bibvsend
\vs Gal 5:2
>'ide
>eg`w
pa~uloc
l'egw
<um~in
<'oti
>e`an
perit'emnhsje
qrist`oc
<um~ac
o>ud`en
>wfel'hsei\bibvsend
\vs Gal 5:3
mart'uromai
d`e
p'alin
pant`i
>anjr'wpw|
peritemnom'enw|
<'oti
>ofeil'ethc
>est`in
<'olon
t`on
n'omon
poi~hsai\bibvsend
\vs Gal 5:4
kathrg'hjhte
>ap`o
t\r{o}~u
\fn{\src{TMK}: tou, \src{V}: \bibempty.}
qristo~u
o<'itinec
>en
n'omw|
dikaio~usje
t~hc
q'aritoc
>e\-xe\-p'e\-s\r{a}\-te\bibvsend
\fn{\src{T|K|V}: exepesate, \src{M}: exepesete.}
\vs Gal 5:5
<hme~ic
g`ar
pne'umati
>ek
p'istewc
>elp'ida
dikaios'unhc
>apekdeq'omeja\bibvsend
\vs Gal 5:6
>en
g`ar
qrist~w|
>ihso~u
o>'ute
peritom'h
ti
>isq'uei
o>'ute
>akrobust'ia
>all`a
p'istic
di>
>ag'aphc
>energoum'enh\bibvsend
\vs Gal 5:7
>etr'eqete
kal~wc
t'ic
<um~ac
>a\r{n}'ekoyen
\fn{\src{T|K}: anekoyen th, \src{M}: enekoyen th, \src{V}: enekoyen [th].}
t~h|
>alhje'ia|
m`h
pe'ijesjai\bibvsend
\vs Gal 5:8
<h
peismon`h
o>uk
>ek
to~u
kalo~untoc
<um~ac\bibvsend
\vs Gal 5:9
mikr`a
vz'umh
<'olon
t`o
vf'urama
vzumo~i\bibvsend
\vs Gal 5:10
>eg`w
p'epoija
e>ic
<um~ac
>en
kur'iw|
<'oti
o>ud`en
>'allo
vfron'hsete
<o
d`e
tar'asswn
<um~ac
vbast'asei
t`o
kr'ima
<'ostic
>`a\r{n}
\fn{\src{TMK}: an, \src{V}: ean.}
>~h|\bibvsend
\vs Gal 5:11
>eg`w
d`e
>adelfo`i
e>i
peritom`hn
>'eti
khr'ussw
t'i
>'eti
di'wkomai
>'ara
kat'hrghtai
t`o
sk'andalon
to~u
stauro~u\bibvsend
\vs Gal 5:12
>'ofelon
ka`i
>apok'oyontai
o<i
>anastato~untec
<um~ac\bibvsend
\vs Gal 5:13
<ume~ic
g`ar
>ep>
>eleujer'ia|
>ekl'hjhte
>adelfo`i
m'onon
m`h
t`hn
>eleujer'ian
e>ic
>aform`hn
t~h|
sark`i
>all`a
di`a
t~hc
>ag'aphc
doule'uete
>all'hloic\bibvsend
\vs Gal 5:14
<o
g`ar
p~ac
n'omoc
>en
<en`i
l'ogw|
pl\r{h}ro~utai
\fn{\src{TMK}: plhroutai, \src{V}: peplhrwtai.}
>en
t~w|
>agap'hseic
t`on
plhs'ion
sou
<wc
<e\r{a}ut'on\bibvsend
\fn{\src{T|K}: eauton, \src{M|V}: seauton.}
\vs Gal 5:15
e>i
d`e
>all'hlouc
d'aknete
ka`i
katesj'iete
vbl'epete
m`h
<u\r{p}`o
\fn{\src{TMK}: upo, \src{V}: up.}
>all'hlwn
>analwj~hte\bibvsend
\vs Gal 5:16
l'egw
d`e
pne'umati
peripate~ite
ka`i
>epijum'ian
sark`oc
o>u
m`h
tel'eshte\bibvsend
\vs Gal 5:17
<h
g`ar
s`arx
>epijume~i
kat`a
to~u
pne'umatoc
t`o
d`e
pne~uma
kat`a
t~hc
sark`oc
ta~uta
d`e\r{}
\fn{\src{TMK}: de antikeitai allhloic, \src{V}: gar allhloic antikeitai.}
>ant'ikeitai
>all'hloic
<'ina
m`h
<`a
>`a\r{n}
\fn{\src{TMK}: an, \src{V}: ean.}
vj'elhte
ta~uta
poi~hte\bibvsend
\vs Gal 5:18
e>i
d`e
pne'umati
>'agesje
o>uk
>est`e
<up`o
n'omon\bibvsend
\vs Gal 5:19
vfaner`a
d'e
>estin
t`a
>'erga
t~hc
sark`oc
<'atin'a
>estin
moi\r{q}e'ia
\fn{\src{TMK}: moiqeia, \src{V}: \bibempty.}
porne'ia
>akajars'ia
>as'elgeia\bibvsend
\vs Gal 5:20
e>idwlolatr\r{e}'ia
\fn{\src{TMK}: eidwlolatreia, \src{V}: eidwlolatria.}
vfarmake'ia
>'eqjrai
>'ereic\r{}
\fn{\src{TMK}: ereic vzhloi, \src{V}: eric vzhloc.}
vz~hloi
vjumo`i
>erije~iai
diqostas'iai
a<ir'eseic\bibvsend
\vs Gal 5:21
vfj'onoi
vf'o\r{n}oi
\fn{\src{TMK}: vfonoi, \src{V}: \bibempty.}
m'ejai
k~wmoi
ka`i
t`a
<'omoia
to'utoic
<`a
prol'egw
<um~in
kaj`wc
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
proe~ipon
<'oti
o<i
t`a
toia~uta
pr'assontec
vbasile'ian
vjeo~u
o>u
klhronom'hsousin\bibvsend
\vs Gal 5:22
<o
d`e
karp`oc
to~u
pne'umat'oc
>estin
>ag'aph
qar`a
e>ir'hnh
makrojum'ia
qrhst'othc
>agajws'unh
p'istic\bibvsend
\vs Gal 5:23
p\r{r}a|'othc
\fn{\src{TMK}: praothc, \src{V}: prauthc.}
>egkr'ateia
kat`a
t~wn
toio'utwn
o>uk
>'estin
n'omoc\bibvsend
\vs Gal 5:24
o<i
d`e
to~u
qrist\r{o}~u
\fn{\src{TMK}: qristou, \src{V}: qristou [ihsou].}
t`hn
s'arka
>esta'urwsan
s`un
to~ic
paj'hmasin
ka`i
ta~ic
>epijum'iaic\bibvsend
\vs Gal 5:25
e>i
vz~wmen
pne'umati
pne'umati
ka`i
stoiq~wmen\bibvsend
\vs Gal 5:26
m`h
gin'wmeja
ken'odoxoi
>all'hlouc
prokalo'umenoi
>all'hloic
vfjono~untec\bibvsend
\vs Gal 6:1
>adelfo`i
>e`an
ka`i
prolh\r{f}j~h|
\fn{\src{TMK}: prolhfjh, \src{V}: prolhmfjh.}
>'anjrwpoc
>'en
tini
parapt'wmati
<ume~ic
o<i
pneumatiko`i
katart'izete
t`on
toio~uton
>en
pne'umati
p\r{r}a|\-'oth\-toc
\fn{\src{TMK}: praothtoc, \src{V}: prauthtoc.}
skop~wn
seaut`on
m`h
ka`i
s`u
peirasj~h|c\bibvsend
\vs Gal 6:2
>all'hlwn
t`a
vb'arh
vbast'azete
ka`i
o<'utwc
>anaplhr'ws\r{a}te
\fn{\src{TMK}: anaplhrwsate, \src{V}: anaplhrwsete.}
t`on
n'omon
to~u
qristo~u\bibvsend
\vs Gal 6:3
e>i
g`ar
doke~i
tic
e>~ina'i
ti
mhd`en
>`wn
<eaut`on\r{}
\fn{\src{TMK}: eauton vfrenapata, \src{V}: vfrenapata eauton.}
vfrenapat~a|\bibvsend
\vs Gal 6:4
t`o
d`e
>'ergon
<eauto~u
dokimaz'etw
<'ekastoc
ka`i
t'ote
e>ic
<eaut`on
m'onon
t`o
ka'uqhma
<'exei
ka`i
o>uk
e>ic
t`on
<'eteron\bibvsend
\vs Gal 6:5
<'ekastoc
g`ar
t`o
>'idion
vfort'ion
vbast'asei\bibvsend
\vs Gal 6:6
koinwne'itw
d`e
<o
kathqo'umenoc
t`on
l'ogon
t~w|
kathqo~unti
>en
p~asin
>agajo~ic\bibvsend
\vs Gal 6:7
m`h
plan~asje
vje`oc
o>u
mukthr'izetai
<`o
g`ar
>e`an
spe'irh|
>'anjrwpoc
to~uto
ka`i
vjer'isei\bibvsend
\vs Gal 6:8
<'oti
<o
spe'irwn
e>ic
t`hn
s'arka
<eauto~u
>ek
t~hc
sark`oc
vjer'isei
vfjor`an
<o
d`e
spe'irwn
e>ic
t`o
pne~uma
>ek
to~u
pne'umatoc
vjer'isei
vzw`hn
a>i'wnion\bibvsend
\vs Gal 6:9
t`o
d`e
kal`on
poio~untec
m`h
>e\r{k}kak~wmen
\fn{\src{TMK}: ekkakwmen, \src{V}: egkakwmen.}
kair~w|
g`ar
>id'iw|
vjer'isomen
m`h
>eklu'omenoi\bibvsend
\vs Gal 6:10
>'ara
o>~un
<wc
kair`on
>'eq\r{o}men
\fn{\src{TMKVN}: eqomen, \src{B[*]|aleph}: eqwmen.}
>ergaz'wmeja
t`o
>agaj`on
pr`oc
p'antac
m'alista
d`e
pr`oc
to`uc
o>ike'iouc
t~hc
p'istewc\bibvsend
\vs Gal 6:11
>'idete
\r{p}hl'ikoic
\fn{\src{TMKVN}: phlikoic, \src{B[*]|Pap[46]}: hlikoic, \src{F}: poikiloic.}
<um~in
gr'ammasin
>'egraya
t~h|
>em~h|
qeir'i\bibvsend
\vs Gal 6:12
<'osoi
vj'elousin
e>uproswp~hsai
>en
sark`i
o<~utoi
>anagk'azousin
<um~ac
perit'emnesjai
m'onon
<'ina
m`h\r{}
\fn{\src{TMK}: mh tw staurw tou qristou, \src{V}: tw staurw tou qristou mh.}
t~w|
staur~w|
to~u
qristo~u
di'wkwntai\bibvsend
\vs Gal 6:13
o>ud`e
g`ar
o<i
peritem\r{n}'omenoi
\fn{\src{T|K|V}: peritemnomenoi, \src{M}: peritetmhmenoi.}
a>uto`i
n'omon
vful'assousin
>all`a
vj'elousin
<um~ac
perit'emnesjai
<'ina
>en
t~h|
<umet'era|
sark`i
kauq'hswntai\bibvsend
\vs Gal 6:14
>emo`i
d`e
m`h
g'enoito
kauq~asjai
e>i
m`h
>en
t~w|
staur~w|
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
di>
o<~u
>emo`i
k'osmoc
>esta'urwtai
k>ag`w
\r{t}~w|
\fn{\src{TMK}: tw, \src{V}: \bibempty.}
k'osmw|\bibvsend
\vs Gal 6:15
>e\r{n}
\fn{\src{TMK}: en gar qristw ihsou, \src{V}: \bibempty.}
g`ar
qrist~w|
>ihso~u
o>'ute\r{}
\fn{\src{TMK}: oute peritomh ti isquei, \src{V}: oute gar peritomh ti estin.}
peritom'h
ti
>isq'uei
o>'ute
>akrobust'ia
>all`a
kain`h
kt'isic\bibvsend
\vs Gal 6:16
ka`i
<'osoi
t~w|
kan'oni
to'utw|
stoiq'hsousin
e>ir'hnh
>ep>
a>uto`uc
ka`i
>'eleoc
ka`i
>ep`i
t`on
>isra`hl
to~u
vjeo~u\bibvsend
\vs Gal 6:17
to~u
loipo~u
k'opouc
moi
mhde`ic
pareq'etw
>eg`w
g`ar
t`a
st'igmata
to~u
ku\r{r}io~u
\fn{\src{TMK}: kuriou, \src{V}: \bibempty.}
>ihso~u
>en
t~w|
s'wmat'i
mou
vbast'azw\bibvsend
\vs Gal 6:18
<h
q'aric
to~u
kur'iou
<hm~wn
>ihso~u
qristo~u
met`a
to~u
pne'umatoc
<um~wn
>adelfo`i
>am'hn\bibvsend
Pr`oc\r{}
\fn{\src{T}: Proc \ldots\ vrwmhc, \src{K|M|V}: \bibempty.}
gal'atac
>egr'afh
>ap`o
<r'wmhc\bibvsend
