\bibbook{H PROS EBRAIOUS\\\LARGE EPISTOLH PAULOU\r{}}{PROS EBRAIOUS}{Hebrews}{Heb}[PROS EBRAIOUS]
\vs Heb 1:1
polumer~wc
\fnt{\src{T}: H PROS EBRAIOUS EPISTOLH PAULOU, \src{K}: PAULOU TOU APOSTOLOU H PROS EBRAIOUS EPISTOLH, \src{M|V}: PROS EBRAIOUS.}
ka`i
polutr'opwc
p'alai
<o
vje`oc
lal'hsac
to~ic
patr'asi\r{n}
\fn{\src{TMKVN}: patrasin, \src{Pap[12,46]}: patrasin hmwn.}
>en
to~ic
prof'htaic\bibvsend
\vs Heb 1:2
>ep>
>esq'at\r{w}n
\fn{\src{T|K}: esqatwn, \src{M|V}: esqatou.}
t~wn
<hmer~wn
to'utwn
>el'alhsen
<hm~in
>en
u<i~w|
<`on
>'ejhken
klhron'omon
p'antwn
di>
o<~u
k\r{a}`i
\fn{\src{TMKVN}: kai, \src{Pap[46]}: \bibempty.}
to`uc\r{}
\fn{\src{TMK}: touc aiwnac epoihsen, \src{V}: epoihsen touc aiwnac.}
a>i~wnac
>epo'ihsen\bibvsend
\vs Heb 1:3
<`oc
>`wn
>apa'ugasma
t~hc
d'oxhc
ka`i
qarakt`hr
t~hc
<upost'asewc
a>uto~u
\r{vf}'erwn
\fn{\src{TMKVN}: vferwn, \src{B}: vfanerwn.}
te
t`a
p'anta
t~w|
<r'hmati
t~hc
dun'amewc
a>u\r{t}o~u
\fn{\src{TMKVN}: autou, \src{Pap[46]}: \bibempty.}
di>\r{}
\fn{\src{TMK}: di eautou kajarismon poihsamenoc twn amartiwn hmwn, \src{V}: kajarismon twn amartiwn poihsamenoc.}
<eauto~u
kajarism`on
poihs'amenoc
t~wn
<amarti~wn
<hm~wn
>ek'ajisen
>en
dexi~a|
t~hc
megalws'unhc
>en
<uyhlo~ic\bibvsend
\vs Heb 1:4
toso'utw|
kre'ittwn
gen'omenoc
\r{t}~wn
\fn{\src{TMKVN}: twn, \src{B}: \bibempty.}
>agg'elwn
<'osw|
diafor'wteron
par>
a>uto`uc
keklhron'omhken
>'onoma\bibvsend
\vs Heb 1:5
t'ini
g`ar
e>~ip'en
pote
t~wn
>agg'elwn
u<i'oc
mou
e>~i
s`u
>eg`w
s'hmeron
geg'ennhk'a
se
ka`i
p'alin
>eg`w
>'esomai
a>ut~w|
e>ic
pat'era
ka`i
a>ut`oc
>'estai
moi
e>ic
u<i'on\bibvsend
\vs Heb 1:6
<'otan
d`e
p'alin
e>isag'agh|
t`on
prwt'otokon
e>ic
t`hn
o>ikoum'enhn
l'egei
ka`i
proskunhs'atwsan
a>ut~w|
p'antec
>'aggeloi
vjeo~u\bibvsend
\vs Heb 1:7
ka`i
pr`oc
m`en
to`uc
>agg'elou\r{c}
\fn{\src{TMKVN}: aggelouc, \src{F}: aggelouc autou.}
l'egei
<o
poi~wn
to`uc
>agg'elouc
a>uto~u
pne'uma\r{t}a
\fn{\src{TMKVN}: pneumata, \src{F}: pneuma.}
ka`i
to`uc
leitourgo`uc
a>uto~u
pur`oc
vfl'oga\bibvsend
\vs Heb 1:8
pr`oc
d`e
t`on
u<i`on
<o
vjr'onoc
sou
<o
vje`oc
e>ic
t`on
a>i~wna
to~u\r{}
\fn{\src{TMKVN}: tou aiwnoc, \src{B}: \bibempty.}
a>i~wnoc
<r'abdoc\r{}
\fn{\src{TMK}: vrabdoc eujuthtoc h, \src{V}: kai h vrabdoc thc eujuthtoc.}
e>uj'uthtoc
<h
<r'abdoc
t~hc
vbasile'iac
s\r{o}u\bibvsend
\fn{\src{TMKVN}: sou, \src{aleph|B}: autou.}
\vs Heb 1:9
>hg'aphsac
dikaios'unhn
ka`i
>em'ishsac
>a\r{n}om'ian
\fn{\src{TMKVN}: anomian, \src{aleph|A}: adikian, \src{F}: anomiac.}
di`a
to~uto
>'eqris'en
se
<o
vje`oc
<o
vje'oc
sou
>'elaion
>agalli'asewc
par`a
to`uc
met'oqouc
sou\bibvsend
\vs Heb 1:10
ka`i
s`u
kat>
>arq`ac
k'urie
t`hn
g~hn
>ejemel'iwsac
ka`i
>'erga
t~wn
qeir~wn
so'u
e>isin
o<i
o>urano'i\bibvsend
\vs Heb 1:11
a>uto`i
>apolo~untai
s`u
d`e
diam'en\r{e}ic
\fn{\src{TMKVN}: diam'eneic, \src{F}: diamene~ic.}
ka`i
p'antec
<wc
<im'ation
palaiwj'hsontai\bibvsend
\vs Heb 1:12
ka`i
<wse`i
perib'olaion
<el'ix\r{e}ic
\fn{\src{TMKVN}: elixeic, \src{aleph}: allaxeic.}
a>uto`u\r{c}
\fn{\src{TMK}: autouc, \src{V}: autouc wc imation.}
ka`i
>allag'hsontai
s`u
d`e
<o
a>ut`oc
e>~i
ka`i
t`a
>'eth
sou
o>uk
>ekle'iyousin\bibvsend
\vs Heb 1:13
pr`oc
t'ina
d`e
t~wn
>agg'elwn
e>'irhk'en
pote
k'ajou
>ek
dexi~wn
mou
<'ewc
>`an
vj~w
to`uc
>eqjro'uc
sou
<upop'odion
t~wn
pod~wn
sou\bibvsend
\vs Heb 1:14
o>uq`i
p'antec
e>is`in
leitourgik`a
pne'umata
e>ic
diakon'ia\r{n}
\fn{\src{TMKVN}: diakonian, \src{B}: diakoniac.}
>apostell'omena
di`a
to`uc
m'ellontac
klhronome~in
swthr'ian\bibvsend
\vs Heb 2:1
di`a
to~uto
de~i
perissot'erwc
<hm~ac\r{}
\fn{\src{TMK}: hmac proseqein, \src{V}: proseqein hmac.}
pros'eqein
to~ic
>akousje~isin
m'h\r{}
\fn{\src{T|K}: mh pote, \src{M|V}: mhpote.}
pote
parar\r{r}u~wmen\bibvsend
\fn{\src{TMK}: pararruwmen, \src{V}: pararuwmen.}
\vs Heb 2:2
e>i
g`ar
<o
di>
>agg'el\r{w}n
\fn{\src{TMKVN}: aggelwn, \src{F}: aggelou.}
lalhje`ic
l'ogoc
>eg'eneto
vb'ebaioc
ka`i
p~asa
par'abasic
ka`i
parako`h
>'elaben
>'endikon
misjapodos'ian\bibvsend
\vs Heb 2:3
p~wc
<hme~ic
>ekfeux'omeja
thlika'uthc
>amel'hsantec
swthr'iac
<'htic
>arq`hn
labo~usa
lale~isjai
di`a
to~u
kur'iou
<up`o
t~wn
>akous'antwn
e>ic
<hm~ac
>ebebai'wjh\bibvsend
\vs Heb 2:4
sun\-e\r{p}i\-mar\-tu\-ro~un\-toc
\fn{\src{TMKVN}: sunepimarturo~untoc, \src{B}: summarturountoc.}
to~u
vjeo~u
shme'ioic
\r{t}e
\fn{\src{TMKVN}: te, \src{F}: \bibempty.}
ka`i
t'erasin
ka`i
poik'ilaic
dun'amesin
ka`i
pne'umatoc
<ag'iou
merismo~ic
kat`a
t`hn
a>u\r{t}o~u
\fn{\src{TMKVN}: autou, \src{F}: tou vjeou.}
vj'elhsin\bibvsend
\vs Heb 2:5
o>u
g`ar
>agg'eloic
<up'etaxen
t`hn
o>ikoum'enhn
t`hn
m'ellousan
per`i
<~hc
lalo~umen\bibvsend
\vs Heb 2:6
diemart'urato
d'e
po'u
tic
l'egwn
\r{t}'i
\fn{\src{TMKVN}: ti, \src{Pap[46]}: tic.}
>estin
>'anjrwpoc
<'oti
mimn'hskh|
a>uto~u
>`h
u<i`oc
>anjr'wpou
<'oti
>episk'epth|
a>ut'on\bibvsend
\vs Heb 2:7
>hl'attwsac
a>ut`on
vbraq'u
ti
par>
>agg'elouc
d'oxh|
ka`i
tim~h|
>estef'anwsac
a>ut`on
ka`i\r{}
\fn{\src{T|K}: kai \ldots\ sou, \src{M|V}: \bibempty.}
kat'esthsac
a>ut`on
>ep`i
t`a
>'erga
t~wn
qeir~wn
sou\bibvsend
\vs Heb 2:8
p'anta
<up'etaxac
<upok'atw
t~wn
pod~wn
a>uto~u
>en
g`ar\r{}
\fn{\src{TMK}: gar tw, \src{V}: tw gar.}
t~w|
<upot'axai
a>u\r{t}~w|
\fn{\src{TMK}: autw, \src{V}: [autw], \src{Pap[46]}: \bibempty.}
t`a
p'anta
o>ud`en
>af~hken
a>ut~w|
>anup'otakton
n~un
d`e
o>'upw
<or~wmen
a>ut~w|
t`a
p'anta
<upotetagm'ena\bibvsend
\vs Heb 2:9
t`on
d`e
vbraq'u
ti
par>
>agg'elouc
>hlattwm'enon
vbl'epomen
>ihso~un
di`a
t`o
p'ajhma
to~u
vjan'atou
d'oxh|
ka`i
tim~h|
>estefanwm'enon
<'opwc
q'ariti
vjeo~u
<up`er
pant`oc
ge'ushtai
vjan'atou\bibvsend
\vs Heb 2:10
>'eprepen
g`ar
a>ut~w|
di>
<`on
t`a
p'anta
ka`i
di>
o<~u
t`a
p'anta
pollo`uc
u<io`uc
e>ic
d'oxan
>agag'onta
t`on
>arqhg`on
t~hc
swthr'iac
a>ut~wn
di`a
pajhm'atwn
telei~wsai\bibvsend
\vs Heb 2:11
<'o
te
g`ar
<agi'azwn
ka`i
o<i
<agiaz'omenoi
>ex
<en`oc
p'antec
di>
<`hn
a>it'ian
o>uk
>epaisq'unetai
>adelfo`uc
a>uto`uc
kale~in\bibvsend
\vs Heb 2:12
l'egwn
>apaggel~w
t`o
>'onom'a
sou
to~ic
>adelfo~ic
mou
>en
m'esw|
>ekklhs'iac
<umn'hsw
se\bibvsend
\vs Heb 2:13
ka`i
p'alin
>eg`w
>'esomai
pepoij`wc
>ep>
a>ut~w|
ka`i
p'alin
>ido`u
>eg`w
ka`i
t`a
paid'ia
<'a
moi
>'edwken
<o
vje'oc\bibvsend
\vs Heb 2:14
>epe`i
o>~un
t`a
paid'ia
kekoin'wnhken
sark`oc\r{}
\fn{\src{TMK}: sarkoc kai aimatoc, \src{V}: aimatoc kai sarkoc.}
ka`i
a<'imatoc
ka`i
a>ut`oc
paraplhs'iwc
met'esqen
t~wn
a>ut~w\r{n}
\fn{\src{TMKVN}: autwn, \src{F}: autwn pajhmatwn.}
<'ina
di`a
to~u
vjan'atou
katarg'hsh|
t`on
t`o
kr'atoc
>'eqonta
to~u
vjan'atou
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
t`on
di'abolon\bibvsend
\vs Heb 2:15
ka`i
>apall'axh|
to'utouc
<'osoi
vf'obw|
vjan'atou
di`a
pant`oc
to~u
vz~h|n
>'enoqoi
>~hsan
doule'iac\bibvsend
\vs Heb 2:16
o>u
g`ar
d'hpou
>agg'elwn
>epilamb'anetai
>all`a
sp'ermatoc
>abra`am
>epilamb'anetai\bibvsend
\vs Heb 2:17
<'ojen
>'wfeilen
kat`a
p'anta
to~ic
>adelfo~ic
<omoiwj~hnai
<'ina
>ele'hmwn
g'enhtai
ka`i
pist`oc
>arqiere`uc
t`a
pr`oc
t`on
vje`on
e>ic
t`o
<il'askesjai
t`ac
<amart'iac
to~u
lao~u\bibvsend
\vs Heb 2:18
>en
<~w|
g`ar
p'eponjen
a>ut`oc
peirasje`ic
d'unatai
to~ic
peirazom'enoic
vbohj~hsai\bibvsend
\vs Heb 3:1
<'ojen
>adelfo`i
<'agioi
kl'hsewc
>epouran'iou
m'etoqoi
katano'hsate
t`on
>ap'ostolon
ka`i
>arqier'ea
t~hc
<omolog'iac
<hm~wn
qrist`on\r{}
\fn{\src{T|K}: qriston ihsoun, \src{M}: ihsoun qriston, \src{V}: ihsoun.}
>ihso~un\bibvsend
\vs Heb 3:2
pist`on
>'onta
t~w|
poi'hsanti
a>ut`on
<wc
ka`i
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
>en
<'olw|
t~w|
o>'ikw|
a>uto~u\bibvsend
\vs Heb 3:3
ple'ionoc
g`ar
d'oxhc\r{}
\fn{\src{TMK}: doxhc outoc, \src{V}: outoc doxhc.}
o<~utoc
par`a
mw\-\r{s}~hn
\fn{\src{T|K}: mwshn, \src{M|V}: mwushn.}
>hx'iwtai
kaj>
<'oson
ple'iona
tim`hn
>'eqei
to~u
o>'ikou
<o
kataskeu'asac
a>ut'on\bibvsend
\vs Heb 3:4
p~ac
g`ar
o>~ikoc
kataskeu'azetai
<up'o
tinoc
<o
d`e
\r{t}`a
\fn{\src{TMK}: ta, \src{V}: \bibempty.}
p'anta
kataskeu'asac
vje'oc\bibvsend
\vs Heb 3:5
ka`i
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
m`en
pist`oc
>en
<'olw|
t~w|
o>'ikw|
a>uto~u
<wc
vjer'apwn
e>ic
mart'urion
t~wn
lalhjhsom'enwn\bibvsend
\vs Heb 3:6
qrist`oc
d`e
<wc
u<i`oc
>ep`i
t`on
o>~ikon
a>uto~u
o<~u
o>~ik'oc
>esmen
<hme~ic
>e'a\r{n}per
\fn{\src{TMK}: eanper, \src{V}: ean[per].}
t`hn
parrhs'ian
ka`i
t`o
ka'uqhma
t~hc
>elp'idoc
m'eqri\r{}
\fn{\src{TMK}: meqri telouc vbebaian, \src{V}: \bibempty.}
t'elouc
vbeba'ian
kat'asqwmen\bibvsend
\vs Heb 3:7
di`o
kaj`wc
l'egei
t`o
pne~uma
t`o
<'agion
s'hmeron
>e`an
t~hc
vfwn~hc
a>uto~u
>ako'ushte\bibvsend
\vs Heb 3:8
m`h
sklhr'unhte
t`ac
kard'iac
<um~wn
<wc
>en
t~w|
parapikrasm~w|
kat`a
t`hn
<hm'eran
to~u
peirasmo~u
>en
t~h|
>er'hmw|\bibvsend
\vs Heb 3:9
o<~u
>epe'iras'an
\r{m}e
\fn{\src{TMK}: me, \src{V}: \bibempty.}
o<i
pat'erec
<um~wn
>edok'imas'an\r{}
\fn{\src{TMK}: edokimasan me, \src{V}: en dokimasia.}
me
ka`i
e>~idon
t`a
>'erga
mou
tess\r{a}r'akonta
\fn{\src{TMK}: tessarakonta, \src{V}: tesserakonta.}
>'eth\bibvsend
\vs Heb 3:10
di`o
pros'wqjisa
t~h|
gene~a|
>ek\r{e}'inh|
\fn{\src{TMK}: ekeinh, \src{V}: tauth.}
ka`i
e>~ipon
>ae`i
plan~wntai
t~h|
kard'ia|
a>uto`i
d`e
o>uk
>'egnwsan
t`ac
<odo'uc
mou\bibvsend
\vs Heb 3:11
<wc
>'wmosa
>en
t~h|
>org~h|
mou
e>i
e>isele'usontai
e>ic
t`hn
kat'apaus'in
mou\bibvsend
\vs Heb 3:12
vbl'epete
>adelfo`i
m'h\r{}
\fn{\src{T|K}: mh pote, \src{M|V}: mhpote.}
pote
>'estai
>'en
tini
<um~wn
kard'ia
ponhr`a
>apist'iac
>en
t~w|
>apost~hnai
>ap`o
vjeo~u
vz~wntoc\bibvsend
\vs Heb 3:13
>all`a
parakal\r{e}~ite
\fn{\src{TMKVN}: parakaleite, \src{Pap[13]}: parakalesate.}
<eauto`uc
kaj>
<ek'asthn
<hm'eran
>'aqric
o<~u
t`o
s'hmeron
kale~itai
<'ina
m`h
sklhrunj~h|
tic\r{}
\fn{\src{T|K|V}: tic ex umwn, \src{M}: ex umwn tic.}
>ex
<um~wn
>ap'ath|
t~hc
<amart'iac\bibvsend
\vs Heb 3:14
m'etoqoi
g`ar
geg'onamen\r{}
\fn{\src{TMK}: gegonamen tou qristou, \src{V}: tou qristou gegonamen.}
to~u
qristo~u
>e'anper
t`hn
>arq`hn
t~hc
<upost'asewc
m'eqri
t'elouc
vbeba'ian
kat'asqwmen\bibvsend
\vs Heb 3:15
>en
t~w|
l'egesjai
s'hmeron
>e`an
t~hc
vfwn~hc
a>uto~u
>ako'ushte
m`h
sklhr'unhte
t`ac
kard'iac
<um~wn
<wc
>en
t~w|
parapikrasm~w|\bibvsend
\vs Heb 3:16
ti\r{n}`ec
\fn{\src{T|K}: tin`ec, \src{M|V}: t'inec.}
g`ar
>ako'usantec
parep'ikranan
>all>
o>u
p'antec
o<i
>exelj'ontec
>ex
a>ig'uptou
di`a
mw\r{s}'ewc\bibvsend
\fn{\src{T|K}: mwsewc, \src{M|V}: mwusewc.}
\vs Heb 3:17
t'isin
d`e
pros'wqjisen
tess\r{a}r'akonta
\fn{\src{TMK}: tessarakonta, \src{V}: tesserakonta.}
>'eth
o>uq`i
to~ic
<a\r{m}art'hsasin
\fn{\src{TMKVN}: amarthsasin, \src{A}: apeijhsasin.}
<~wn
t`a
k~wla
>'epesen
>en
t~h|
>er'hmw|\bibvsend
\vs Heb 3:18
t'isin
d`e
>'wmosen
m`h
e>isele'usesjai
e>ic
t`hn
kat'apausin
a>uto~u
e>i
m`h
to~ic
>ap\r{e}ij'hsasin\bibvsend
\fn{\src{TMKVN}: apeijhsasin, \src{Pap[46]}: apisthsasin.}
\vs Heb 3:19
ka`i
vbl'epomen
<'oti
o>uk
>hdun'hjhsan
e>iselje~in
di>
>apist'ian\bibvsend
\vs Heb 4:1
fobhj~wmen
o>~un
m'h\r{}
\fn{\src{T|K}: mh pote, \src{M|V}: mhpote.}
pote
kataleipom'enhc
>epaggel'iac
e>iselje~in
e>ic
t`hn
kat'apausin
a>uto~u
dok~h|
tic
>ex
<um~wn
<usterhk'enai\bibvsend
\vs Heb 4:2
ka`i
g'ar
>esmen
e>uhggelism'enoi
kaj'aper
k>ake~inoi
>all>
o>uk
>wf'elhsen
<o
l'ogoc
t~hc
>ako~hc
>eke'inouc
m`h
sugkekra\r{m}'enoc
\fn{\src{T|K}: sugkekramenoc, \src{M}: sugkekramenouc, \src{V}: sugkekerasmenouc.}
t~h|
p'istei
to~ic
>ako'usasin\bibvsend
\vs Heb 4:3
e>iser\r{q}'omeja
\fn{\src{TMKVN}: eiserqomeja, \src{A|C}: eiserqwmeja.}
\r{g}`ar
\fn{\src{TMKVN}: gar, \src{aleph|A|C}: oun.}
e>ic
\r{t}`hn
\fn{\src{TMK}: thn, \src{V}: [thn], \src{B}: \bibempty.}
kat'apausin
o<i
piste'usantec
kaj`wc
e>'irhken
<wc
>'wmosa
>en
t~h|
>org~h|
mou
e>i
e>isele'usontai
e>ic
t`hn
kat'apaus'in
mou
ka'itoi
t~wn
>'ergwn
>ap`o
katabol~hc
k'osmou
genhj'entwn\bibvsend
\vs Heb 4:4
e>'irhken
g'ar
pou
per`i
t~hc
<ebd'omhc
o<'utwc
ka`i
kat'epausen
<o
vje`oc
>en
t~h|
<hm'era|
t~h|
<ebd'omh|
>ap`o
p'antwn
t~wn
>'ergwn
a>uto~u\bibvsend
\vs Heb 4:5
ka`i
>en
to'utw|
p'alin
e>i
e>isele'usontai
e>ic
t`hn
kat'apaus'in
mou\bibvsend
\vs Heb 4:6
>epe`i
o>~un
>apole'ipeta'i
tinac
e>iselje~in
e>ic
a>ut`hn
ka`i
o<i
pr'oteron
e>uaggelisj'entec
o>uk
e>is~hljon
di>
>ap\r{e}'ijeian\bibvsend
\fn{\src{TMKVN}: apeijeian, \src{aleph}: apistian.}
\vs Heb 4:7
p'alin
tin`a
<or'izei
<hm'eran
s'hmeron
>en
da\r{b}`id
\fn{\src{TMK}: dabid, \src{V}: dauid.}
l'egwn
met`a
toso~uton
qr'onon
kaj`wc
\r{e}>'irhtai
\fn{\src{TMK}: eirhtai, \src{V}: proeirhtai.}
s'hmeron
>e`an
t~hc
vfwn~hc
a>uto~u
>ako'ushte
m`h
sklhr'unhte
t`ac
kard'iac
<um~wn\bibvsend
\vs Heb 4:8
e>i
g`ar
a>uto`uc
>ihso~uc
kat'epausen
o>uk
>`a\r{n}
\fn{\src{TMKVN}: an, \src{B}: ara.}
per`i
>'allhc
>el'alei
met`a
ta~uta
<hm'erac\bibvsend
\vs Heb 4:9
>'ara
>apole'ipetai
sabbatism`oc
t~w|
la~w|
to~u
vjeo~u\bibvsend
\vs Heb 4:10
<o
g`ar
e>iselj`wn
e>ic
t`hn
kat'apausin
a>uto~u
ka`i
a>ut`oc
kat'epausen
>ap`o
t~wn
>'ergwn
a>uto~u
<'wsper
>ap`o
t~wn
>id'iwn
<o
vje'oc\bibvsend
\vs Heb 4:11
spoud'aswmen
o>~un
e>iselje~in
e>ic
>eke'inhn
t`hn
kat'apausin
<'ina
m`h
>en
t~w|
a>ut~w|
tic
<upode'igmati
p'esh|
t~hc
>ap\r{e}ije'iac\bibvsend
\fn{\src{TMKVN}: apeijeiac, \src{Pap[46]}: apistiac, \src{F}: alhjeiac.}
\vs Heb 4:12
vz~wn
g`ar
<o
l'ogoc
to~u
vjeo~u
ka`i
>en\r{e}rg`hc
\fn{\src{TMKVN}: energhc, \src{B}: enarghc.}
ka`i
tom'wteroc
<up`er
p~asan
m'aqairan
d'istomon
ka`i
di"ikno'umenoc
>'aqri
merismo~u
yuq~hc
\r{t}e
\fn{\src{TMK}: te, \src{V}: \bibempty.}
ka`i
\r{p}ne'umatoc
\fn{\src{TMKVN}: pneumatoc, \src{F}: swmatoc.}
<arm~wn
t`e
ka`i
muel~wn
ka`i
kritik`oc
>enjum'hsewn
ka`i
>ennoi~wn
kard'iac\bibvsend
\vs Heb 4:13
ka`i
o>uk
>'estin
kt'isic
>afan`hc
>en'wpion
a>uto~u
p'anta
d`e
gumn`a
ka`i
tetraqhlism'ena
to~ic
>ofjalmo~ic
a>uto~u
pr`oc
<`on
<hm~in
<o
l'ogoc\bibvsend
\vs Heb 4:14
>'eqontec
o>~un
>arqier'ea
m'egan
dielhluj'ota
to`uc
o>urano`uc
>ihso~un
t`on
u<i`on
to~u
vjeo~u
krat~wmen
t~hc
<omolog'iac\bibvsend
\vs Heb 4:15
o>u
g`ar
>'eqomen
>arqier'ea
m`h
dun'amenon
sumpaj~hsai
ta~ic
>asjene'iaic
<hm~wn
pepeira\r{m}'enon
\fn{\src{T|M}: pepeiramenon, \src{K|V}: pepeirasmenon.}
d`e
kat`a
p'anta
kaj>
<omoi'othta
qwr`ic
<amart'iac\bibvsend
\vs Heb 4:16
proserq'wmeja
o>~un
met`a
parrhs'iac
t~w|
vjr'onw|
t~hc
q'aritoc
<'ina
l'abwmen
>'eleo\r{n}
\fn{\src{TMK}: eleon, \src{V}: eleoc.}
ka`i
q'arin
e<'urwmen
e>ic
e>'ukairon
vbo'hjeian\bibvsend
\vs Heb 5:1
p~ac
g`ar
>arqiere`uc
>ex
>anjr'wpwn
lamban'omenoc
<up`er
>anjr'wpwn
kaj'istatai
t`a
pr`oc
t`on
vje`on
<'ina
prosf'erh|
d~wr'a
te
ka`i
vjus'iac
<up`er
<amarti~wn\bibvsend
\vs Heb 5:2
metriopaje~in
dun'amenoc
to~ic
>agnoo~usin
ka`i
planwm'enoic
>epe`i
ka`i
a>ut`oc
per'ikeitai
>asj'eneian\bibvsend
\vs Heb 5:3
ka`i
di`a\r{}
\fn{\src{TMK}: dia tauthn, \src{V}: di authn.}
ta'uthn
>ofe'ilei
kaj`wc
per`i
to~u
lao~u
o<'utwc
ka`i
per`i
<e\r{a}uto~u
\fn{\src{TMK}: eautou, \src{V}: autou.}
prosf'erein
<u\r{p}`er
\fn{\src{TMK}: uper, \src{V}: peri.}
<amarti~wn\bibvsend
\vs Heb 5:4
ka`i
o>uq
<eaut~w|
tic
lamb'anei
t`hn
tim`hn
>al\r{l}`a
\fn{\src{T|K|V}: alla, \src{M}: all.}
<o\r{}
\fn{\src{TMK}: o, \src{V}: \bibempty.}
kalo'umenoc
<up`o
to~u
vjeo~u
kaj'a\r{p}er
\fn{\src{TMK}: kajaper, \src{V}: kajwsper.}
ka`i
<o\r{}
\fn{\src{T|K}: o, \src{M|V}: \bibempty.}
>aar'wn\bibvsend
\vs Heb 5:5
o<'utwc
ka`i
<o
qrist`oc
o>uq
<eaut`on
>ed'oxasen
genhj~hnai
>arqier'ea
>all>
<o
lal'hsac
pr`oc
a>ut`on
u<i'oc
mou
e>~i
s`u
>eg`w
s'hmeron
geg'ennhk'a
se\bibvsend
\vs Heb 5:6
kaj`wc
ka`i
>en
<et'erw|
l'egei
\r{s}`u
\fn{\src{TMKVN}: su, \src{Pap[46]}: su ei.}
<iere`uc
e>ic
t`on
a>i~wna
kat`a
t`hn
t'axin
melqised'ek\bibvsend
\vs Heb 5:7
<`oc
>en
ta~ic
<hm'eraic
t~hc
sark`oc
a>uto~u
de'hseic
te
ka`i
<ikethr'iac
pr`oc
t`on
dun'amenon
s'wzein
a>ut`on
>ek
vjan'atou
met`a
kraug~hc
>isqur~ac
ka`i
dakr'uwn
prosen'egkac
ka`i
e>isakousje`ic
>ap`o
t~hc
e>ulabe'iac\bibvsend
\vs Heb 5:8
ka'iper
>`wn
u<i`oc
>'emajen
>af>
<~wn
>'epajen
t`hn
<upako'hn\bibvsend
\vs Heb 5:9
ka`i
teleiwje`ic
>eg'eneto
to~ic\r{}
\fn{\src{TMK}: toic upakouousin autw pasin, \src{V}: pasin toic upakouousin autw.}
<upako'uousin
a>ut~w|
p~asin
a>'itioc
swthr'iac
a>iwn'iou\bibvsend
\vs Heb 5:10
prosagoreuje`ic
<up`o
to~u
vjeo~u
>arqiere`uc
kat`a
t`hn
t'axin
melqised'ek\bibvsend
\vs Heb 5:11
per`i
o<~u
pol`uc
<hm~in
<o
l'ogoc
ka`i
duserm'hneutoc
l'egein
>epe`i
nwjro`i
geg'onate
ta~ic
>akoa~ic\bibvsend
\vs Heb 5:12
ka`i
g`ar
>ofe'ilontec
e>~inai
did'askaloi
di`a
t`on
qr'onon
p'alin
qre'ian
>'eqete
to~u
did'askein
<um~ac
tin`a
t`a
stoiqe~ia
t~hc
>arq~hc
t~wn
log'iwn
to~u
vjeo~u
ka`i
geg'onate
qre'ian
>'eqontec
g'alaktoc
ka`i
o>u
stere~ac
trof~hc\bibvsend
\vs Heb 5:13
p~ac
g`ar
<o
met'eqwn
g'alaktoc
>'apeiroc
l'ogou
dikaios'unhc
n'hpioc
g'a\r{r}
\fn{\src{TMKVN}: gar, \src{F}: gar akmhn.}
>estin\bibvsend
\vs Heb 5:14
tele'iwn
d'e
>estin
<h
stere`a
trof`h
t~wn
di`a
t`hn
<'exin
t`a
a>isjht'hria
gegumnasm'ena
>eq'ontwn
pr`oc
di'akrisin
kalo~u
te
ka`i
kako~u\bibvsend
\vs Heb 6:1
di`o
>af'entec
t`on
t~hc
>arq~hc
to~u
qristo~u
l'ogon
>ep`i
t`hn
telei'othta
vfer'wmeja
m`h
p'alin
vjem'elion
kataball'omenoi
metano'iac
>ap`o
nekr~wn
>'ergwn
ka`i
p'istewc
>ep`i
vje'on\bibvsend
\vs Heb 6:2
vbaptism~wn
didaq~h\r{c}
\fn{\src{TMKVN}: didaqhc, \src{B}: didaqhn.}
>epij'ese'wc
te
qeir~wn
>anast'ase'wc
te
nekr~wn
ka`i
kr'imatoc
a>iwn'iou\bibvsend
\vs Heb 6:3
ka`i
to~uto
poi'hs\r{o}men
\fn{\src{T|K|V}: poihsomen, \src{M}: poihswmen.}
>e'anper
>epitr'eph|
<o
vje'oc\bibvsend
\vs Heb 6:4
>ad'unaton
g`ar
to`uc
<'apax
vfwtisj'entac
geusam'enouc
te
t~hc
dwre~ac
t~hc
>epouran'iou
ka`i
met'oqouc
genhj'entac
pne'umatoc
<ag'iou\bibvsend
\vs Heb 6:5
ka`i
kal`on
geusam'enouc
vjeo~u
<r~hma
dun'ameic
te
m'ellontoc
a>i~wnoc\bibvsend
\vs Heb 6:6
ka`i
parapes'ontac
p'alin
>anakain'izein
e>ic
met'anoian
>anastauro~untac
<eauto~ic
t`on
u<i`on
to~u
vjeo~u
ka`i
paradeigmat'izontac\bibvsend
\vs Heb 6:7
g~h
g`ar
<h
pio~usa
t`on
>ep>
a>ut~hc
poll'akic\r{}
\fn{\src{TMK}: pollakic erqomenon, \src{V}: erqomenon pollakic.}
>erq'omenon
<uet`on
ka`i
t'iktousa
vbot'anhn
e>'ujeton
>eke'inoic
di>
o<`uc
ka`i
gewrge~itai
metalamb'anei
e>ulog'iac
>ap`o
to~u
vjeo~u\bibvsend
\vs Heb 6:8
>ekf'erousa
d`e
>ak'anjac
ka`i
trib'olouc
>ad'okimoc
ka`i
kat'arac
>egg`uc
<~hc
t`o
t'eloc
e>ic
ka~usin\bibvsend
\vs Heb 6:9
pepe'ismeja
d`e
per`i
<um~wn
>aga\r{p}hto`i
\fn{\src{TMKVN}: agaphtoi, \src{aleph}: adelfoi, \src{F}: agaphtoi adelfoi.}
t`a
kre'i\r{t}tona
\fn{\src{T|K}: kreittona, \src{M|V}: kreissona.}
ka`i
>eq'omena
swthr'iac
e>i
ka`i
o<'utwc
lalo~umen\bibvsend
\vs Heb 6:10
o>u
g`ar
>'adikoc
<o
vje`oc
>epilaj'esjai
to~u
>'ergou
<um~wn
ka`i
to~u\r{}
\fn{\src{TMK}: tou kopou, \src{V}: \bibempty.}
k'opou
t~hc
>ag'aphc
<~h\r{c}
\fn{\src{TMKVN}: hc, \src{Pap[46]}: hn.}
>en\r{e}de'ixasje
\fn{\src{T|V}: enedeixasje, \src{M|K}: endeixasje.}
e>ic
t`o
>'onoma
a>uto~u
diakon'hsantec
to~ic
<ag'ioic
ka`i
diakono~untec\bibvsend
\vs Heb 6:11
>epijumo~umen
d`e
<'ekaston
<um~wn
t`hn
a>ut`hn
>ende'iknusjai
spoud`hn
pr`oc
t`hn
plhrofor'ian
t~hc
>el\r{p}'idoc
\fn{\src{TMKVN}: elpidoc, \src{F}: pistewc.}
>'aqri
t'elouc\bibvsend
\vs Heb 6:12
<'ina
m`h
nwjro`i
g'enhsje
mimhta`i
d`e
t~wn
di`a
p'istewc
ka`i
makrojum'iac
klhronomo'untwn
t`ac
>epaggel'iac\bibvsend
\vs Heb 6:13
t~w|
g`ar
>abra`am
>epaggeil'amenoc
<o
vje`oc
>epe`i
kat>
o>uden`oc
e>~iqen
me'izonoc
>om'osai
>'wmosen
kaj>
<eauto~u\bibvsend
\vs Heb 6:14
l'egwn
>~h\r{}
\fn{\src{TMK}: h, \src{V}: ei.}
m`hn
e>ulog~wn
e>ulog'hsw
se
ka`i
plhj'unwn
plhjun~w
se\bibvsend
\vs Heb 6:15
ka`i
o<'utwc
makrojum'hsac
>ep'etuqen
t~hc
>epaggel'iac\bibvsend
\vs Heb 6:16
>'anjrwpoi
m`e\r{n}
\fn{\src{TMK}: men, \src{V}: \bibempty.}
g`ar
kat`a
to~u
me'izonoc
>omn'uousin
ka`i
p'ashc
a>uto~ic
>antilog'iac
p'erac
e>ic
vbeba'iwsin
<o
<'orkoc\bibvsend
\vs Heb 6:17
>en
<~w|
periss'oteron
vboul'omenoc
<o
vje`oc
>epide~ixai
to~ic
klhron'omoic
t~hc
>epaggel'iac
t`o
>amet'ajeton
t~hc
vboul~hc
a>uto~u
>emes'iteusen
<'orkw|\bibvsend
\vs Heb 6:18
<'ina
di`a
d'uo
pragm'atwn
>ametaj'etwn
>en
o<~ic
>ad'unaton
ye'usasjai
vj\r{e}`on
\fn{\src{TMK}: vjeon, \src{V}: [ton] vjeon.}
>isqur`an
par'aklhsin
>'eqwmen
o<i
katafug'ontec
krat~hsai
t~hc
prokeim'enhc
>elp'idoc\bibvsend
\vs Heb 6:19
<`hn
<wc
>'agkuran
>'eqomen
t~hc
yuq~hc
>asfal~h
te
ka`i
vbeba'ian
ka`i
e>iserqom'enhn
e>ic
t`o
>es'wteron
to~u
katapet'asmatoc\bibvsend
\vs Heb 6:20
<'opou
pr'odromoc
<up`er
<hm~wn
e>is~hljen
>ihso~uc
kat`a
t`hn
t'axin
melqised`ek
>arqiere`uc
gen'omenoc
e>ic
t`on
a>i~wna\bibvsend
\vs Heb 7:1
o<~utoc
g`ar
<o
melqised`ek
vbasile`uc
sal`hm
<iere`uc
to~u
vjeo~u
to~u
<uy'istou
<o
sunant'hsac
>abra`am
<upostr'efonti
>ap`o
t~hc
kop~hc
t~wn
vbasil'ewn
ka`i
e>ulog'hsac
a>ut'on\bibvsend
\vs Heb 7:2
<~w|
ka`i
dek'athn
>ap`o
p'antwn
>em'erisen
>abra`am
pr~wton
m`en
<ermhneu'omenoc
vbasile`uc
dikaios'unhc
>'epeita
d`e
ka`i
vbasile`uc
sal`hm
<'o
>estin
vbasile`uc
e>ir'hnhc\bibvsend
\vs Heb 7:3
>ap'atwr
>am'htwr
>ageneal'oghtoc
m'hte
>arq`hn
<hmer~wn
m'hte
vzw~hc
t'eloc
>'eqwn
>afwmoiwm'enoc
d`e
t~w|
u<i~w|
to~u
vjeo~u
m'enei
<iere`uc
e>ic
t`o
dihnek'ec\bibvsend
\vs Heb 7:4
vjewre~ite
d`e
phl'ikoc
o<~utoc
<~w|
ka`i
dek'athn
>abra`am
>'edwken
>ek
t~wn
>akrojin'iwn
<o
patri'arqhc\bibvsend
\vs Heb 7:5
ka`i
o<i
m`en
>ek
t~wn
u<i~wn
leu"`i
t`hn
<ierate'ian
lamb'anontec
>entol`hn
>'eqousin
>apodekato~un
t`on
la`on
kat`a
t`on
n'omon
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
to`uc
>adelfo`uc
a>ut~wn
ka'iper
>exelhluj'otac
>ek
t~hc
>osf'uoc
>abra'am\bibvsend
\vs Heb 7:6
<o
d`e
m`h
genealogo'umenoc
>ex
a>ut~wn
dedek'atwken
t`on\r{}
\fn{\src{TMK}: ton, \src{V}: \bibempty.}
>abra`am
ka`i
t`on
>'eqonta
t`ac
>epaggel'iac
e>ul'oghken\bibvsend
\vs Heb 7:7
qwr`ic
d`e
p'ashc
>antilog'iac
t`o
>'elatton
<up`o
to~u
kre'ittonoc
e>uloge~itai\bibvsend
\vs Heb 7:8
ka`i
<~wde
m`en
dek'atac
>apojn'hskontec
>'anjrwpoi
lamb'anousin
>eke~i
d`e
marturo'umenoc
<'oti
vz~h|\bibvsend
\vs Heb 7:9
ka`i
<wc
>'epoc
e>ipe~in
di`a\r{}
\fn{\src{TMK}: dia, \src{V}: di.}
>abra`am
ka`i
leu"`i
<o
dek'atac
lamb'anwn
dedek'atwtai\bibvsend
\vs Heb 7:10
>'eti
g`ar
>en
t~h|
>osf'u"i
to~u
patr`oc
>~hn
<'ote
sun'hnthsen
a>ut~w|
<o\r{}
\fn{\src{TMK}: o, \src{V}: \bibempty.}
melqised'ek\bibvsend
\vs Heb 7:11
e>i
m`en
o>~un
tele'iwsic
di`a
t~hc
leu"itik~hc
<ierws'unhc
>~hn
<o
la`oc
g`ar
>ep>
a>ut~h|\r{}
\fn{\src{TMK}: auth nenomojethto, \src{V}: authc nenomojethtai.}
nenomoj'ethto
t'ic
>'eti
qre'ia
kat`a
t`hn
t'axin
melqised`ek
<'eteron
>an'istasjai
<ier'ea
ka`i
o>u
kat`a
t`hn
t'axin
>aar`wn
l'egesjai\bibvsend
\vs Heb 7:12
metatijem'enhc
g`ar
t~hc
<ierws'unhc
>ex
>an'agkhc
ka`i
n'omou
met'ajesic
g'inetai\bibvsend
\vs Heb 7:13
>ef>
<`on
g`ar
l'egetai
ta~uta
vful~hc
<et'erac
met'esqhken
>af>
<~hc
o>ude`ic
pros'esqhken
t~w|
vjusiasthr'iw|\bibvsend
\vs Heb 7:14
pr'odhlon
g`ar
<'oti
>ex
>io'uda
>anat'etalken
<o
k'urioc
<hm~wn
e>ic
<`hn
vful`hn
o>ud`en\r{}
\fn{\src{TMK}: ouden peri ierwsunhc, \src{V}: peri ierewn ouden.}
per`i
<ierws'unhc
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
>el'alhsen\bibvsend
\vs Heb 7:15
ka`i
periss'oteron
>'eti
kat'adhl'on
>estin
e>i
kat`a
t`hn
<omoi'othta
melqised`ek
>an'istatai
<iere`uc
<'eteroc\bibvsend
\vs Heb 7:16
<`oc
o>u
kat`a
n'omon
>entol~hc
sarki\r{k}~hc
\fn{\src{TMK}: sarkikhc, \src{V}: sarkinhc.}
g'egonen
>all`a
kat`a
d'unamin
vzw~hc
>akatal'utou\bibvsend
\vs Heb 7:17
martur\r{e}~i
\fn{\src{TMK}: marturei, \src{V}: martureitai.}
g`ar
<'oti
s`u
<iere`uc
e>ic
t`on
a>i~wna
kat`a
t`hn
t'axin
melqised'ek\bibvsend
\vs Heb 7:18
>aj'ethsic
m`en
g`ar
g'inetai
proago'ushc
>entol~hc
di`a
t`o
a>ut~hc
>asjen`ec
ka`i
>anwfel'ec\bibvsend
\vs Heb 7:19
o>ud`en
g`ar
>etele'iwsen
<o
n'omoc
>epeisagwg`h
d`e
kre'ittonoc
>elp'idoc
di>
<~hc
>egg'izomen
t~w|
vje~w|\bibvsend
\vs Heb 7:20
ka`i
kaj>
<'oson
o>u
qwr`ic
<orkwmos'iac\bibvsend
\vs Heb 7:21
o<i
m`en
g`ar
qwr`ic
<orkwmos'iac
e>is`in
<iere~ic
gegon'otec
<o
d`e
met`a
<orkwmos'iac
di`a
to~u
l'egontoc
pr`oc
a>ut`on
>'wmosen
k'urioc
ka`i
o>u
metamelhj'hsetai
s`u
<iere`uc
e>ic
t`on
a>i~wna
kat`a\r{}
\fn{\src{TMK}: kata thn taxin melqisedek, \src{V}: \bibempty.}
t`hn
t'axin
melqised'ek\bibvsend
\vs Heb 7:22
kat`a
toso~uto\r{n}
\fn{\src{TMK}: tosouton, \src{V}: tosouto [kai].}
kre'ittonoc
diaj'hkhc
g'egonen
>'egguoc
>ihso~uc\bibvsend
\vs Heb 7:23
ka`i
o<i
m`en
ple'ion'ec
e>isin
gegon'otec
<iere~ic
di`a
t`o
vjan'atw|
kwl'uesjai
param'enein\bibvsend
\vs Heb 7:24
<o
d`e
di`a
t`o
m'enein
a>ut`on
e>ic
t`on
a>i~wna
>apar'abaton
>'eqei
t`hn
<ierws'unhn\bibvsend
\vs Heb 7:25
<'ojen
ka`i
s'wzein
e>ic
t`o
pantel`ec
d'unatai
to`uc
proserqom'enouc
di>
a>uto~u
t~w|
vje~w|
p'antote
vz~wn
e>ic
t`o
>entugq'anein
<up`er
a>ut~wn\bibvsend
\vs Heb 7:26
toio~utoc
g`ar
<hm~i\r{n}
\fn{\src{TMK}: hmin, \src{V}: hmin kai.}
>'eprepen
>arqiere`uc
<'osioc
>'akakoc
>am'iantoc
keqwrism'enoc
>ap`o
t~wn
<amartwl~wn
ka`i
<uyhl'oteroc
t~wn
o>uran~wn
gen'omenoc\bibvsend
\vs Heb 7:27
<`oc
o>uk
>'eqei
kaj>
<hm'eran
>an'agkhn
<'wsper
o<i
>arqiere~ic
pr'oteron
<up`er
t~wn
>id'iwn
<amarti~wn
vjus'iac
>anaf'erein
>'epeita
t~wn
to~u
lao~u
to~uto
g`ar
>epo'ihsen
>ef'apax
<eaut`on
>anen'egkac\bibvsend
\vs Heb 7:28
<o
n'omoc
g`ar
>anjr'wpouc
kaj'isthsin
>arqiere~ic
>'eqontac
>asj'eneian
<o
l'ogoc
d`e
t~hc
<orkwmos'iac
t~hc
met`a
t`on
n'omon
u<i`on
e>ic
t`on
a>i~wna
teteleiwm'enon\bibvsend
\vs Heb 8:1
kef'alaion
d`e
>e\r{p}`i
\fn{\src{TMKVN}: epi, \src{A}: en.}
to~ic
legom'enoic
toio~uton
>'eqomen
>arqier'ea
<`oc
>ek'ajisen
>en
dexi~a|
to~u
vjr'onou
t~hc
megalws'unhc
>en
to~ic
\r{o}>urano~ic\bibvsend
\fn{\src{TMKVN}: ouranoic, \src{F}: uyhloic.}
\vs Heb 8:2
t~wn
<ag'iwn
leitourg`oc
ka`i
t~hc
skhn~hc
t~hc
>alhjin~hc
<`hn
>'ephxen
<o
k'urioc
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
o>uk
>'anjrwpoc\bibvsend
\vs Heb 8:3
p~ac
g`ar
>arqiere`uc
e>ic
t`o
prosf'erein
d~wr'a
te
ka`i
vjus'iac
kaj'istatai
<'ojen
>anagka~ion
>'eqein
ti
ka`i
to~uton
<`o
prosen'egkh|\bibvsend
\vs Heb 8:4
e>i
m`en
\r{g}`ar
\fn{\src{TMK}: gar, \src{V}: oun.}
>~hn
>ep`i
g~hc
o>ud>
>`an
>~hn
<iere`uc
>'ontwn
t~wn\r{}
\fn{\src{TMK}: twn ierewn, \src{V}: \bibempty.}
<ier'ewn
t~wn
prosfer'ontwn
kat`a
\r{t}`on
\fn{\src{TMK}: ton, \src{V}: \bibempty.}
n'omon
t`a
d~wra\bibvsend
\vs Heb 8:5
o<'itinec
<upode'igmati
ka`i
ski~a|
latre'uousin
t~wn
>epouran'iwn
kaj`wc
keqrhm'atistai
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
m'ellwn
>epitele~in
t`hn
skhn`hn
<'ora
g'ar
vfhsin
poi'h\r{s}h|c
\fn{\src{T|K}: poihshc, \src{M|V}: poihseic.}
p'anta
kat`a
t`on
t'upon
t`on
deiqj'enta
soi
>en
t~w|
>'orei\bibvsend
\vs Heb 8:6
nu\r{n}`i
\fn{\src{TMK}: nuni, \src{V}: nun[i], \src{Pap[46*]}: nun.}
d`e
diaforwt'erac
t'et\r{e}uqen
\fn{\src{T|K}: teteuqen, \src{M|V}: tetuqen, \src{F}: tetuqhken.}
leitourg'iac
<'osw|
k\r{a}`i
\fn{\src{TMKVN}: kai, \src{F}: \bibempty.}
kre'itton'oc
>estin
diaj'hkhc
mes'ithc
<'htic
>ep`i
kre'ittosin
>epaggel'iaic
nenomoj'ethtai\bibvsend
\vs Heb 8:7
e>i
g`ar
<h
pr'wth
>eke'inh
>~hn
>'amemptoc
o>uk
>`an
de\r{u}t'erac
\fn{\src{TMKVN}: deuterac, \src{B}: eterac, \src{F}: deuteroc.}
>ezhte~ito
t'opoc\bibvsend
\vs Heb 8:8
memf'omenoc
g`ar
a>ut\r{o}~ic
\fn{\src{TMK}: autoic, \src{V}: autouc.}
l'egei
>ido`u
<hm'erai
>'erqontai
l'egei
k'urioc
ka`i
suntel'esw
>ep`i
t`on
o>~ikon
>isra`hl
ka`i
>ep`i
t`on
o>~ikon
>io'uda
diaj'hkhn
kain'hn\bibvsend
\vs Heb 8:9
o>u
kat`a
t`hn
diaj'hkhn
<`hn
>epo'ihsa
to~ic
patr'asin
a>ut~wn
>en
<hm'e\r{r}a|
\fn{\src{TMKVN}: hmera, \src{B}: hmeraic.}
>epilabom'enou
mou
t~hc
qeir`oc
a>ut~wn
>exagage~in
a>uto`uc
>ek
g~hc
a>ig'uptou
<'oti
a>uto`i
o>uk
>en'emeinan
>en
t~h|
diaj'hkh|
mou
k>ag`w
>hm'elhsa
a>ut~wn
l'egei
k'urioc\bibvsend
\vs Heb 8:10
<'oti
a<'uth
<h
diaj'hk\r{h}
\fn{\src{TMKVN}: diajhkh, \src{A}: diajhkh mou.}
<`hn
diaj'hsomai
t~w|
o>'ikw|
>isra`hl
met`a
t`ac
<hm'erac
>eke'inac
l'egei
k'urioc
dido`uc
n'omouc
mou
e>ic
t`hn
di'anoian
a>ut~wn
ka`i
>ep`i
kard'ia\r{c}
\fn{\src{TMKVN}: kardiac, \src{aleph}: kardian, \src{B}: kardia, \src{F}: kardiaic.}
a>ut~wn
>e\r{p}igr'ayw
\fn{\src{TMKVN}: epigrayw, \src{B|Pap[46]}: grayw.}
a>uto`uc
ka`i
>'esomai
a>uto~ic
e>ic
vje`on
ka`i
a>uto`i
>'esonta'i
moi
e>ic
la'on\bibvsend
\vs Heb 8:11
ka`i
o>u
m`h
did'axwsin
<'e\r{k}astoc
\fn{\src{TMKVN}: ekastoc, \src{Pap[46]}: eteroc.}
t`on
plh\r{s}'ion
\fn{\src{T|K}: plhsion, \src{M|V}: polithn.}
a>uto~u
ka`i
<'ekastoc
t`on
>adelf`on
a>u\r{t}o~u
\fn{\src{TMKVN}: autou, \src{Pap[46]}: \bibempty.}
l'egwn
gn~wji
t`on
k'urion
<'oti
p'antec
e>id'hsous'in
me
>ap`o
mikro~u
a>u\r{t}~wn
\fn{\src{TMK}: autwn, \src{V}: \bibempty.}
<'ewc
meg'alou
a>ut~wn\bibvsend
\vs Heb 8:12
<'oti
<'ilewc
>'esomai
ta~ic
>adik'iaic
a>ut~wn
ka`i
t~wn
<amarti~wn
a>ut~wn
ka`i\r{}
\fn{\src{TMK}: kai twn anomiwn autwn, \src{V}: \bibempty.}
t~wn
>anomi~wn
a>ut~wn
o>u
m`h
mnhsj~w
>'eti\bibvsend
\vs Heb 8:13
>en
t~w|
l'egein
kain`hn
pepala'iwken
t`hn
pr'wthn
t`o
d`e
palaio'umenon
ka`i
ghr'askon
>egg`uc
>afanismo~u\bibvsend
\vs Heb 9:1
e>~iqen
m`en
o>~un
ka`i
<h
pr'wth
sk\r{h}n`h
\fn{\src{T}: skhnh, \src{K|M|V}: \bibempty.}
dikai'wmata
latre'iac
t'o
te
<'agion
kosmik'on\bibvsend
\vs Heb 9:2
skhn`h
g`ar
kateskeu'asjh
<h
pr'wth
>en
<~h|
<'h
te
luqn'ia
ka`i
<h
tr'apeza
ka`i
<h
pr'ojesic
t~wn
>'artw\r{n}
\fn{\src{TMKVN}: artwn, \src{B}: artwn kai to qrusoun vjumiathrion.}
<'htic
l'egetai
<a\r{g}'ia\bibvsend
\fn{\src{T}: <ag'ia, \src{K|M|V}: <'agia, \src{B}: ta agia, \src{A|Pap[46]}: agia agiwn.}
\vs Heb 9:3
met`a
d`e
t`o
de'uteron
katap'etasma
skhn`h
<h
legom'enh
<'agia\r{}
\fn{\src{TMKVN}: agia agiwn, \src{B}: ta agia twn agiwn, \src{Pap[46]}: ana, \src{F}: agia twn agiwn.}
<ag'iwn\bibvsend
\vs Heb 9:4
qruso~un\r{}
\fn{\src{TMKVN}: qrusoun eqousa vjumiathrion kai, \src{B}: eqousa.}
>'eqousa
vjumiat'hrion
ka`i
t`hn
kibwt`on
t~hc
diaj'hkhc
perikekalumm'enhn
p'antojen
qrus'iw|
>en
<~h|
st'amnoc
qrus~h
>'eqousa
t`o
m'anna
ka`i
<h
<r'abdoc
>aar`wn
<h\r{}
\fn{\src{TMKVN}: h, \src{B}: \bibempty.}
vblast'hsasa
ka`i
a<i
pl'akec
t~hc
diaj'hkhc\bibvsend
\vs Heb 9:5
<uper'anw
d`e
a>ut~hc
qeroub`i\r{m}
\fn{\src{TMK}: qeroubim, \src{V}: qeroubin.}
d'oxhc
kataski'azonta
t`o
<ilast'hrion
per`i
<~wn
o>uk
>'estin
n~un
l'egein
kat`a
m'eroc\bibvsend
\vs Heb 9:6
to'utwn
d`e
o<'utwc
kateskeuasm'enwn
e>ic
m`en
t`hn
pr'wthn
skhn`hn
dia\r{p}ant`oc
\fn{\src{T}: diapantoc, \src{K|M|V}: dia pantoc.}
e>is'iasin
o<i
<iere~ic
t`ac
latre'iac
>epitelo~untec\bibvsend
\vs Heb 9:7
e>ic
d`e
t`hn
deut'eran
<'apax
to~u
>eniauto~u
m'onoc
<o
>arqiere`uc
o>u
qwr`ic
a<'imatoc
<`o
prosf'erei
<up`er
<eauto~u
ka`i
t~wn
to~u
lao~u
>agnohm'atwn\bibvsend
\vs Heb 9:8
to~uto
dhlo~untoc
to~u
pne'umatoc
to~u
<ag'iou
m'hpw
pefaner~wsjai
t`hn
t~wn
<ag'iwn
<od`on
>'eti
t~hc
pr'wthc
skhn~hc
>eqo'ushc
st'asin\bibvsend
\vs Heb 9:9
<'htic
\r{p}arabol`h
\fn{\src{TMKVN}: parabolh, \src{F}: prwth parabolh.}
e>ic
t`on
kair`on
t`on
>enesthk'ota
kaj>
<`o\r{n}
\fn{\src{TMK}: on, \src{V}: hn.}
d~wr'a
te
ka`i
vjus'iai
prosf'erontai
m`h
dun'amenai
kat`a
sune'idhsin
telei~wsai
t`on
latre'uonta\bibvsend
\vs Heb 9:10
m'onon
>ep`i
vbr'wmasin
ka`i
p'omasin
ka`i
diaf'oroic
vbaptismo~ic
ka`i\r{}
\fn{\src{TMK}: kai dikaiwmasin, \src{V}: dikaiwmata.}
dikai'wmasin
sark`oc
m'eqri
kairo~u
diorj'wsewc
>epike'imena\bibvsend
\vs Heb 9:11
qrist`oc
d`e
paragen'omenoc
>arqiere`uc
t~wn
\r{m}ell'ontwn
\fn{\src{TMK}: mellontwn, \src{V}: genomenwn.}
>agaj~wn
di`a
t~hc
me'izonoc
ka`i
teleiot'erac
skhn~hc
o>u
qeiropoi'htou
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
o>u
ta'uthc
t~hc
kt'isewc\bibvsend
\vs Heb 9:12
o>ud`e
di>
a<'imatoc
tr'agwn
ka`i
m'osqwn
di`a
d`e
to~u
>id'iou
a<'imatoc
e>is~hljen
>ef'apax
e>ic
t`a
<'agi\r{a}
\fn{\src{TMKVN}: agia, \src{F}: agia twn agiwn.}
a>iwn'ian
l'utrwsin
e<ur'amenoc\bibvsend
\vs Heb 9:13
e>i
g`ar
t`o
a<~ima
ta'urwn\r{}
\fn{\src{TMK}: taurwn kai tragwn, \src{V}: tragwn kai taurwn.}
ka`i
tr'agwn
ka`i
spod`oc
dam'alewc
<rant'izousa
to`uc
kekoinwm'enouc
<agi'azei
pr`oc
t`hn
t~hc
sark`oc
kajar'othta\bibvsend
\vs Heb 9:14
p'osw|
m~allon
t`o
a<~ima
to~u
qristo~u
<`oc
di`a
pne'umatoc
a>iw\r{n}'iou
\fn{\src{TMKVN}: aiwniou, \src{F}: agiou.}
<eaut`on
pros'hnegken
>'amwmon
t~w|
vje~w|
kajarie~i
t`hn
sune'idhsin
<u\r{m}~wn
\fn{\src{TMK}: umwn, \src{V}: hmwn.}
>ap`o
nekr~wn
>'ergwn
e>ic
t`o
latre'uein
vje~w|
vz~wnti\bibvsend
\vs Heb 9:15
ka`i
di`a
to~uto
diaj'hkhc
kain~hc
mes'ithc
>est`in
<'opwc
vjan'atou
genom'enou
e>ic
>apol'utrwsin
t~wn
>ep`i
t~h|
pr'wth|
diaj'hkh|
parab'asewn
t`hn
>epaggel'ian
l'abwsin
o<i
keklhm'enoi
t~hc
a>iwn'iou
klhronom'iac\bibvsend
\vs Heb 9:16
<'opou
g`ar
diaj'hkh
vj'anaton
>an'agkh
vf'eresjai
to~u
diajem'enou\bibvsend
\vs Heb 9:17
diaj'hkh
g`ar
>ep`i
nekro~ic
vbeba'ia
>epe`i
m'h\r{}
\fn{\src{T|K}: mh pote, \src{M|V}: mhpote, \src{aleph}: mh tote.}
pote
>isq'uei
<'ote
vz~h|
<o
diaj'emenoc\bibvsend
\vs Heb 9:18
<'ojen
\r{o}>ud>
\fn{\src{TMK}: oud, \src{V}: oude.}
<h
pr'wth
qwr`ic
a<'imatoc
>egkeka'inistai\bibvsend
\vs Heb 9:19
lalhje'ishc
g`ar
p'ashc
>e\r{n}tol~hc
\fn{\src{TMKVN}: entolhc, \src{Pap[46]}: thc entolhc.}
kat`a
\r{n}'omon
\fn{\src{TMK}: nomon, \src{V}: ton nomon.}
<up`o
mw"us'ewc
pant`i
t~w|
la~w|
lab`wn
t`o
a<~ima
t~wn
m'osqwn
ka`i\r{}
\fn{\src{TMK}: kai tragwn, \src{V}: [kai twn tragwn], \src{Pap[46]}: \bibempty.}
tr'agwn
me\r{t}`a
\fn{\src{TMKVN}: meta, \src{Pap[46]}: mej.}
<'udatoc
ka`i
>er'iou
kokk'inou
ka`i
<uss'wpou
a>ut'o
te
t`o
vbibl'ion
ka`i
p'anta
t`on
la`on
>er\r{r}'antisen\bibvsend
\fn{\src{TMK}: errantisen, \src{V}: erantisen.}
\vs Heb 9:20
l'egwn
to~uto
t`o
a<~ima
t~hc
diaj'hkhc
<~hc
>enete'ilato
pr`oc
<um~ac
<o
vje'oc\bibvsend
\vs Heb 9:21
ka`i
t`hn
skhn`hn
d`e
ka`i
p'anta
t`a
ske'uh
t~hc
leitourg'iac
t~w|
a<'imati
<omo'iwc
>err'antisen\bibvsend
\fn{\src{TMK|V[*]}: >err'antisen, \src{V|N}: >er'antisen.}
\vs Heb 9:22
ka`i
sqed`on
>en
a<'imati
p'anta
kajar'izetai
kat`a
t`on
n'omon
ka`i
qwr`ic
a<imatekqus'iac
o>u
g'inetai
>'afesic\bibvsend
\vs Heb 9:23
>an'agkh
o>~un
t`a
m`en
<upode'igmata
t~wn
>en
to~ic
o>urano~ic
to'utoic
kajar'izesjai
a>ut`a
d`e
t`a
>epour'ania
kre'ittosin
vjus'iaic
par`a
ta'utac\bibvsend
\vs Heb 9:24
o>u
g`ar
e>ic
qeiropo'ihta
<'agia\r{}
\fn{\src{TMK}: agia eishljen o, \src{V}: eishljen agia.}
e>is~hljen
<o
qrist`oc
>ant'itupa
t~wn
>alhjin~wn
>all>
e>ic
a>ut`on
t`on
o>uran`on
n~un
>emfanisj~hnai
t~w|
pros'wpw|
to~u
vjeo~u
<up`er
<hm~wn\bibvsend
\vs Heb 9:25
o>ud>
<'ina
poll'akic
prosf'erh|
<eaut`on
<'wsper
<o
>arqiere`uc
e>is'erqetai
e>ic
t`a
<'agi\r{a}
\fn{\src{TMKVN}: agia, \src{F}: agia twn agiwn.}
kat>
>eniaut`on
>en
a<'imati
>allotr'iw|\bibvsend
\vs Heb 9:26
>epe`i
>'edei
a>ut`on
poll'akic
\r{p}aje~in
\fn{\src{TMKVN}: pajein, \src{F}: apojanein.}
>ap`o
katabol~hc
k'osmou
n~u\r{n}
\fn{\src{TMK}: nun, \src{V}: nuni.}
d`e
<'apax
>ep`i
suntele'ia|
t~wn
a>i'wnwn
e>ic
>aj'ethsin
<a\r{m}art'iac
\fn{\src{TMK}: amartiac, \src{V}: [thc] amartiac, \src{F}: amartiwn.}
di`a
t~hc
vjus'iac
a>uto~u
pefan'erwtai\bibvsend
\vs Heb 9:27
ka`i
kaj>
<'oson
>ap'okeitai
to~ic
>anjr'wpoic
<'apax
>apojane~in
met`a
d`e
to~uto
kr'isic\bibvsend
\vs Heb 9:28
o<'utwc
<o\r{}
\fn{\src{T|K}: o, \src{M|V}: kai o.}
qrist`oc
<'apax
proseneqje`ic
e>ic
t`o
poll~wn
>anenegke~in
<amart'iac
>ek
deut'erou
qwr`ic
<amart'iac
>ofj'hsetai
to~ic
a>ut`on
>apekdeqom'enoic
e>ic
swthr'ia\r{n}\bibvsend
\fn{\src{TMKVN}: swthrian, \src{A}: swthrian dia pistewc.}
\vs Heb 10:1
ski`an
g`ar
>'eqwn
<o
n'omoc
t~wn
mell'ontwn
>agaj~wn
o>uk
a>ut`hn
t`hn
e>ik'ona
t~wn
pragm'atwn
kat>
>eniaut`on
ta~ic
a>uta~ic
vjus'iaic
<`ac
prosf'erousin
e>ic
t`o
dihnek`ec
o>ud'epote
d'una\r{t}ai
\fn{\src{T|K|V}: dunatai, \src{M}: dunantai.}
to`uc
proserqom'enouc
telei~wsai\bibvsend
\vs Heb 10:2
>epe`i
o>uk
>`an
>epa'usanto
prosfer'omenai
di`a
t`o
mhdem'ian
>'eqein
>'eti
sune'idhsin
<amarti~wn
to`uc
latre'uontac
<'apax
kekajar\r{m}'enouc\bibvsend
\fn{\src{TMK}: kekajarmenouc, \src{V}: kekajarismenouc.}
\vs Heb 10:3
>all>
>en
a>uta~ic
>an'amnhsic
<amarti~wn
kat>
>eniaut'on\bibvsend
\vs Heb 10:4
>ad'unaton
g`ar
a<~ima
ta'urwn\r{}
\fn{\src{TMKVN}: taurwn kai tragwn, \src{Pap[46]}: tragwn kai taurwn.}
ka`i
tr'agwn
>afai\r{r}e~in
\fn{\src{TMKVN}: afairein, \src{F}: afelein.}
<amart'iac\bibvsend
\vs Heb 10:5
di`o
e>iserq'omenoc
e>ic
t`on
k'osmon
l'egei
vjus'ian
ka`i
prosfor`an
o>uk
>hj'elhsac
s~wma
d`e
kathrt'isw
moi\bibvsend
\vs Heb 10:6
<olokaut'wma\r{t}a
\fn{\src{TMKVN}: olokautwmata, \src{Pap[46]}: olokautwma.}
ka`i
per`i
<amart'iac
o>uk
e>ud'okhsac\bibvsend
\vs Heb 10:7
t'ote
e>~ipon
>ido`u
<'hkw
>en
kefal'idi
vbibl'iou
g'egrapt\r{a}i
\fn{\src{TMKVN}: gegraptai, \src{Pap[46]}: gegraptai gar.}
per`i
>emo~u
to~u
poi~hsai
<o
vje`oc
t`o
vj'elhm'a
sou\bibvsend
\vs Heb 10:8
>an'wteron
l'egwn
<'oti
vjus'ian\r{}
\fn{\src{TMK}: vjusian kai prosforan, \src{V}: vjusiac kai prosforac.}
ka`i
prosfor`an
ka`i
<olokaut'wmata
ka`i
per`i
<amart'iac
o>uk
>hj'elhsac
o>ud`e
e>ud'okhsac
a<'itinec
kat`a
\r{t}`on
\fn{\src{TMK}: ton, \src{V}: \bibempty.}
n'omon
prosf'erontai\bibvsend
\vs Heb 10:9
t'ote
e>'irhken
>ido`u
<'hkw
to~u
poi~hsai
<o\r{}
\fn{\src{TMK}: o vjeoc, \src{V}: \bibempty.}
vje`oc
t`o
vj'elhm'a
sou
>anaire~i
t`o
pr~wton
<'ina
t`o
de'uteron
st'hsh|\bibvsend
\vs Heb 10:10
>en
<~w|
vjel'hmati
<hgiasm'enoi
>esm`en
\r{o}<i
\fn{\src{T|M}: oi, \src{K|V}: \bibempty.}
di`a
t~hc
prosfor~ac
to~u
\r{s}'wmatoc
\fn{\src{TMKVN}: swmatoc, \src{F}: aimatoc.}
t\r{o}~u
\fn{\src{T|K}: tou, \src{M|V}: \bibempty.}
>ihso~u
qristo~u
>ef'apax\bibvsend
\vs Heb 10:11
ka`i
p~ac
m`en
<i\r{e}re`uc
\fn{\src{TMKVN}: iereuc, \src{A|C}: arqiereuc.}
<'esthken
kaj>
<hm'eran
leitourg~wn
ka`i
t`ac
a>ut`ac
poll'akic
prosf'erwn
vjus'iac
a<'itinec
o>ud'epote
d'unantai
periele~in
<amart'ia\r{c}\bibvsend
\fn{\src{TMKVN}: amartiac, \src{Pap[13]}: amartian.}
\vs Heb 10:12
\r{a}>ut`oc
\fn{\src{TMK}: autoc, \src{V}: outoc.}
d`e
m'ian
<up`er
<amarti~wn
prosen'egkac
vjus'ian
e>ic
t`o
dihnek`ec
>ek'ajisen
>en
dexi~a|
to~u
vjeo~u\bibvsend
\vs Heb 10:13
t`o
loip`on
>ekdeq'omenoc
<'ewc
tej~wsin
o<i
>eqjro`i
a>u\r{t}o~u
\fn{\src{TMKVN}: autou, \src{Pap[13]}: \bibempty.}
<upop'odion
t~wn
pod~wn
a>uto~u\bibvsend
\vs Heb 10:14
mi~a|
g`ar
prosfor~a|
tetele'iwken
e>ic
t`o
dihnek`ec
to`uc
<a\r{g}iazom'enouc\bibvsend
\fn{\src{TMKVN}: agiazomenouc, \src{Pap[46]}: anaswzomenouc.}
\vs Heb 10:15
marture~i
d`e
<hm~in
ka`i
t`o
pne~uma
t`o
<'agion
met`a
g`ar
t`o
\r{p}roeirhk'enai\bibvsend
\fn{\src{TMK}: proeirhkenai, \src{V}: eirhkenai.}
\vs Heb 10:16
a<'uth
<h
diaj'hkh
<`hn
diaj'hsomai
pr`oc
a>uto`uc
met`a
t`ac
<hm'erac
>eke'inac
l'egei
k'urioc
dido`uc
n'omouc
mou
>ep`i
kard'iac
a>ut~wn
ka`i
>ep`i
t~wn\r{}
\fn{\src{TMK}: twn dianoiwn, \src{V}: thn dianoian.}
dianoi~wn
a>ut~wn
>epigr'ayw
a>uto'uc\bibvsend
\vs Heb 10:17
ka`i
t~wn
<amarti~wn
a>u\r{t}~wn
\fn{\src{T|K|V}: autwn, \src{M}: \bibempty.}
ka`i
t~wn
>anomi~wn
a>ut~wn
o>u
m`h
mnh\r{s}j~w
\fn{\src{TMK}: mnhsjw, \src{V}: mnhsjhsomai.}
>'eti\bibvsend
\vs Heb 10:18
<'opou
d`e
>'afesic
to'u\r{t}wn
\fn{\src{TMKVN}: toutwn, \src{aleph}: \bibempty.}
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
prosfor`a
per`i
<amart'iac\bibvsend
\vs Heb 10:19
>'eqontec
o>~un
>adelfo`i
parrhs'ian
e>ic
t`hn
e>'isodon
t~wn
<ag'iwn
>en
t~w|
a<'imati
>ihso~u\bibvsend
\vs Heb 10:20
<`hn
>eneka'inisen
<hm~in
<od`on
pr'osfaton
ka`i
vz~wsan
di`a
to~u
katapet'asmatoc
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
t~hc
sark`oc
a>uto~u\bibvsend
\vs Heb 10:21
ka`i
<ier'ea
m'egan
>ep`i
t`on
o>~ikon
to~u
vjeo~u\bibvsend
\vs Heb 10:22
proser\r{q}'wmeja
\fn{\src{TMKVN}: proserqwmeja, \src{Pap[46*]}: proserqomeja.}
met`a
>alhjin~hc
kard'iac
>en
plhrofor'ia|
p'istewc
>e\r{r}rantism'enoi
\fn{\src{TMK}: errantismenoi, \src{V}: vrerantismenoi.}
t`ac
kard'iac
>ap`o
suneid'hsewc
ponhr~ac
ka`i
lelou\r{m}'enoi
\fn{\src{TMK}: leloumenoi, \src{V}: lelousmenoi.}
t`o
s~wma
<'udati
kajar~w|\bibvsend
\vs Heb 10:23
kat'eqwmen
t`hn
<omolog'ian
t~hc
>elp'ido\r{c}
\fn{\src{TMKVN}: elpidoc, \src{aleph}: elpidoc hmwn.}
>aklin~h
pist`oc
g`ar
<o
>epaggeil'amenoc\bibvsend
\vs Heb 10:24
ka`i
katano~wmen
>all'hlouc
e>ic\r{}
\fn{\src{TMKVN}: eic paroxusmon, \src{Pap[46]}: ek paroxusmou.}
paroxusm`on
>ag'aphc
ka`i
kal~wn
>'ergwn\bibvsend
\vs Heb 10:25
m`h
>e\r{g}katale'ipontec
\fn{\src{TMKVN}: egkataleipontec, \src{Pap[46]}: kataleipontec.}
t`hn
>episunagwg`hn
<eaut~wn
kaj`wc
>'ejoc
tis`in
>all`a
parakalo~unte\r{c}
\fn{\src{TMKVN}: parakalountec, \src{F}: parakalountec eautouc.}
ka`i
toso'utw|
m~allon
<'osw|
vbl'epete
>egg'izousan
t`hn
<hm'eran\bibvsend
\vs Heb 10:26
<ekous'iwc
g`ar
<amartan'ontwn
<hm~wn
met`a
t`o
labe~in
t`hn
>ep'ignwsin
t~hc
>alhje'iac
o>uk\r{}
\fn{\src{T}: ouk eti, \src{K|M|V}: ouketi.}
>'eti
per`i
<amarti~wn
>apole'ipetai
vjus'ia\bibvsend
\vs Heb 10:27
vfober`a
d'e
tic
>ekdoq`h
kr'isewc
ka`i
pur`oc
vz~hloc
>esj'iein
m'ellontoc
to`uc
<upenant'iouc\bibvsend
\vs Heb 10:28
>ajet'hsac
tic
n'omon
mw\r{s}'ewc
\fn{\src{T|K}: mwsewc, \src{M|V}: mwusewc.}
qwr`ic
o>iktirm~w\r{n}
\fn{\src{TMKVN}: oiktirmwn, \src{F}: oiktirmwn kai dakruwn.}
>ep`i
dus`in
>`h
tris`in
m'artusin
>apojn'hskei\bibvsend
\vs Heb 10:29
p'osw|
doke~ite
qe'ironoc
>axi\r{w}j'hsetai
\fn{\src{TMKVN}: axiwjhsetai, \src{Pap[46]}: kataxiwjhsetai.}
timwr'iac
<o
t`on
u<i`on
to~u
vjeo~u
katapat'hsac
ka`i
t`o
a<~ima
t~h\r{c}
\fn{\src{TMKVN}: thc, \src{F}: thc kainhc.}
diaj'hkhc
koin`on
<hghs'amenoc
>en\r{}
\fn{\src{TMKVN}: en w hgiasjh, \src{A}: \bibempty.}
<~w|
<hgi'asjh
ka`i
t`o
pne~uma
t~hc
q'aritoc
>enubr'isac\bibvsend
\vs Heb 10:30
o>'idamen
g`ar
t`on
e>ip'onta
>emo`i
>ekd'ikhsic
>eg`w
>antapod'wsw
l'egei\r{}
\fn{\src{TMK}: legei kurioc, \src{V}: \bibempty.}
k'urioc
ka`i
p'alin
k'urioc\r{}
\fn{\src{TMK}: kurioc krinei, \src{V}: krinei kurioc.}
krine~i
t`on
la`on
a>uto~u\bibvsend
\vs Heb 10:31
vfober`on
t`o
>empese~in
e>ic
qe~irac
vjeo~u
vz~wntoc\bibvsend
\vs Heb 10:32
>anamimn'hskesje
d`e
t`ac
pr'oteron
<h\r{m}'erac
\fn{\src{TMKVN}: hmerac, \src{aleph}: amartiac umwn, \src{F}: hmerac umwn.}
>en
a<~ic
vfwtisj'entec
poll`hn
>'ajlhsin
<upeme'inate
pajhm'atwn\bibvsend
\vs Heb 10:33
to~uto
m`en
>oneidismo~ic
te
ka`i
vjl'iyesin
vjea\r{t}riz'omenoi
\fn{\src{TMKVN}: vjeatrizomenoi, \src{F}: oneidizomenoi.}
to~uto
d`e
koinwno`i
t~wn
o<'utwc
>anastrefom'enwn
genhj'entec\bibvsend
\vs Heb 10:34
ka`i
g`ar
to~ic
desmo~ic\r{}
\fn{\src{TMK}: desmoic mou, \src{V}: desmioic.}
mou
sunepaj'hsate
ka`i
t`hn
<arpag`hn
t~wn
<uparq'ontwn
<um~wn
met`a
qar~ac
prosed'exasje
gin'wskontec
>'eqein
>en\r{}
\fn{\src{T|K}: en eautoic, \src{M}: eautoic, \src{V}: eautouc, \src{F}: \bibempty.}
<eauto~ic
kre'ittona
<'uparxin
>en\r{}
\fn{\src{TMK}: en ouranoic, \src{V}: \bibempty.}
o>urano~ic
ka`i
m'enousan\bibvsend
\vs Heb 10:35
m`h
>apob'alhte
o>~un
t`hn
parrhs'ian
<um~wn
<'htic
>'eqei
misjapodos'ian\r{}
\fn{\src{TMK}: misjapodosian megalhn, \src{V}: megalhn misjapodosian.}
meg'alhn\bibvsend
\vs Heb 10:36
<upomon~hc
g`ar
>'eqete
qre'ian
<'ina
t`o
vj'elhma
to~u
vjeo~u
poi'hsantec
kom'ishsje
t`hn
>epaggel'ian\bibvsend
\vs Heb 10:37
>'eti
\r{g}`ar
\fn{\src{TMKVN}: gar, \src{Pap[13]}: \bibempty.}
mikr`on
<'oson
<'oson
<o
>erq'omenoc
<'hxei
ka`i
o>u
qroni\r{e}~i\bibvsend
\fn{\src{TMK}: qroniei, \src{V}: qronisei.}
\vs Heb 10:38
<o
d`e
d'ikaio\r{c}
\fn{\src{TMK}: dikaioc, \src{V}: dikaioc mou.}
>ek
p'istewc
vz'hsetai
ka`i
>e`an
<uposte'ilhtai
o>uk
e>udoke~i
<h
yuq'h
mou
>en
a>ut~w|\bibvsend
\vs Heb 10:39
<hme~ic
d`e
o>uk
>esm`en
<upostol~hc
e>ic
>ap'wleian
>all`a
p'istewc
e>ic
peripo'ihsin
yuq~hc\bibvsend
\vs Heb 11:1
>'estin
d`e
p'istic
>elpizom'enwn
<up'ostasic
pragm'atwn
>'elegqoc
o>u
vblepom'enwn\bibvsend
\vs Heb 11:2
>en
ta'uth|
g`ar
>emartur'hjhsan
o<i
presb'uteroi\bibvsend
\vs Heb 11:3
p'istei
noo~umen
kathrt'isjai
to`uc
a>i~wnac
<r'hmati
vjeo~u
e>ic
t`o
m`h
>ek
vfainom'enwn
t`a\r{}
\fn{\src{TMK}: ta vblepomena, \src{V}: to vblepomenon.}
vblep'omena
gegon'enai\bibvsend
\vs Heb 11:4
p'istei
ple'iona
vjus'ian
>'abel
par`a
k'a"in
pros'hnegken
t~w|\r{}
\fn{\src{TMKVN}: tw vjew, \src{Pap[13]}: \bibempty.}
vje~w|
di>
<~hc
>emartur'hjh
e>~inai
d'ikaioc
marturo~untoc
>ep`i
to~ic
d'wroic
a>uto~u
to~u
vjeo~u
ka`i
di>
a>ut~hc
>apojan`wn
>'eti
lale~i\r{t}ai\bibvsend
\fn{\src{T|M}: laleitai, \src{K|V}: lalei.}
\vs Heb 11:5
p'istei
>en`wq
metet'ejh
to~u
m`h
>ide~in
vj'anaton
ka`i
o>uq
\r{e}<ur'isketo
\fn{\src{TMK}: eurisketo, \src{V}: hurisketo.}
di'oti
met'ejhken
a>ut`on
<o
vje`oc
pr`o
g`ar
t~hc
metaj'esewc
a>u\r{t}o~u
\fn{\src{TMK}: autou, \src{V}: \bibempty.}
memart'urhtai
e>u\r{h}resthk'enai
\fn{\src{TMK}: euhresthkenai, \src{V}: euaresthkenai.}
t~w|
vje~w|\bibvsend
\vs Heb 11:6
qwr`ic
d`e
p'istewc
>ad'unaton
e>uarest~hsai
piste~usai
g`ar
de~i
t`on
proserq'omenon
\r{t}~w|
\fn{\src{TMKVN}: tw, \src{aleph}: \bibempty.}
vje~w|
<'oti
>'estin
ka`i
to~ic
>e\r{k}zhto~usin
\fn{\src{TMKVN}: ekzhtousin, \src{Pap[13]}: vzhtousin.}
a>ut`on
misjapod'othc
g'inetai\bibvsend
\vs Heb 11:7
p'istei
qrhmatisje`ic
n~we
per`i
t~wn
mhd'epw
vblepom'enwn
e>ulabhje`ic
kateske'uasen
kibwt`on
e>ic
swthr'ian
to~u
o>'ikou
a>uto~u
di>
<~hc
kat'ekrinen
t`on
k'osmon
ka`i
t~hc
kat`a
p'istin
dikaios'unhc
>eg'eneto
klhron'omoc\bibvsend
\vs Heb 11:8
p'istei
\r{k}alo'umenoc
\fn{\src{TMKVN}: kaloumenoc, \src{A}: o kaloumenoc.}
>abra`am
<up'hkousen
>exelje~in
e>ic
\r{t}`on
\fn{\src{TMK}: ton, \src{V}: \bibempty.}
t'opon
<`on
>'hmellen
lamb'anein
e>ic
klhronom'ian
ka`i
>ex~hljen
m`h
>epist'amenoc
po~u
>'erqetai\bibvsend
\vs Heb 11:9
p'istei
par'w|khsen
e>ic
\r{t}`hn
\fn{\src{T|K}: thn, \src{M|V}: \bibempty.}
g~hn
t~hc
>epaggel'iac
<wc
>allotr'ian
>en
skhna~ic
katoik'hsac
met`a
>isa`ak
ka`i
>iak`wb
t~wn
sugklhron'omwn
t~hc
>epaggel'iac
t~hc
a>ut~hc\bibvsend
\vs Heb 11:10
>exed'eqeto
g`ar
t`hn
to`uc
vjemel'iouc
>'eqousan
p'olin
<~hc
teqn'ithc
ka`i
dhmiourg`oc
<o
vje'oc\bibvsend
\vs Heb 11:11
p'istei
ka`i
a>ut`h
s'arr\r{a}
\fn{\src{TMK}: sarra, \src{V}: sarra steira.}
d'unamin
e>ic
katabol`hn
sp'ermatoc
>'elabe\r{n}
\fn{\src{TMKVN}: elaben, \src{F}: elaben eic to teknwsai.}
ka`i
par`a
kair`on
<hlik'iac
>'e\r{t}eken
\fn{\src{TMK}: eteken, \src{V}: \bibempty.}
>epe`i
pist`on
<hg'hsato
t`on
>epaggeil'amenon\bibvsend
\vs Heb 11:12
di`o
ka`i
>af>
<en`oc
>egen\r{n}'hjhsan
\fn{\src{TMKVN}: egennhjhsan, \src{A}: egenhjhsan.}
ka`i
ta~uta
nenekrwm'enou
kaj`wc
t`a
>'astra
to~u
o>urano~u
t~w|
pl'hjei
ka`i
<ws\r{e}`i
\fn{\src{T|K}: wsei, \src{M|V}: wc h.}
>'ammoc
<h\r{}
\fn{\src{TMKVN}: h para to qeiloc, \src{Pap[46]}: \bibempty.}
par`a
t`o
qe~iloc
t~hc
vjal'asshc
<h
>anar'ijmhtoc\bibvsend
\vs Heb 11:13
kat`a
p'istin
>ap'ejanon
o<~utoi
p'antec
m`h
lab'ontec
t`ac
>epaggel'iac
>all`a
p'orrwjen
a>ut`ac
>id'ontec
ka`i
peisj'entec\r{}
\fn{\src{T|K}: peisjentec kai, \src{M|V}: \bibempty.}
ka`i
>aspas'amenoi
ka`i
<omolog'hsantec
<'oti
x'enoi
ka`i
parep'idhmo'i
e>isin
>ep`i
t~hc
g~hc\bibvsend
\vs Heb 11:14
o<i
g`ar
toia~uta
l'egontec
>emfan'izousin
<'oti
patr'ida
>e\r{p}izhto~usin\bibvsend
\fn{\src{TMKVN}: epizhtousin, \src{Pap[46]}: vzhtousin.}
\vs Heb 11:15
ka`i
e>i
m`en
>eke'inhc
>e\r{m}nhm'oneuon
\fn{\src{TMKVN}: emnhmoneuon, \src{aleph}: mnhmoneuousin, \src{F}:  emnhmoneusan.}
>af>
<~hc
>ex~hlj\r{o}n
\fn{\src{TMK}: exhljon, \src{V}: exebhsan.}
e>~iqon
>`an
kair`on
>anak'amyai\bibvsend
\vs Heb 11:16
nu\r{n}`i
\fn{\src{T|K}: nuni, \src{M|V}: nun.}
d`e
kre'ittonoc
>or'egontai
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
>epouran'iou
di`o
o>uk
>epaisq'unetai
a>uto`uc
<o
vje`oc
vje`oc
>epikale~isjai
a>ut~wn
<hto'imasen
g`ar
a>uto~ic
p'olin\bibvsend
\vs Heb 11:17
p'istei
prosen'hnoqen
>abra`am
t`on
>isa`ak
peiraz'omenoc
ka`i
t`on
monogen~h
pros'eferen
<o
t`ac
>epaggel'iac
>anadex'amenoc\bibvsend
\vs Heb 11:18
pr`oc
<`on
>elal'hjh
<'oti
>en
>isa`ak
klhj'hseta'i
soi
sp'erma\bibvsend
\vs Heb 11:19
logis'amenoc
<'oti
ka`i
>ek
nekr~wn
>ege'irein
dunat`oc
<o
vje`oc
<'ojen
a>ut`on
ka`i
>en
parabol~h|
>ekom'isato\bibvsend
\vs Heb 11:20
p'istei
\r{p}er`i
\fn{\src{TMK}: peri, \src{V}: kai peri.}
mell'ontwn
e>ul'oghsen
>isa`ak
t`on
>iak`wb
ka`i
t`on
>hsa~u\bibvsend
\vs Heb 11:21
p'istei
>iak`wb
>apojn'hskwn
<'ekaston
t~wn
u<i~wn
>iws`hf
e>ul'oghsen
ka`i
prosek'unhsen
>ep`i
t`o
>'akron
t~hc
<r'abdou
a>uto~u\bibvsend
\vs Heb 11:22
p'istei
>iws`hf
teleut~wn
per`i
t~hc
>ex'odou
t~wn
u<i~wn
>isra`hl
>emnhm'oneusen
ka`i
per`i
t~wn
>ost'ewn
a>uto~u
>enete'ilato\bibvsend
\vs Heb 11:23
p'istei
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
gennhje`ic
>ekr'ubh
tr'imhnon
<up`o
t~wn
pat'erwn
a>uto~u
di'oti
e>~idon
>aste~ion
t`o
paid'ion
ka`i
o>uk
>efob'hjhsan
t`o
di'a\r{t}agma
\fn{\src{TMKVN}: diatagma, \src{F}: dogma.}
to~u
vbasil'ew\r{c}\bibvsend
\fn{\src{TMKVN}: vbasilewc, \src{F}: vbasilewc pistei megac genomenoc mwushc aneilen ton aiguption katanown thn tapeinwsin twn adelfwn autou.}
\vs Heb 11:24
p'istei
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
m'egac
gen'omenoc
>hrn'hsato
l'egesjai
u<i`oc
vjugatr`oc
vfara'w\bibvsend
\vs Heb 11:25
m~allon
<el'omenoc
sugkakouqe~isjai
t~w|
la~w|
to~u
vjeo~u
>`h
pr'oskairon
>'eqein
<amart'iac
>ap'olausin\bibvsend
\vs Heb 11:26
me'izona
plo~uton
<hghs'amenoc
t~wn
>en\r{}
\fn{\src{T|K}: en aiguptw, \src{M|V}: aiguptou.}
a>ig'uptw|
vjhsaur~wn
t`on
>oneidism`on
to~u
qristo~u
>ap'eblepen
g`ar
e>ic
t`hn
misjapodos'ian\bibvsend
\vs Heb 11:27
p'istei
kat'elipen
a>'igupton
m`h
vfobhje`ic
t`on
vjum`on
to~u
vbasil'ewc
t`on
g`ar
>a'oraton
<wc
<or~wn
>ekart'erhsen\bibvsend
\vs Heb 11:28
p'istei
pepo'ihken
t`o
p'asqa
ka`i
t`hn
pr'osqusin
to~u
a<'imatoc
<'ina
m`h
<o
>olojre'uwn
t`a
prwt'otoka
vj'igh|
a>ut~wn\bibvsend
\vs Heb 11:29
p'istei
di'ebhsan
t`hn
>erujr`an
vj'alassan
<wc
di`a
xhr~ac
<~h\r{c}
\fn{\src{TMK}: hc, \src{V}: ghc hc.}
pe~iran
lab'ontec
o<i
a>ig'uptioi
katep'ojhsan\bibvsend
\vs Heb 11:30
p'istei
t`a
te'iqh
<ieriq`w
>'epes\r{e}n
\fn{\src{TMK}: epesen, \src{V}: epesan.}
kuklwj'enta
>ep`i
<ept`a
<hm'erac\bibvsend
\vs Heb 11:31
p'istei
<ra`ab
<h\r{}
\fn{\src{TMKVN}: h, \src{aleph}: h epilegomenh.}
p'ornh
o>u
sunap'wleto
to~ic
>ap\r{e}ij'hsasin
\fn{\src{TMKVN}: apeijhsasin, \src{Pap[46]}: apisthsasin.}
dexam'enh
to`uc
katask'opouc
met>
e>ir'hnhc\bibvsend
\vs Heb 11:32
ka`i
t'i
>'eti
l'egw
>epile'iyei
g'ar\r{}
\fn{\src{TMK}: gar me, \src{V}: me gar.}
me
dihgo'umenon
<o
qr'onoc
per`i
gede`wn
vbar'ak
te\r{}
\fn{\src{TMK}: te kai, \src{V}: \bibempty.}
ka`i
samy`wn
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: \bibempty.}
>iefj'ae
da\r{b}'id
\fn{\src{TMK}: dabid, \src{V}: dauid.}
te
ka`i
samou`hl
ka`i
t~wn
profht~wn\bibvsend
\vs Heb 11:33
o<`i
di`a
p'istewc
kathgwn'isanto
vbasile'i\r{a}c
\fn{\src{TMKVN}: vbasileiac, \src{Pap[46]}: vbasileic.}
e>irg'asanto
dikaios'unhn
>ep'etuqon
>epaggeli~wn
>'efraxan
st'omata
le'ontwn\bibvsend
\vs Heb 11:34
>'esbesan
d'unamin
pur`oc
>'efugon
st'omata
maqa'irac\r{}
\fn{\src{TMK}: maqairac enedunamwjhsan, \src{V}: maqairhc edunamwjhsan.}
>enedunam'wjhsan
>ap`o
>asjene'iac
>egen'hjhsan
>isquro`i
>en
pol'emw|
parembol`ac
>'eklinan
>allotr'iwn\bibvsend
\vs Heb 11:35
>'elabon
guna~ikec
>ex
>anast'asewc
to`uc
nekro`uc
a>ut~wn
>'alloi
d`e
>etumpan'isjhsan
o>u
prosdex'amenoi
t`hn
>apol'utrwsin
<'ina
kre'ittonoc
>anast'asewc
t'uqwsin\bibvsend
\vs Heb 11:36
<'eteroi
d`e
>empaigm~wn
ka`i
mast'igwn
pe~iran
>'elabon
>'eti
d`e
desm~wn
ka`i
vfulak~hc\bibvsend
\vs Heb 11:37
>elij'asjhsan
>epr'isjhsan
>epei\r{r}'asjhsan
\fn{\src{TMK}: epeirasjhsan, \src{V}: \bibempty.}
>en
vf'onw|
maqa'ir\r{a}c
\fn{\src{TMK}: maqairac, \src{V}: maqairhc.}
>ap'ejanon
peri~hljon
>en
mhlwta~ic
>en
a>ige'ioic
d'ermasin
<ustero'umenoi
vjlib'omenoi
kakouqo'umenoi\bibvsend
\vs Heb 11:38
<~wn
o>uk
>~hn
>'axioc
<o
k'osmoc
>e\r{n}
\fn{\src{TMK}: en, \src{V}: epi.}
>erhm'iaic
plan'wmenoi
ka`i
>'oresin
ka`i
sphla'ioic
ka`i
ta~ic
>opa~ic
t~hc
g~hc\bibvsend
\vs Heb 11:39
ka`i
o<~u\r{t}oi
\fn{\src{TMKVN}: outoi, \src{Pap[46]}: \bibempty.}
p'antec
marturhj'entec
di`a
t~hc
p'istewc
o>uk
>ekom'isanto
t`hn
>epaggel'ian\bibvsend
\vs Heb 11:40
to~u
vjeo~u
per`i
<hm~wn
kre~itt'on
ti
probleyam'enou
<'ina
m`h
qwr`ic
<hm~wn
teleiwj~wsin\bibvsend
\vs Heb 12:1
toigaro~un
ka`i
<hme~ic
to\r{s}o~uton
\fn{\src{TMKVN}: tosouton, \src{aleph}: thlikouton.}
>'eqontec
perike'imenon
<hm~in
n'efoc
mart'urwn
>'ogkon
>apoj'emenoi
p'anta
ka`i
t`hn
e>uper'is\r{t}aton
\fn{\src{TMKVN}: euperistaton, \src{Pap[46]}: euperispaston.}
<amart'ian
di>
<upomon~hc
tr'eqwmen
t`on
proke'imenon
<hm~in
>ag~wna\bibvsend
\vs Heb 12:2
>afor~wntec
e>ic
t`on
t~hc
p'istewc
>arqhg`on
ka`i
teleiwt`hn
>ihso~un
<`oc
>ant`i
t~hc
prokeim'enhc
a>ut~w|
qar~ac
<up'emeinen
\r{s}taur`on
\fn{\src{TMKVN}: stauron, \src{Pap[46]}: ton stauron.}
a>isq'unhc
katafron'hsac
>en
dexi~a|
te
to~u
vjr'onou
to~u
vjeo~u
\r{e}k'ajisen\bibvsend
\fn{\src{T|K}: ekajisen, \src{M|V}: kekajiken.}
\vs Heb 12:3
>analog'isasje
g`ar
t`on
toia'uthn
<upomemenhk'ota
<up`o
t~wn
<amartwl~wn
e>ic
\r{a}>ut`on
\fn{\src{TMK}: auton, \src{V}: eauton.}
>antilog'ian
<'ina
m`h
k'amhte
ta~ic
yuqa~ic
<um~wn
>ekl\r{u}'omenoi\bibvsend
\fn{\src{TMKVN}: ekluomenoi, \src{Pap[13]}: eklelumenoi, \src{Pap[46]}: eglelumenoi.}
\vs Heb 12:4
o>'upw
m'eqric
a<'imatoc
>antikat'esthte
pr`oc
t`hn
<amart'ian
>antagwniz'omenoi\bibvsend
\vs Heb 12:5
ka`i
>ekl'elhsje
t~hc
parakl'hsewc
<'htic
<um~in
<wc
u<io~ic
dial'egetai
u<i'e
mou
m`h
>olig'wrei
paide'iac
kur'iou
mhd`e
>ekl'uou
<up>
a>uto~u
>elegq'omenoc\bibvsend
\vs Heb 12:6
<`on
g`ar
>agap~a|
k'urioc
paide'uei
mastigo~i
d`e
p'anta
u<i`on
<`on
parad'eqetai\bibvsend
\vs Heb 12:7
\r{e}>i
\fn{\src{T|K}: ei, \src{M|V}: eic.}
paide'ian
<upom'enete
<wc
u<io~ic
<um~in
prosf'eretai
<o
vje`oc
t'ic
g'ar
>estin\r{}
\fn{\src{TMK}: estin uioc, \src{V}: uioc.}
u<i`oc
<`on
o>u
paide'uei
pat'hr\bibvsend
\vs Heb 12:8
e>i
d`e
qwr'ic
>este
paide'iac
<~hc
m'etoqoi
geg'onasin
p'antec
>'ara
n'ojoi
>este\r{}
\fn{\src{TMK}: este kai ouq uioi, \src{V}: kai ouq uioi este.}
ka`i
o>uq
u<io'i\bibvsend
\vs Heb 12:9
e>~ita
to`uc
m`en
t~hc
sark`oc
<hm~wn
pat'erac
e>'iqomen
paideut`ac
ka`i
>enetrep'omeja
o>u
p\r{o}ll~w|
\fn{\src{TMK}: pollw, \src{V}: polu [de].}
m~allon
<upotaghs'omeja
t~w|
patr`i
t~wn
pneum'at\r{w}n
\fn{\src{TMKVN}: pneumatwn, \src{F}: pneumatikwn, \src{F}: paterwn.}
ka`i
vz'hsomen\bibvsend
\vs Heb 12:10
o<i
m`en
g`ar
pr`oc
>ol'igac
<hm'erac
kat`a
t`o
doko~un
a>uto~ic
>epa'ideuon
<o
d`e
>ep`i
t`o
sumf'eron
e>ic
t`o
metalabe~in
t~hc
<agi'othtoc
a>uto~u\bibvsend
\vs Heb 12:11
p~asa
d`e
paide'ia
pr`oc
m`en
t`o
par`on
o>u
doke~i
qar~ac
e>~inai
>all`a
l'uphc
<'usteron
d`e
karp`on
e>irhnik`on
to~ic
di>
a>ut~hc
gegumnasm'enoic
>apod'idwsin
dikaios'unhc\bibvsend
\vs Heb 12:12
di`o
t`ac
pareim'enac
qe~irac
ka`i
t`a
paralelum'ena
g'onata
>anorj'wsate\bibvsend
\vs Heb 12:13
ka`i
troqi`ac
>orj`ac
poi'h\r{s}ate
\fn{\src{TMK}: poihsate, \src{V}: poieite.}
to~ic
pos`in
<um~wn
<'ina
m`h
t`o
qwl`on
>ektrap~h|
>iaj~h|
d`e
m~allon\bibvsend
\vs Heb 12:14
e>ir'hnhn
di'wkete
met`a
p'antwn
ka`i
t`on
<agiasm`on
o<~u
qwr`ic
o>ude`ic
>'oyetai
t`on
k'urion\bibvsend
\vs Heb 12:15
>episkopo~untec
m'h
tic
<uster~wn
>ap`o
t~hc
q'aritoc
to~u
vjeo~u
m'h
tic
<r'iza
pikr'iac
>'anw
vf'uousa
>enoql~h|
ka`i
di`a\r{}
\fn{\src{TMK}: dia tauthc, \src{V}: di authc.}
ta'uthc
mianj~wsin
pollo'i\bibvsend
\vs Heb 12:16
m'h
tic
p'ornoc
>`h
vb'ebhloc
<wc
>hsa~u
<`oc
>ant`i
vbr'wsewc
mi~ac
>ap'ed\r{o}to
\fn{\src{TMK}: apedoto, \src{V}: apedeto.}
t`a
prwtot'okia
\r{a}>uto~u\bibvsend
\fn{\src{TMK}: autou, \src{V}: eautou.}
\vs Heb 12:17
>'iste
g`ar
<'oti
ka`i
met'epeita
vj'elwn
klhronom~hsai
t`hn
e>ulog'ian
>apedokim'asjh
metano'iac
g`ar
t'opon
o>uq
e<~uren
ka'iper
met`a
dakr'uwn
>ekzht'hsac
a>ut'hn\bibvsend
\vs Heb 12:18
o>u
g`ar
proselhl'ujate
yhlafwm'enw|
>'o\r{r}ei
\fn{\src{TMK}: orei, \src{V}: \bibempty.}
ka`i
kekaum'enw|
pur`i
ka`i
gn'ofw|
ka`i
\r{s}k'otw|
\fn{\src{TMK}: skotw, \src{V}: vzofw.}
ka`i
vju'ellh|\bibvsend
\vs Heb 12:19
ka`i
s'alpiggoc
>'hqw|
ka`i
vfwn~h|
<rhm'atwn
<~hc
o<i
>ako'usantec
parh|t'hsanto
m`h
prostej~hnai
a>uto~ic
l'ogon\bibvsend
\vs Heb 12:20
o>uk
>'eferon
g`ar
t`o
diastell'omenon
k>`an
vjhr'ion
vj'igh|
to~u
>'orouc
lijobolhj'hsetai
>`h\r{}
\fn{\src{T|K}: h vbolidi katatoxeujhsetai, \src{M|V}: \bibempty.}
vbol'idi
katatoxeuj'hsetai\bibvsend
\vs Heb 12:21
ka`i
o<'utwc
vfober`on
>~hn
t`o
vfantaz'omenon
mw\r{s}~hc
\fn{\src{T|K}: mwshc, \src{M|V}: mwushc.}
e>~ipen
>'ekfob'oc
e>imi
ka`i
>'entromoc\bibvsend
\vs Heb 12:22
>all`a
proselhl'ujate
si`wn
>'orei
ka`i
p'olei
vjeo~u
vz~wntoc
<ierousal`hm
>epouran'iw|
ka`i
muri'asin
>agg'elwn\bibvsend
\vs Heb 12:23
panhg'urei
ka`i
>ekklhs'ia|
prwtot'okwn
>en\r{}
\fn{\src{TMK}: en ouranoic apogegrammenwn, \src{V}: apogegrammenwn en ouranoic.}
o>urano~ic
>apogegramm'enwn
ka`i
krit~h|
vje~w|
p'antwn
ka`i
pne'umasin
dika'iwn
teteleiwm'enwn\bibvsend
\vs Heb 12:24
ka`i
diaj'hkhc
n'eac
mes'ith|
>ihso~u
ka`i
a<'imati
<rantismo~u
kre'itton\r{a}
\fn{\src{T|K}: kreittona, \src{M|V}: kreitton.}
lalo~unti
par`a
t`o\r{n}
\fn{\src{T|V}: ton, \src{M|K}: to.}
>'abel\bibvsend
\vs Heb 12:25
vbl'epete
m`h
parait'hshsje
t`on
lalo~unta
e>i
g`ar
>eke~inoi
o>uk
>'efugon\r{}
\fn{\src{T|K}: efugon ton epi thc, \src{M}: efugon ton epi, \src{V}: exefugon epi.}
t`on
>ep`i
t~hc
g~hc
paraiths'amenoi
qrhmat'izonta\r{}
\fn{\src{TMK}: qrhmatizonta pollw, \src{V}: ton qrhmatizonta polu.}
poll~w|
m~allon
<hme~ic
o<i
t`on
>ap>
o>uran~wn
>apostref'omenoi\bibvsend
\vs Heb 12:26
o<~u
<h
vfwn`h
t`hn
g~hn
>es'aleusen
t'ote
n~un
d`e
>ep'hggeltai
l'egwn
>'eti
<'apax
>eg`w
se'i\r{w}
\fn{\src{TMK}: seiw, \src{V}: seisw.}
o>u
m'onon
t`hn
g~hn
>all`a
ka`i
t`on
o>uran'on\bibvsend
\vs Heb 12:27
t`o
d'e
>'eti
<'apax
dhlo~i
t~wn\r{}
\fn{\src{TMK}: twn saleuomenwn thn, \src{V}: [thn] twn saleuomenwn.}
saleuom'enwn
t`hn
met'ajesin
<wc
pepoihm'enwn
<'ina
me'inh|
t`a
m`h
saleu'omena\bibvsend
\vs Heb 12:28
di`o
vbasile'ian
>as'aleuton
paralamb'anontec
>'eqwmen
q'arin
di>
<~hc
latre'u\r{w}men
\fn{\src{T|K|V}: latreuwmen, \src{M}: latreuomen.}
e>uar'estwc
t~w|
vje~w|
met`a
a>ido~uc\r{}
\fn{\src{TMK}: aidouc kai eulabeiac, \src{V}: eulabeiac kai deouc.}
ka`i
e>ulabe'iac\bibvsend
\vs Heb 12:29
ka`i
g`ar
<o
vje`oc
<hm~wn
p~ur
katanal'iskon\bibvsend
\vs Heb 13:1
<h
vfiladelf'ia
men'etw\bibvsend
\vs Heb 13:2
t~hc
vfiloxen'iac
m`h
>epilanj'anesje
di`a
ta'uthc
g`ar
>'elaj'on
tinec
xen'isantec
>agg'elouc\bibvsend
\vs Heb 13:3
mimn'hskesje
t~wn
desm'iwn
<wc
sundedem'enoi
t~wn
kakouqoum'enwn
<wc
ka`i
a>uto`i
>'ontec
>en
s'wmati\bibvsend
\vs Heb 13:4
t'imioc
<o
g'amoc
>en
p~asin
ka`i
<h
ko'ith
>am'iantoc
p'ornouc
d`e\r{}
\fn{\src{TMK}: de, \src{V}: gar.}
ka`i
moiqo`uc
krine~i
<o
vje'oc\bibvsend
\vs Heb 13:5
>afil'arguroc
<o
tr'opoc
>arko'umen\r{o}i
\fn{\src{TMKVN}: arkoumenoi, \src{Pap[46c]}: arkoumenoc.}
to~ic
paro~usin
a>ut`oc
g`ar
e>'irhken
o>u
m'h
se
>an~w
o>ud>
o>u
m'h
se
>egkatal'i\r{p}w\bibvsend
\fn{\src{T|K|V}: egkatalipw, \src{M}: egkataleipw.}
\vs Heb 13:6
<'wste
vjarro~untac
<hm~ac
l'egein
k'urioc
>emo`i
vbohj`oc
k\r{a}`i
\fn{\src{TMK}: kai, \src{V}: [kai], \src{aleph}: \bibempty.}
o>u
vfobhj'hsomai
t'i
poi'hsei
moi
>'anjrwpoc\bibvsend
\vs Heb 13:7
mnhmone'uete
t~wn
<hgoum'enwn
<um~wn
o<'itinec
>el'alhsan
<um~in
t`on
l'ogon
to~u
vjeo~u
<~wn
>anajewro~untec
t`hn
>'ekbasin
t~hc
>anastrof~hc
mime~isje
t`hn
p'istin\bibvsend
\vs Heb 13:8
>ihso~uc
qrist`oc
\r{q}j`ec
\fn{\src{TMK}: qjec, \src{V}: eqjec.}
ka`i
s'hmeron
<o
a>ut`oc
ka`i
e>ic
to`uc
a>i~wna\r{c}\bibvsend
\fn{\src{TMKVN}: aiwnac, \src{F}: aiwnac amhn.}
\vs Heb 13:9
didaqa~ic
poik'ilaic
ka`i
x'enaic
m`h
p\r{e}rif'eresje
\fn{\src{T|K}: periferesje, \src{M|V}: paraferesje.}
kal`on
g`ar
q'ariti
vbebaio~usjai
t`hn
kard'ian
o>u
vbr'wmasin
>en
o<~ic
o>uk
>wfel'hjhsan
o<i
peripat'h\r{s}antec\bibvsend
\fn{\src{TMK}: peripathsantec, \src{V}: peripatountec.}
\vs Heb 13:10
>'eqomen
vjusiast'hrion
>ex
o<~u
vfage~in
o>uk
>'eqousin
>exo\r{u}s'ian
\fn{\src{TMKVN}: exousian, \src{F}: \bibempty.}
o<i
t~h|
skhn~h|
latre'uontec\bibvsend
\vs Heb 13:11
<~wn
g`ar
e>isf'eretai
vz'wwn
t`o
a<~ima
per`i
<amart'iac
e>ic
t`a
<'agia
di`a
to~u
>arqier'ewc
to'utwn
t`a
s'wmata
kataka'ietai
>'exw
t~hc
parembol~hc\bibvsend
\vs Heb 13:12
di`o
ka`i
>ihso~uc
<'ina
<agi'ash|
di`a
to~u
>id'iou
a<'imatoc
t`on
la`on
>'exw
t~hc
\r{p}'ulhc
\fn{\src{TMKVN}: pulhc, \src{Pap[46]}: parembolhc.}
>'epajen\bibvsend
\vs Heb 13:13
to'inun
>exerq'wmeja
pr`oc
a>ut`on
>'exw
t~hc
parembol~hc
t`on
>oneidism`on
a>uto~u
vf'erontec\bibvsend
\vs Heb 13:14
o>u
g`ar
>'eqomen
<~wde
m'enousan
p'olin
>all`a
t`hn
m'ellousan
>epizhto~umen\bibvsend
\vs Heb 13:15
di>
a>uto~u
\r{o}>~un
\fn{\src{TMK}: oun, \src{V}: [oun], \src{aleph|Pap[46]}: \bibempty.}
>anaf'erwmen
vjus'ian
a>in'esewc
dia\r{p}ant`oc
\fn{\src{T}: diapantoc, \src{K|M|V}: dia pantoc.}
t~w|
vje~w|
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
karp`on
qeil'ewn
<omologo'untwn
t~w|
>on'omati
a>uto~u\bibvsend
\vs Heb 13:16
t~hc
d`e
e>upoi"'iac
k\r{a}`i
\fn{\src{TMKVN}: kai, \src{Pap[46]}: kai thc.}
koinwn'iac
m`h
>epilanj'anesje
toia'utaic
g`ar
vjus'iaic
e>uareste~itai
<o
vje'oc\bibvsend
\vs Heb 13:17
pe'ijesje
to~ic
<hgoum'enoic
<um~wn
ka`i
<upe'ikete
a>uto`i
g`ar
>agrupno~usin
<up`er
t~wn
yuq~wn
<um~wn
<wc
l'ogon
>apod'wsonte\r{c}
\fn{\src{TMKVN}: apodwsontec, \src{F}: apodwsontai peri umwn.}
<'ina
met`a
qar~ac
to~uto
poi~wsin
ka`i
m`h
sten'azontec
>alusitel`ec
g`ar
<um~in
to~uto\bibvsend
\vs Heb 13:18
prose'uqesje
\r{p}er`i
\fn{\src{TMKVN}: peri, \src{F}: kai peri.}
<hm~wn
pe\r{p}o'ijamen
\fn{\src{TMK}: pepoijamen, \src{V}: peijomeja.}
g`ar
<'oti
kal`hn
sune'idhsin
>'eqomen
>en
p~asin
kal~wc
vj'elontec
>anastr'efesjai\bibvsend
\vs Heb 13:19
perissot'erwc
d`e
parakal~w
to~uto
poi~hsai
<'ina
t'aqion
>apokatastaj~w
<um~in\bibvsend
\vs Heb 13:20
<o
d`e
vje`oc
t~hc
e>ir'hnhc
<o
>anagag`wn
>ek
nekr~wn
t`on
poim'ena
t~wn
prob'atwn
t`on
m'egan
>en
a<'imati
diaj'hkhc
a>iwn'iou
t`on
k'urion
<hm~wn
>ihso~u\r{n}\bibvsend
\fn{\src{TMKVN}: ihsoun, \src{F}: ihsoun qriston.}
\vs Heb 13:21
katart'isai
<um~ac
>en
pant`i
>'e\r{r}gw|
\fn{\src{TMK}: ergw, \src{V}: \bibempty.}
>agaj~w|
e>ic
t`o
poi~hsai
t`o
vj'elhma
a>uto~u
\r{p}oi~wn
\fn{\src{TMKVN}: poiwn, \src{aleph|A}: autw poiwn, \src{Pap[46]}: auto poiwn, \src{F}: autoc poiwn.}
>en
<u\r{m}~in
\fn{\src{TMK}: umin, \src{V}: hmin.}
t`o
e>u'areston
>en'wpion
a>uto~u
di`a
>ihso~u
qristo~u
<~w|
<h
d'oxa
e>ic
to`uc
a>i~wnac
t~wn\r{}
\fn{\src{TMK}: twn aiwnwn, \src{V}: [twn aiwnwn], \src{Pap[46]}: \bibempty.}
a>i'wnwn
>am'hn\bibvsend
\vs Heb 13:22
parakal~w
d`e
<um~ac
>adelfo`i
>an'eqesj\r{e}
\fn{\src{TMKVN}: aneqesje, \src{F}: aneqesjai.}
to~u
l'ogou
t~hc
parakl'hsewc
ka`i
g`ar
di`a
vbraq'ewn
>ep'esteila
<um~in\bibvsend
\vs Heb 13:23
gin'wskete
t`on
>adelf`o\r{n}
\fn{\src{TMK}: adelfon, \src{V}: adelfon hmwn.}
tim'ojeon
>apolelum'enon
mej>
o<~u
>e`an
t'aqion
>'erqhtai
>'oyomai
<um~ac\bibvsend
\vs Heb 13:24
>asp'asasje
\r{p}'antac
\fn{\src{TMKVN}: pantac, \src{Pap[46]}: \bibempty.}
to`uc
<hgoum'enouc
<um~wn
ka`i
p'antac
to`uc
<ag'iouc
>asp'azontai
<um~ac
o<i
>ap`o
t~hc
>ital'iac\bibvsend
\vs Heb 13:25
<h
q'aric
met`a
p'antwn
<u\r{m}~wn
\fn{\src{TMKVN}: umwn, \src{F}: twn agiwn.}
>a\r{m}'hn\bibvsend
\fn{\src{TMK}: amhn, \src{V}: \bibempty.}
Pr`oc\r{}
\fn{\src{T}: Proc \ldots\ timojeou, \src{K|M|V}: \bibempty.}
<ebra'iouc
>egr'afh
>ap`o
t~hc
>ital'iac
di`a
timoj'eou\bibvsend
