\bibbook{H PROS TOUS FILIPPHSIOUS\\\LARGE EPISTOLH\r{}}{PROS FILIPPHSIOUS}{Philippians}{Phi}[PROS FILIPPHSIOUS]
\vs Phi 1:1
pa~uloc
\fnt{\src{T}: H PROS TOUS FILIPPHSIOUS EPISTOLH, \src{K}: PAULOU TOU APOSTOLOU H PROS FILIPPHSIOUS EPISTOLH, \src{M|V}: PROS FILIPPHSIOUS.}
ka`i
tim'ojeoc
do~uloi
>ihso~u\r{}
\fn{\src{TMK}: ihsou qristou, \src{V}: qristou ihsou.}
qristo~u
p~asin
to~ic
<ag'ioic
>en
qrist~w|
>ihso~u
to~ic
o>~usin
>en
vfil'ippoic
s`un
>episk'opoic
ka`i
diak'onoic\bibvsend
\vs Phi 1:2
q'aric
<um~in
ka`i
e>ir'hnh
>ap`o
vjeo~u
patr`oc
<hm~wn
ka`i
kur'iou
>ihso~u
qristo~u\bibvsend
\vs Phi 1:3
e>uqarist~w
t~w|
vje~w|
mou
>ep`i
p'ash|
t~h|
mne'ia|
<um~wn\bibvsend
\vs Phi 1:4
p'antote
>en
p'ash|
de'hsei
mou
<up`er
p'antwn
<um~wn
met`a
qar~ac
t`hn
d'ehsin
poio'umenoc\bibvsend
\vs Phi 1:5
>ep`i
t~h|
koinwn'ia|
<um~wn
e>ic
t`o
e>uagg'elion
>a\r{p}`o
\fn{\src{TMK}: apo, \src{V}: apo thc.}
pr'wthc
<hm'erac
>'aqri
to~u
n~un\bibvsend
\vs Phi 1:6
pepoij`wc
a>ut`o
to~uto
<'oti
<o
>enarx'amenoc
>en
<um~in
>'ergon
>agaj`on
>epitel'esei
>'aqri\r{c}
\fn{\src{TMK}: aqric, \src{V}: aqri.}
<hm'erac
>ihso~u\r{}
\fn{\src{T|K}: ihsou qristou, \src{M|V}: qristou ihsou.}
qristo~u\bibvsend
\vs Phi 1:7
kaj'wc
>estin
d'ikaion
>emo`i
to~uto
vfrone~in
<up`er
p'antwn
<um~wn
di`a
t`o
>'eqein
me
>en
t~h|
kard'ia|
<um~ac
>'en
te
to~ic
desmo~ic
mou
ka`i
\r{t}~h|
\fn{\src{T|K}: th, \src{M|V}: en th.}
>apolog'ia|
ka`i
vbebai'wsei
to~u
e>uaggel'iou
sugkoinwno'uc
mou
t~hc
q'aritoc
p'antac
<um~ac
>'ontac\bibvsend
\vs Phi 1:8
m'artuc
g'ar
mo'u
>e\r{s}tin
\fn{\src{TMK}: estin, \src{V}: \bibempty.}
<o
vje`oc
<wc
>epipoj~w
p'antac
<um~ac
>en
spl'agqnoic
>ihso~u\r{}
\fn{\src{TMK}: ihsou qristou, \src{V}: qristou ihsou.}
qristo~u\bibvsend
\vs Phi 1:9
ka`i
to~uto
prose'uqomai
<'ina
<h
>ag'aph
<um~wn
>'eti
m~allon
ka`i
m~allon
perisse'uh|
>en
>epign'wsei
ka`i
p'ash|
a>isj'hsei\bibvsend
\vs Phi 1:10
e>ic
t`o
dokim'azein
<um~ac
t`a
diaf'eronta
<'ina
>~hte
e>ilikrine~ic
ka`i
>apr'oskopoi
e>ic
<hm'eran
qristo~u\bibvsend
\vs Phi 1:11
peplhrwm'enoi
kar\r{p}~wn
\fn{\src{TMK}: karpwn, \src{V}: karpon.}
dikaios'unhc
\r{t}~wn
\fn{\src{TMK}: twn, \src{V}: ton.}
di`a
>ihso~u
qristo~u
e>ic
d'oxan
ka`i
>'epainon
vjeo~u\bibvsend
\vs Phi 1:12
gin'wskein
d`e
<um~ac
vbo'ulomai
>adelfo`i
<'oti
t`a
kat>
>em`e
m~allon
e>ic
prokop`hn
to~u
e>uaggel'iou
>el'hlujen\bibvsend
\vs Phi 1:13
<'wste
to`uc
desmo'uc
mou
vfanero`uc
>en
qrist~w|
gen'esjai
>en
<'olw|
t~w|
praitwr'iw|
ka`i
to~ic
loipo~ic
p~asin\bibvsend
\vs Phi 1:14
ka`i
to`uc
ple'ionac
t~wn
>adelf~wn
>en
kur'iw|
pepoij'otac
to~ic
desmo~ic
mou
perissot'erwc
tolm~a|n
>af'obwc
t`on
l'ogon
lale~in\bibvsend
\vs Phi 1:15
tin`ec
m`en
ka`i
di`a
vfj'onon
ka`i
>'erin
tin`ec
d`e
ka`i
di>
e>udok'ian
t`on
qrist`on
khr'ussousin\bibvsend
\vs Phi 1:16
o<i
m`en
>ex
>erije'iac\r{}
\fn{\src{TMK}: erijeiac ton qriston kataggellousin ouq agnwc oiomenoi vjliyin epiferein toic desmoic mou, \src{V}: agaphc eidotec oti eic apologian tou euaggeliou keimai.}
t`on
qrist`on
katagg'ellousin
o>uq
<agn~wc
o>i'omenoi
vjl'iyin
>epif'erein
to~ic
desmo~ic
mou\bibvsend
\vs Phi 1:17
o<i
d`e
>ex
>ag'aphc\r{}
\fn{\src{TMK}: agaphc eidotec oti eic apologian tou euaggeliou keimai, \src{V}: erijeiac ton qriston kataggellousin ouq agnwc oiomenoi vjliyin egeirein toic desmoic mou.}
e>id'otec
<'oti
e>ic
>apolog'ian
to~u
e>uaggel'iou
ke~imai\bibvsend
\vs Phi 1:18
t'i
g`ar
pl`h\r{n}
\fn{\src{TMK}: plhn, \src{V}: plhn oti.}
pant`i
tr'opw|
e>'ite
prof'asei
e>'ite
>alhje'ia|
qrist`oc
katagg'elletai
ka`i
>en
to'utw|
qa'irw
>all`a
ka`i
qar'hsomai\bibvsend
\vs Phi 1:19
o>~ida
g`ar
<'oti
to~ut'o
moi
>apob'hsetai
e>ic
swthr'ian
di`a
t~hc
<um~wn
de'hsewc
ka`i
>epiqorhg'iac
to~u
pne'umatoc
>ihso~u
qristo~u\bibvsend
\vs Phi 1:20
kat`a
t`hn
>apokaradok'ian
ka`i
>elp'ida
mou
<'oti
>en
o>uden`i
a>isqunj'hsomai
>all>
>en
p'ash|
parrhs'ia|
<wc
p'antote
ka`i
n~un
megalunj'hsetai
qrist`oc
>en
t~w|
s'wmat'i
mou
e>'ite
di`a
vzw~hc
e>'ite
di`a
vjan'atou\bibvsend
\vs Phi 1:21
>emo`i
g`ar
t`o
vz~h|n
qrist`oc
ka`i
t`o
>apojane~in
k'erdoc\bibvsend
\vs Phi 1:22
e>i
d`e
t`o
vz~h|n
>en
sark`i
to~ut'o
moi
karp`oc
>'ergou
ka`i
t'i
a<ir'hsomai
o>u
gnwr'izw\bibvsend
\vs Phi 1:23
sun'eqomai
\r{g}`ar
\fn{\src{T|K}: gar, \src{M|V}: de.}
>ek
t~wn
d'uo
t`hn
>epijum'ian
>'eqwn
e>ic
t`o
>anal~usai
ka`i
s`un
qrist~w|
e>~inai
p\r{o}ll~w|
\fn{\src{TMK}: pollw, \src{V}: pollw [gar].}
m~allon
kre~isson\bibvsend
\vs Phi 1:24
t`o
d`e
>epim'enein
>en
t~h|
sark`i
>anagkai'oteron
di>
<um~ac\bibvsend
\vs Phi 1:25
ka`i
to~uto
pepoij`wc
o>~ida
<'oti
men~w
ka`i
\r{s}umparamen~w
\fn{\src{TMK}: sumparamenw, \src{V}: paramenw.}
p~asin
<um~in
e>ic
t`hn
<um~wn
prokop`hn
ka`i
qar`an
t~hc
p'istewc\bibvsend
\vs Phi 1:26
<'ina
t`o
ka'uqhma
<um~wn
perisse'uh|
>en
qrist~w|
>ihso~u
>en
>emo`i
di`a
t~hc
>em~hc
parous'iac
p'alin
pr`oc
<um~ac\bibvsend
\vs Phi 1:27
m'onon
>ax'iwc
to~u
e>uaggel'iou
to~u
qristo~u
polite'uesje
<'ina
e>'ite
>elj`wn
ka`i
>id`wn
<um~ac
e>'ite
>ap`wn
>ako'u\r{s}w
\fn{\src{TMK}: akousw, \src{V}: akouw.}
t`a
per`i
<um~wn
<'oti
st'hkete
>en
<en`i
pne'umati
mi~a|
yuq~h|
sunajlo~untec
t~h|
p'istei
to~u
e>uaggel'iou\bibvsend
\vs Phi 1:28
ka`i
m`h
ptur'omenoi
>en
mhden`i
<up`o
t~wn
>antikeim'enwn
<'htic
a>uto~ic\r{}
\fn{\src{TMK}: autoic men estin endeixic apwleiac umin, \src{V}: estin autoic endeixic apwleiac umwn.}
m'en
>estin
>'endeixic
>apwle'iac
<um~in
d`e
swthr'iac
ka`i
to~uto
>ap`o
vjeo~u\bibvsend
\vs Phi 1:29
<'oti
<um~in
>eqar'isjh
t`o
<up`er
qristo~u
o>u
m'onon
t`o
e>ic
a>ut`on
piste'uein
>all`a
ka`i
t`o
<up`er
a>uto~u
p'asqein\bibvsend
\vs Phi 1:30
t`on
a>ut`on
>ag~wna
>'eqontec
o<~ion
>'id\r{e}te
\fn{\src{T}: idete, \src{K|M|V}: eidete.}
>en
>emo`i
ka`i
n~un
>ako'uete
>en
>emo'i\bibvsend
\vs Phi 2:1
e>'i
tic
o>~un
par'aklhsic
>en
qrist~w|
e>'i
ti
param'ujion
>ag'aphc
e>'i
tic
koinwn'ia
pne'umatoc
e>'i
ti\r{n}a
\fn{\src{T|K}: tina, \src{M|V}: tic.}
spl'agqna
ka`i
o>iktirmo'i\bibvsend
\vs Phi 2:2
plhr'wsat'e
mou
t`hn
qar`an
<'ina
t`o
a>ut`o
vfron~hte
t`hn
a>ut`hn
>ag'aphn
>'eqontec
s'umyuqoi
t`o
<`en
vfrono~untec\bibvsend
\vs Phi 2:3
mhd`en
kat`a\r{}
\fn{\src{TMK}: kata erijeian h, \src{V}: kat erijeian mhde kata.}
>er'ijeian
>`h
kenodox'ian
>all`a
t~h|
tapeinofros'unh|
>all'hlouc
<hgo'umenoi
<uper'eqontac
<eaut~wn\bibvsend
\vs Phi 2:4
m`h
t`a
<eaut~wn
<'ekastoc
skop\r{e}~ite
\fn{\src{TMK}: skopeite, \src{V}: skopountec.}
>all`a
ka`i
t`a
<et'erwn
<'ekasto\r{c}\bibvsend
\fn{\src{TMK}: ekastoc, \src{V}: ekastoi.}
\vs Phi 2:5
to~uto
g`ar\r{}
\fn{\src{TMK}: gar vfroneisjw, \src{V}: vfroneite.}
vfrone'isjw
>en
<um~in
<`o
ka`i
>en
qrist~w|
>ihso~u\bibvsend
\vs Phi 2:6
<`oc
>en
morf~h|
vjeo~u
<up'arqwn
o>uq
<arpagm`on
<hg'hsato
t`o
e>~inai
>~isa
vje~w|\bibvsend
\vs Phi 2:7
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
<eaut`on
>ek'enwsen
morf`hn
do'ulou
lab`wn
>en
<omoi'wmati
>anjr'wpwn
gen'omenoc\bibvsend
\vs Phi 2:8
ka`i
sq'hmati
e<ureje`ic
<wc
>'anjrwpoc
>etape'inwsen
<eaut`on
gen'omenoc
<up'hkooc
m'eqri
vjan'atou
vjan'atou
d`e
stauro~u\bibvsend
\vs Phi 2:9
di`o
ka`i
<o
vje`oc
a>ut`on
<uper'uywsen
ka`i
>eqar'isato
a>ut~w|
>'o\r{n}oma
\fn{\src{TMK}: onoma, \src{V}: to onoma.}
t`o
<up`er
p~an
>'onoma\bibvsend
\vs Phi 2:10
<'ina
>en
t~w|
>on'omati
>ihso~u
p~an
g'onu
k'amyh|
>epouran'iwn
ka`i
>epige'iwn
ka`i
kataqjon'iwn\bibvsend
\vs Phi 2:11
ka`i
p~asa
gl~wssa
>exomolog'hshtai
<'oti
k'urioc
>ihso~uc
qrist`oc
e>ic
d'oxan
vjeo~u
patr'oc\bibvsend
\vs Phi 2:12
<'wste
>agaphto'i
mou
kaj`wc
p'antote
<uphko'usate
m`h
<wc
>en
t~h|
parous'ia|
mou
m'onon
>all`a
n~un
poll~w|
m~allon
>en
t~h|
>apous'ia|
mou
met`a
vf'obou
ka`i
tr'omou
t`hn
<eaut~wn
swthr'ian
katerg'azesje\bibvsend
\vs Phi 2:13
<o\r{}
\fn{\src{TMK}: o, \src{V}: \bibempty.}
vje`oc
g'ar
>estin
<o
>energ~wn
>en
<um~in
ka`i
t`o
vj'elein
ka`i
t`o
>energe~in
<up`er
t~hc
e>udok'iac\bibvsend
\vs Phi 2:14
p'anta
poie~ite
qwr`ic
goggusm~wn
ka`i
dialogism~wn\bibvsend
\vs Phi 2:15
<'ina
g'enhsje
>'amemptoi
ka`i
>ak'eraioi
t'ekna
vjeo~u
>am'wmhta\r{}
\fn{\src{TMK}: amwmhta en mesw, \src{V}: amwma meson.}
>en
m'esw|
gene~ac
skoli~ac
ka`i
diestramm'enhc
>en
o<~ic
vfa'inesje
<wc
vfwst~hrec
>en
k'osmw|\bibvsend
\vs Phi 2:16
l'ogon
vzw~hc
>ep'eqontec
e>ic
ka'uqhma
>emo`i
e>ic
<hm'eran
qristo~u
<'oti
o>uk
e>ic
ken`on
>'edramon
o>ud`e
e>ic
ken`on
>ekop'iasa\bibvsend
\vs Phi 2:17
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
e>i
ka`i
sp'endomai
>ep`i
t~h|
vjus'ia|
ka`i
leitourg'ia|
t~hc
p'istewc
<um~wn
qa'irw
ka`i
sugqa'irw
p~asin
<um~in\bibvsend
\vs Phi 2:18
t`o
\r{d}>
\fn{\src{TMK}: d, \src{V}: de.}
a>ut`o
ka`i
<ume~ic
qa'irete
ka`i
sugqa'iret'e
moi\bibvsend
\vs Phi 2:19
>elp'izw
d`e
>en
kur'iw|
>ihso~u
tim'ojeon
taq'ewc
p'emyai
<um~in
<'ina
k>ag`w
e>uyuq~w
gno`uc
t`a
per`i
<um~wn\bibvsend
\vs Phi 2:20
o>ud'ena
g`ar
>'eqw
>is'oyuqon
<'ostic
gnhs'iwc
t`a
per`i
<um~wn
merimn'hsei\bibvsend
\vs Phi 2:21
o<i
p'antec
g`ar
t`a
<eaut~wn
vzhto~usin
o>u
t`a
to~u\r{}
\fn{\src{T|K}: tou qristou ihsou, \src{M}: qristou ihsou, \src{V}: ihsou qristou.}
qristo~u
>ihso~u\bibvsend
\vs Phi 2:22
t`hn
d`e
dokim`hn
a>uto~u
gin'wskete
<'oti
<wc
patr`i
t'eknon
s`un
>emo`i
>edo'uleusen
e>ic
t`o
e>uagg'elion\bibvsend
\vs Phi 2:23
to~uton
m`en
o>~un
>elp'izw
p'emyai
<wc
>`an
>a\r{p}'idw
\fn{\src{TMK}: apidw, \src{V}: afidw.}
t`a
per`i
>em`e
>exaut~hc\bibvsend
\vs Phi 2:24
p'epoija
d`e
>en
kur'iw|
<'oti
ka`i
a>ut`oc
taq'ewc
>ele'usomai\bibvsend
\vs Phi 2:25
>anagka~ion
d`e
<hghs'amhn
>epafr'oditon
t`on
>adelf`on
ka`i
sunerg`on
ka`i
sustrati'wthn
mou
<um~wn
d`e
>ap'ostolon
ka`i
leitourg`on
t~hc
qre'iac
mou
p'emyai
pr`oc
<um~ac\bibvsend
\vs Phi 2:26
>epeid`h
>epipoj~wn
>~hn
p'antac
<um~ac
ka`i
>adhmon~wn
di'oti
>hko'usate
<'oti
>hsj'enhsen\bibvsend
\vs Phi 2:27
ka`i
g`ar
>hsj'enhsen
parapl'hsion
vjan'atw|
>al\r{l}>
\fn{\src{T|K}: all, \src{M|V}: alla.}
<o
vje`oc
a>ut`on\r{}
\fn{\src{TMK}: auton hlehsen, \src{V}: hlehsen auton.}
>hl'ehsen
o>uk
a>ut`on
d`e
m'onon
>all`a
ka`i
>em`e
<'ina
m`h
l'uphn
>ep`i
l'u\r{p}h|
\fn{\src{T|K}: luph, \src{M|V}: luphn.}
sq~w\bibvsend
\vs Phi 2:28
spoudaiot'erwc
o>~un
>'epemya
a>ut`on
<'ina
>id'ontec
a>ut`on
p'alin
qar~hte
k>ag`w
>alup'oteroc
>~w\bibvsend
\vs Phi 2:29
prosd'eqesje
o>~un
a>ut`on
>en
kur'iw|
met`a
p'ashc
qar~ac
ka`i
to`uc
toio'utouc
>ent'imouc
>'eqete\bibvsend
\vs Phi 2:30
<'oti
di`a
t`o
>'ergon
t\r{o}~u
\fn{\src{TMK}: tou, \src{V}: \bibempty.}
qristo~u
m'eqri
vjan'atou
>'hggisen
parabo\r{u}leus'amenoc
\fn{\src{TMK}: parabouleusamenoc, \src{V}: paraboleusamenoc.}
t~h|
yuq~h|
<'ina
>anaplhr'wsh|
t`o
<um~wn
<ust'erhma
t~hc
pr'oc
me
leitourg'iac\bibvsend
\vs Phi 3:1
t`o
loip`on
>adelfo'i
mou
qa'irete
>en
kur'iw|
t`a
a>ut`a
gr'afein
<um~in
>emo`i
m`en
o>uk
>oknhr`on
<um~in
d`e\r{}
\fn{\src{T|K|V}: de, \src{M}: de to.}
>asfal'ec\bibvsend
\vs Phi 3:2
vbl'epete
to`uc
k'unac
vbl'epete
to`uc
kako`uc
>erg'atac
vbl'epete
t`hn
katatom'hn\bibvsend
\vs Phi 3:3
<hme~ic
g'ar
>esmen
<h
peritom`h
o<i
pne'umati
vj\r{e}~w|
\fn{\src{T|K}: vjew, \src{M|V}: vjeou.}
latre'uontec
ka`i
kauq'wmenoi
>en
qrist~w|
>ihso~u
ka`i
o>uk
>en
sark`i
pepoij'otec\bibvsend
\vs Phi 3:4
ka'iper
>eg`w
>'eqwn
pepo'ijhsin
ka`i
>en
sark`i
e>'i\r{t}ic
\fn{\src{T}: eitic, \src{K|M|V}: ei tic.}
doke~i
>'alloc
pepoij'enai
>en
sark`i
>eg`w
m~allon\bibvsend
\vs Phi 3:5
peritom`h
>okta'hmeroc
>ek
g'enouc
>isra`hl
vful~hc
vbeniam`in
<ebra~ioc
>ex
<ebra'iwn
kat`a
n'omon
vfarisa~ioc\bibvsend
\vs Phi 3:6
kat`a
vz~hlo\r{n}
\fn{\src{TMK}: vzhlon, \src{V}: vzhloc.}
di'wkwn
t`hn
>ekklhs'ian
kat`a
dikaios'unhn
t`hn
>en
n'omw|
gen'omenoc
>'amemptoc\bibvsend
\vs Phi 3:7
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: [alla].}
<'atina
>~hn
moi
k'erdh
ta~uta
<'hghmai
di`a
t`on
qrist`on
vzhm'ian\bibvsend
\vs Phi 3:8
>all`a
meno~un\r{g}e
\fn{\src{T|K|V}: menounge, \src{M}: menoun.}
ka`i
<hgo~umai
p'anta
vzhm'ian
e>~inai
di`a
t`o
<uper'eqon
t~hc
gn'wsewc
qristo~u
>ihso~u
to~u
kur'iou
mou
di>
<`on
t`a
p'anta
>ezhmi'wjhn
ka`i
<hgo~umai
sk'ubala
e>~i\r{n}ai
\fn{\src{TMK}: einai, \src{V}: \bibempty.}
<'ina
qrist`on
kerd'hsw\bibvsend
\vs Phi 3:9
ka`i
e<urej~w
>en
a>ut~w|
m`h
>'eqwn
>em`hn
dikaios'unhn
t`hn
>ek
n'omou
>all`a
t`hn
di`a
p'istewc
qristo~u
t`hn
>ek
vjeo~u
dikaios'unhn
>ep`i
t~h|
p'istei\bibvsend
\vs Phi 3:10
to~u
gn~wnai
a>ut`on
ka`i
t`hn
d'unamin
t~hc
>anast'asewc
a>uto~u
ka`i
t`hn
koinwn'ian
t~wn
pajhm'atwn
a>uto~u
summorf\r{o}'umenoc
\fn{\src{TMK}: summorfoumenoc, \src{V}: summorfizomenoc.}
t~w|
vjan'atw|
a>uto~u\bibvsend
\vs Phi 3:11
e>'i
pwc
katant'hsw
e>ic
t`hn
>exan'astasin
\r{t}~wn
\fn{\src{TMK}: twn, \src{V}: thn ek.}
nekr~wn\bibvsend
\vs Phi 3:12
o>uq
<'oti
>'hdh
>'elabon
>`h
>'hdh
tetele'iwmai
di'wkw
d`e
e>i
ka`i
katal'abw
>ef>
<~w|
ka`i
katel'h\r{f}jhn
\fn{\src{TMK}: katelhfjhn, \src{V}: katelhmfjhn.}
<up`o
t\r{o}~u
\fn{\src{TMK}: tou, \src{V}: \bibempty.}
qristo~u
>ihso~u\bibvsend
\vs Phi 3:13
>adelfo`i
>eg`w
>emaut`on
o>u
log'izomai
kateilhf'enai
<`en
d`e
t`a
m`en
>op'isw
>epilanjan'omenoc
to~ic
d`e
>'emprosjen
>epektein'omenoc\bibvsend
\vs Phi 3:14
kat`a
skop`on
di'wkw
>e\r{p}`i
\fn{\src{TMK}: epi, \src{V}: eic.}
t`o
vbrabe~ion
t~hc
>'anw
kl'hsewc
to~u
vjeo~u
>en
qrist~w|
>ihso~u\bibvsend
\vs Phi 3:15
<'osoi
o>~un
t'eleioi
to~uto
vfron~wmen
ka`i
e>'i
ti
<et'erwc
vfrone~ite
ka`i
to~uto
<o
vje`oc
<um~in
>apokal'uyei\bibvsend
\vs Phi 3:16
pl`hn
e>ic
<`o
>efj'asamen
t~w|
a>ut~w|
stoiqe~in
kan'oni\r{}
\fn{\src{TMK}: kanoni to auto vfronein, \src{V}: \bibempty.}
t`o
a>ut`o
vfrone~in\bibvsend
\vs Phi 3:17
summimhta'i
mou
g'inesje
>adelfo`i
ka`i
skope~ite
to`uc
o<'utwc
peripato~untac
kaj`wc
>'eqete
t'upon
<hm~ac\bibvsend
\vs Phi 3:18
pollo`i
g`ar
peripato~usin
o<`uc
poll'akic
>'elegon
<um~in
n~un
d`e
ka`i
kla'iwn
l'egw
to`uc
>eqjro`uc
to~u
stauro~u
to~u
qristo~u\bibvsend
\vs Phi 3:19
<~wn
t`o
t'eloc
>ap'wleia
<~wn
<o
vje`oc
<h
koil'ia
ka`i
<h
d'oxa
>en
t~h|
a>isq'unh|
a>ut~wn
o<i
t`a
>ep'igeia
vfrono~untec\bibvsend
\vs Phi 3:20
<hm~wn
g`ar
t`o
pol'iteuma
>en
o>urano~ic
<up'arqei
>ex
o<~u
ka`i
swt~hra
>apekdeq'omeja
k'urion
>ihso~un
qrist'on\bibvsend
\vs Phi 3:21
<`oc
metasqhmat'isei
t`o
s~wma
t~hc
tapein'wsewc
<hm~wn
e>ic\r{}
\fn{\src{TMK}: eic to genesjai auto, \src{V}: \bibempty.}
t`o
gen'esjai
a>ut`o
s'ummorfon
t~w|
s'wmati
t~hc
d'oxhc
a>uto~u
kat`a
t`hn
>en'ergeian
to~u
d'unasjai
a>ut`on
ka`i
<upot'axai
<e\r{a}ut~w|
\fn{\src{TMK}: eautw, \src{V}: autw.}
t`a
p'anta\bibvsend
\vs Phi 4:1
<'wste
>adelfo'i
mou
>agaphto`i
ka`i
>epip'ojhtoi
qar`a
ka`i
st'efan'oc
mou
o<'utwc
st'hkete
>en
kur'iw|
>agaphto'i\bibvsend
\vs Phi 4:2
e>u\r{w}d'ian
\fn{\src{T}: euwdian, \src{K|M|V}: euodian.}
parakal~w
ka`i
sunt'uqhn
parakal~w
t`o
a>ut`o
vfrone~in
>en
kur'iw|\bibvsend
\vs Phi 4:3
\r{k}a`i
\fn{\src{T|K}: kai, \src{M|V}: nai.}
>erwt~w
ka'i
se
s'uzuge\r{}
\fn{\src{TMK}: suzuge gnhsie, \src{V}: gnhsie suzuge.}
gn'hsie
sullamb'anou
a>uta~ic
a<'itinec
>en
t~w|
e>uaggel'iw|
sun'hjlhs'an
moi
met`a
ka`i
kl'hmentoc
ka`i
t~wn
loip~wn
sunerg~wn
mou
<~wn
t`a
>on'omata
>en
vb'iblw|
vzw~hc\bibvsend
\vs Phi 4:4
qa'irete
>en
kur'iw|
p'antote
p'alin
>er~w
qa'irete\bibvsend
\vs Phi 4:5
t`o
>epieik`ec
<um~wn
gnwsj'htw
p~asin
>anjr'wpoic
<o
k'urioc
>egg'uc\bibvsend
\vs Phi 4:6
mhd`en
merimn~ate
>all>
>en
pant`i
t~h|
proseuq~h|
ka`i
t~h|
de'hsei
met`a
e>uqarist'iac
t`a
a>it'hmata
<um~wn
gnwriz'esjw
pr`oc
t`on
vje'on\bibvsend
\vs Phi 4:7
ka`i
<h
e>ir'hnh
to~u
vjeo~u
<h
<uper'eqousa
p'anta
no~un
vfrour'hsei
t`ac
kard'iac
<um~wn
ka`i
t`a
no'hmata
<um~wn
>en
qrist~w|
>ihso~u\bibvsend
\vs Phi 4:8
t`o
loip`on
>adelfo`i
<'osa
>est`in
>alhj~h
<'osa
semn`a
<'osa
d'ikaia
<'osa
<agn`a
<'osa
prosfil~h
<'osa
e>'ufhma
e>'i
tic
>aret`h
ka`i
e>'i
tic
>'epainoc
ta~uta
log'izesje\bibvsend
\vs Phi 4:9
<`a
ka`i
>em'ajete
ka`i
parel'abete
ka`i
>hko'usate
ka`i
e>'idete
>en
>emo`i
ta~uta
pr'assete
ka`i
<o
vje`oc
t~hc
e>ir'hnhc
>'estai
mej>
<um~wn\bibvsend
\vs Phi 4:10
>eq'arhn
d`e
>en
kur'iw|
meg'alwc
<'oti
>'hdh
pot`e
>anej'alete
t`o
<up`er
>emo~u
vfrone~in
>ef>
<~w|
ka`i
>efrone~ite
>hkaire~isje
d'e\bibvsend
\vs Phi 4:11
o>uq
<'oti
kaj>
<ust'erhsin
l'egw
>eg`w
g`ar
>'emajon
>en
o<~ic
e>imi
a>ut'arkhc
e>~inai\bibvsend
\vs Phi 4:12
o>~ida
d`e\r{}
\fn{\src{T}: de, \src{K|M|V}: kai.}
tapeino~usjai
o>~ida
ka`i
perisse'uein
>en
pant`i
ka`i
>en
p~asin
mem'uhmai
ka`i
qort'azesjai
ka`i
pein~a|n
ka`i
perisse'uein
ka`i
<ustere~isjai\bibvsend
\vs Phi 4:13
p'anta
>isq'uw
>en
t~w|
>endunamo~unt'i
me
qri\r{s}t~w|\bibvsend
\fn{\src{TMK}: qristw, \src{V}: \bibempty.}
\vs Phi 4:14
pl`hn
kal~wc
>epoi'hsate
sugkoinwn'hsant'ec
mou
t~h|
vjl'iyei\bibvsend
\vs Phi 4:15
o>'idate
d`e
ka`i
<ume~ic
vfilipp'hsioi
<'oti
>en
>arq~h|
to~u
e>uaggel'iou
<'ote
>ex~hljon
>ap`o
makedon'iac
o>udem'ia
moi
>ekklhs'ia
>ekoin'wnhsen
e>ic
l'ogon
d'osewc
ka`i
l'h\r{y}ewc
\fn{\src{TMK}: lhyewc, \src{V}: lhmyewc.}
e>i
m`h
<ume~ic
m'onoi\bibvsend
\vs Phi 4:16
<'oti
ka`i
>en
vjessalon'ikh|
ka`i
<'apax
ka`i
d`ic
e>ic
t`hn
qre'ian
moi
>ep'emyate\bibvsend
\vs Phi 4:17
o>uq
<'oti
>epizht~w
t`o
d'oma
>al\r{l}>
\fn{\src{TMK}: all, \src{V}: alla.}
>epizht~w
t`on
karp`on
t`on
pleon'azonta
e>ic
l'ogon
<um~wn\bibvsend
\vs Phi 4:18
>ap'eqw
d`e
p'anta
ka`i
perisse'uw
pepl'hrwmai
dex'amenoc
par`a
>epafrod'itou
t`a
par>
<um~wn
>osm`hn
e>uwd'iac
vjus'ian
dekt`hn
e>u'areston
t~w|
vje~w|\bibvsend
\vs Phi 4:19
<o
d`e
vje'oc
mou
plhr'wsei
p~asan
qre'ian
<um~wn
kat`a
t`on\r{}
\fn{\src{TMK}: ton plouton, \src{V}: to ploutoc.}
plo~uton
a>uto~u
>en
d'oxh|
>en
qrist~w|
>ihso~u\bibvsend
\vs Phi 4:20
t~w|
d`e
vje~w|
ka`i
patr`i
<hm~wn
<h
d'oxa
e>ic
to`uc
a>i~wnac
t~wn
a>i'wnwn
>am'hn\bibvsend
\vs Phi 4:21
>asp'asasje
p'anta
<'agion
>en
qrist~w|
>ihso~u
>asp'azontai
<um~ac
o<i
s`un
>emo`i
>adelfo'i\bibvsend
\vs Phi 4:22
>asp'azontai
<um~ac
p'antec
o<i
<'agioi
m'alista
d`e
o<i
>ek
t~hc
ka'isaroc
o>ik'iac\bibvsend
\vs Phi 4:23
<h
q'aric
to~u
kur'iou
<h\r{m}~wn
\fn{\src{T|K}: hmwn, \src{M|V}: \bibempty.}
>ihso~u
qristo~u
met`a
p'antwn\r{}
\fn{\src{TMK}: pantwn umwn amhn, \src{V}: tou pneumatoc umwn.}
<um~wn
>am'hn\bibvsend
Pr`oc\r{}
\fn{\src{T}: Proc \ldots\ epafroditou, \src{K|M|V}: \bibempty.}
vfilipphs'iouc
>egr'afh
>ap`o
<r'wmhc
di>
>epafrod'itou\bibvsend
