\bibbook{H PROS FILHMONA\\\LARGE EPISTOLH PAULOU\r{}}{PROS FILHMONA}{Philemon}{Phm}[PROS FILHMONA]
\vs Phm 1:1
pa~uloc
\fnt{\src{T}: H PROS FILHMONA EPISTOLH PAULOU, \src{K}: PAULOU H PROS FILHMONA EPISTOLH, \src{M|V}: PROS FILHMONA.}
d'esmioc
qristo~u
>ihso~u
ka`i
tim'ojeoc
<o
>adelf`oc
vfil'hmoni
t~w|
>agapht~w|
ka`i
sunerg~w|
<hm~wn\bibvsend
\vs Phm 1:2
ka`i
>apf'ia|
t~h|
>a\r{g}a\-ph\-t~h|
\fn{\src{TMK}: agaphth, \src{V}: adelfh.}
ka`i
>arq'ippw|
t~w|
sustrati'wth|
<hm~wn
ka`i
t~h|
kat>
o>~ik'on
sou
>ekklhs'ia|\bibvsend
\vs Phm 1:3
q'aric
<um~in
ka`i
e>ir'hnh
>ap`o
vjeo~u
patr`oc
<hm~wn
ka`i
kur'iou
>ihso~u
qristo~u\bibvsend
\vs Phm 1:4
e>uqarist~w
t~w|
vje~w|
mou
p'antote
mne'ian
sou
poio'umenoc
>ep`i
t~wn
proseuq~wn
mou\bibvsend
\vs Phm 1:5
>ako'uwn
sou
t`hn
>ag'aphn
ka`i
t`hn
p'istin
<`hn
>'eqeic
pr`oc
t`on
k'urion
>ihso~un
ka`i
e>ic
p'antac
to`uc
<ag'iouc\bibvsend
\vs Phm 1:6
<'opwc
<h
koinwn'ia
t~hc
p'iste'wc
sou
>energ`hc
g'enhtai
>en
>epign'wsei
pant`oc
>agajo~u
to~u
>en
<u\r{m}~in
\fn{\src{T|K}: umin, \src{M|V}: hmin.}
e>ic
qrist`on
>ih\r{s}o~un\bibvsend
\fn{\src{TMK}: ihsoun, \src{V}: \bibempty.}
\vs Phm 1:7
q'arin\r{}
\fn{\src{T|M}: qarin gar eqomen pollhn, \src{K}: qaran gar eqomen pollhn, \src{V}: qaran gar pollhn esqon.}
g`ar
>'eqomen
poll`hn
ka`i
par'aklhsin
>ep`i
t~h|
>ag'aph|
sou
<'oti
t`a
spl'agqna
t~wn
<ag'iwn
>anap'epautai
di`a
so~u
>adelf'e\bibvsend
\vs Phm 1:8
di`o
poll`hn
>en
qrist~w|
parrhs'ian
>'eqwn
>epit'assein
soi
t`o
>an~hkon\bibvsend
\vs Phm 1:9
di`a
t`hn
>ag'aphn
m~allon
parakal~w
toio~utoc
>`wn
<wc
pa~uloc
presb'uthc
nun`i
d`e
ka`i
d'esmioc
>ihso~u\r{}
\fn{\src{TMK}: ihsou qristou, \src{V}: qristou ihsou.}
qristo~u\bibvsend
\vs Phm 1:10
parakal~w
se
per`i
to~u
>emo~u
t'eknou
<`on
>eg'ennhsa
>en
to~ic
desmo~ic
m\r{o}u
\fn{\src{TMK}: mou, \src{V}: \bibempty.}
>on'hsimon\bibvsend
\vs Phm 1:11
t'on
pot'e
soi
>'aqrhston
nun`i
d'e\r{}
\fn{\src{TMK}: de, \src{V}: de [kai].}
soi
ka`i
>emo`i
e>'uqrhston\bibvsend
\vs Phm 1:12
<`on
>an'epemya
s`u\r{}
\fn{\src{TMK}: su de, \src{V}: soi.}
d`e
a>ut`on
tou\r{t}'estin
\fn{\src{T}: toutestin, \src{K|M|V}: tout estin.}
t`a
>em`a
spl'agqna
pro\r{s}labo~u\bibvsend
\fn{\src{TMK}: proslabou, \src{V}: \bibempty.}
\vs Phm 1:13
<`on
>eg`w
>eboul'omhn
pr`oc
>emaut`on
kat'eqein
<'ina
<up`er
so~u
diakon~h|\r{}
\fn{\src{TMK}: diakonh moi, \src{V}: moi diakonh.}
moi
>en
to~ic
desmo~ic
to~u
e>uaggel'iou\bibvsend
\vs Phm 1:14
qwr`ic
d`e
t~hc
s~hc
gn'wmhc
o>ud`en
>hj'elhsa
poi~hsai
<'ina
m`h
<wc
kat`a
>an'agkhn
t`o
>agaj'on
sou
>~h|
>all`a
kat`a
<eko'usion\bibvsend
\vs Phm 1:15
t'aqa
g`ar
di`a
to~uto
>eqwr'isjh
pr`oc
<'wran
<'ina
a>i'wnion
a>ut`on
>ap'eqh|c\bibvsend
\vs Phm 1:16
o>uk'eti
<wc
do~ulon
>all>
<up`er
do~ulon
>adelf`on
>agapht`on
m'alista
>emo`i
p'osw|
d`e
m~all'on
soi
ka`i
>en
sark`i
ka`i
>en
kur'iw|\bibvsend
\vs Phm 1:17
e>i
o>~un
>e\r{m}`e
\fn{\src{T|K}: eme, \src{M|V}: me.}
>'eqeic
koinwn`on
proslabo~u
a>ut`on
<wc
>em'e\bibvsend
\vs Phm 1:18
e>i
d'e
ti
>hd'ikhs'en
se
>`h
>ofe'ilei
to~uto
>emo`i
>ell'og\r{e}i\bibvsend
\fn{\src{TMK}: ellogei, \src{V}: elloga.}
\vs Phm 1:19
>eg`w
pa~uloc
>'egraya
t~h|
>em~h|
qeir`i
>eg`w
>apot'isw
<'ina
m`h
l'egw
soi
<'oti
ka`i
seaut'on
moi
prosofe'ileic\bibvsend
\vs Phm 1:20
na`i
>adelf`e
>eg'w
sou
>ona'imhn
>en
kur'iw|
>an'apaus'on
mou
t`a
spl'agqna
>en
ku\r{r}'iw|\bibvsend
\fn{\src{TMK}: kuriw, \src{V}: qristw.}
\vs Phm 1:21
pepoij`wc
t~h|
<upako~h|
sou
>'egray'a
soi
e>id`wc
<'oti
ka`i
<up`er
<`o\r{}
\fn{\src{TMK}: o, \src{V}: a.}
l'egw
poi'hseic\bibvsend
\vs Phm 1:22
<'ama
d`e
ka`i
<eto'imaz'e
moi
xen'ian
>elp'izw
g`ar
<'oti
di`a
t~wn
proseuq~wn
<um~wn
qarisj'hsomai
<um~in\bibvsend
\vs Phm 1:23
>asp'az\r{o}nta'i
\fn{\src{TMK}: aspazontai, \src{V}: aspazetai.}
se
>epafr~ac
<o
sunaiqm'alwt'oc
mou
>en
qrist~w|
>ihso~u\bibvsend
\vs Phm 1:24
m'arkoc
>ar'istarqoc
dhm~ac
louk~ac
o<i
sunergo'i
mou\bibvsend
\vs Phm 1:25
<h
q'aric
to~u
kur'iou
<h\r{m}~wn
\fn{\src{TMK}: hmwn, \src{V}: \bibempty.}
>ihso~u
qristo~u
met`a
to~u
pne'umatoc
<um~wn
>a\r{m}'hn\bibvsend
\fn{\src{TMK}: amhn, \src{V}: \bibempty.}
Pr`oc\r{}
\fn{\src{T}: Proc \ldots\ oiketou, \src{K|M|V}: \bibempty.}
vfil'hmona
>egr'afh
>ap`o
<r'wmhc
di`a
>onhs'imou
o>ik'etou\bibvsend
